### 2018-12-18 paper.tex
commit

\documentclass[11pt]{article}
\usepackage[hidelinks]{hyperref}
\usepackage{amsthm,amsmath,amsfonts,amssymb,amstext,mathtools}
\usepackage{fullpage}
\usepackage{macros}

\begin{document}

\title{An Air Drop That Preserves Recipient Privacy}
\author{Dan Boneh \and Riad Wahby}

\maketitle

\begin{abstract}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

More to come.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Private air drop: definitions}

A private air drop (PAD) system is a triple of efficient algorithms:
\begin{itemize}
\item $\text{sendTokens}(\PK) \to (c, s)$:
Generates a token $c$ to be posted on the blockchain,
and a secret $s$ given to the recipient via a private channel
(e.g., by posting an encryption of $s$ encrypted under $\PK$ 
to the blockchain).

\item $\text{sign}(\SK, (c, s), m) \to \text{sig}$:
Signs a message $m$ indicating that the token $c$ is spent.

\item $\text{verify}(c, m, \text{sig}) \to \{\text{yes},\text{no}\}:$
Verifier that a signature $\text{sig}$ on token $c$ is valid.
\end{itemize}

Informal security properties: 
(1) $c$ and $\text{sig}$ should reveal nothing about $\PK$,
(2) without $\SK$: existential unforgeability under a 
(one-time) chosen message attack.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A private air drop to RSA public keys}

From here we use the following notations:
$\range{\ell}$ denotes the set $\{0,1,\ldots,\ell-1\}$ and 
$\textsf{Primes}(\lambda)$ is a set of size $2^\lambda$ 
containing the smallest $2^\lambda$ odd primes.

We will also need a set of public parameters that include the description
of a cyclic group $\GG$ of unknown order.  We let $g$ and $h$ be two
random generators of $\GG$ where the discrete-log of $g$ base $h$ is unknown. 
We assume that an upper bound $G$ on $\abs{\GG}$ is known.

\noindent
With this setup, the private air drop system works as follows:

\paragraph{Algorithm $\text{sendTokens}(\PK)$:}
To send tokens to an RSA public key $\PK = (n, e)$ do:
\begin{itemize}
\item 
generate a random $s \rgets \range{G}$.

\item 
output $(c, s)$ where $c \gets g^n \cdot h^s \in \GG$.
\end{itemize}

\medskip\noindent 
The following two notes can help optimize the scheme:
\begin{itemize}
\item[$-$] $s$ is privately sent to the owner of $\PK$, for example
by encrypting $s$ under $\PK$ to obtain a ciphertext $c'$ and
publishing this $c'$ somewhere, not necessarily on the blockchain.  There is
a public association between $c'$ and $\PK$ (e.g., via a hash table),
so that the owner of $\PK$ can easily find $c'$.  One can include
$H(c)$ in the plaintext encrypted in $c'$ to help the owner of $\PK$
quickly find $c$.

\item[$-$] One can generate $s$ 
as $s \gets H(s')$ where $s'$ is a random 256-bit value and $H$ is a hash
function $H:\{0,1\}^{256} \to \range{G}$.  The ciphertext $c'$ is
an encryption of $s'$, instead of $s$, which can shrink~$c'$.
\end{itemize}

\paragraph{Algorithm $\text{sign}(\SK, (c, s), m)$:}  
To withdraw the funds associated with the token $c$ the user
signs a withdrawl message $m$ using the RSA secret key $\SK = (n,p,q)$ 
as follows:
\begin{itemize}
\item Find a prime $2 \leq t \leq 1000$  such that $t$ is a quadratic 
residue in $\ZZ_n$.

\item The user proves possession of $\SK$ by proving knowledge of 
$w \deq \sqrt{t} \in \ZZ_n$ without revealing $w$ or $n$. 
The user does so as follows:
\begin{enumerate}
\item find integers $(w,a)$ such that $w^2 = t + a n$ in $\ZZ$
           (i.e. $w$ is a square root of $t$ modulo $n$)

\item choose a random $G$-bit integer $s_1$ and compute
           $c_1 \gets g^w \cdot h^{s_1} \in \GG$.

\item with $(c_1, t)$ public, the computed signature is a
  signature of knowledge of seven integers 
%$(n, w, a, s, s_1)$ where
%\begin{align*}
%  c & = g^n h^s         \quad\in \GG,  \\
%  c_1 & = g^w h^{s_1}      \quad\in \GG,   \\
%  w^2 & = t + a \cdot n  \quad\in \ZZ.
%\end{align*}
%The ZKPK works by proving knowledge of integers
   $\textit{witness} = (w, \textit{w2}, s_1, a, \textit{an}, \textit{s1w}, \textit{sa}) \in \ZZ^7$
satisfying:
\begin{align} \label{eq:proofeq}
\begin{split}
     c_1 & = g^w h^{\textit{s1}} \\
     g^{\textit{w2}} h^{\textit{s1w}} & = c_1^w \\
     g^{\textit{an}} \cdot h^{\textit{sa}} & = c^a \\
     \textit{w2} & = t + \textit{an}
\end{split}
\end{align}
\end{enumerate}
\end{itemize}
If~\eqref{eq:proofeq} holds then $w2 = w^2$ and $\mathit{an} = a \cdot n$
in $\ZZ$.
The last equation in~\eqref{eq:proofeq} 
ensures that $w^2 = t + a \cdot n$ in $\ZZ$,
as required.

To implement the ZKPK for~\eqref{eq:proofeq} let us define a 
homomorphism $\phi:\ZZ^7 \to \GG^3 \times \ZZ$ as follows:
\[ 
  \phi(w, \textit{w2}, s_1, a, \textit{an}, \textit{s1w}, \textit{sa}) \deq
      \Big(\ 
       g^w \cdot h^{\textit{s1}},\ \ \ 
       g^{\textit{w2}} \cdot h^{\textit{s1w}} / c_1^w,\ \ \ 
       g^{\textit{an}} \cdot h^{\textit{sa}} / c^a,\ \ \ 
       \textit{w2} - \textit{an}\ \Big)
\]
Then we need a ZKPK for a vector $v \in \ZZ^7$
such that $\phi(v) = (c_1, 1, 1, t) \in \GG^3 \times \ZZ$. 
We to so using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper} 
and convert it
into a signature scheme using Fiat-Shamir.  
The resulting signature scheme works as follows:
\begin{itemize}
\item choose seven random integers
            $r_w, r_\textit{w2}, r_\textit{s1}, r_a, r_\textit{an}, r_\textit{s1w}, r_\textit{sa} \rgets \range{B}$ and compute
\[ (A,B,C,D) \gets \phi(r_w, r_\textit{w2}, r_\textit{s1}, r_a, r_\textit{an}, r_\textit{s1w}, r_\textit{sa}) \in \GG^3 \times \ZZ. \]
The range $\range{B}$ needs to be chosen so that the
random values are sufficiently big to ensure that the vector $z \in \ZZ^7$ below
is statistically independent of the vector $\textit{witness} \in \ZZ^7$.

\item compute
            $\textit{PRNGKey} = \text{Hash}(m, G, g, h, c, c_1, t, A, B, C, D)$.
Use a PRNG seeded with $\textit{PRNGKey}$ to generate a random
  128-bit $\textit{chal}$ and a random 128-bit prime $\ell$.

\item compute the integer vector
   \[  z \gets \textit{chal} \cdot (w, \textit{w2}, \textit{s1}, a, \textit{an}, \textit{s1w}, \textit{sa}) +
                   (r_w, r_\textit{w2}, r_\textit{s1}, r_a, r_\textit{an}, r_\textit{s1w}, r_\textit{sa})  \in \ZZ^7  \]
Let $z \gets (z_w, z_\textit{w2}, z_\textit{s1}, z_a, z_\textit{an}, z_\textit{s1w}, z_\textit{sa})$
and $z' \gets (z \bmod \ell) \in \ZZ^7$.

\item compute 
\[  (A_q, B_q, C_q, D_q) \gets \phi\Big(
        \lfloor z_w / \ell \rfloor, 
        \lfloor z_\textit{w2} / \ell \rfloor, 
        \lfloor z_\textit{s1} / \ell \rfloor, 
        \lfloor z_a / \ell \rfloor, 
        \lfloor z_\textit{an} / \ell \rfloor, 
        \lfloor z_\textit{s1w} / \ell \rfloor, 
        \lfloor z_\textit{sa} / \ell \rfloor \Big) \in \GG^3 \times \ZZ. \]

\item output the signature 
$\text{sig} = (c_1, t, \textit{chal}, \ell, A_q, B_q, C_q, D_q, z')$.
\end{itemize}

\paragraph{Algorithm $\text{verify}(c, m, \text{sig}):$}
Verify that $\text{sig}$ is a valid signature for
token $c$ on the message $m$.
\begin{itemize}
\item compute $(A_\ell, B_\ell, C_\ell, D_\ell) \gets \phi(z') \in \GG^3 \times \ZZ$.
\item compute 
\begin{align*}
     A & \gets A_q^\ell \cdot A_\ell  / c_1^{\textit{chal}} \\
     B & \gets B_q^\ell \cdot B_\ell  \\
     C & \gets C_q^\ell \cdot C_\ell  \\
     D & \gets D_q \cdot \ell + D_\ell - (t \cdot \textit{chal}) \\
     \textit{PRNGkey} & \gets \text{Hash}(m, G, g, h, c, c_1, t, A, B, C, D)
\end{align*}

\item use a PRNG seeded with $\textit{PRNGkey}$ to generate $\text{chal}'$ and
  $\ell'$ as described in the sign algorithm. Since $\ell$ is
  included in the signature, the verifier does not need to search for
  a prime, but can instead verify that the given $\ell$ is prime and
  is not too far from the base starting point of the prime search.

\item accept iff $\text{chal}' = \text{chal}$ and $\ell' = \ell$.
\end{itemize}

\paragraph{Comments.}
There is a seemingly simpler method to prove that one knows the
factorization of $n$, namely, prove that one knows $p$ such that $p$
divides $n$.  That is, instead of committing to $w$ we would commit to
$p$ and then prove that the committed value divides $n$. But we would
also need to prove that the committed factor is not one of 
$\{1, -1, n, -n\}$, and that will result in a longer proof.

This scheme is only secure is a group where there are no known
elements of low order.  The group $\ZZ/n$ is not such a group because
of the element $-1$ of order $2$.  To eliminate this element we work
in the quotient group $(\ZZ/n)/\{\pm 1\}$, representing elements as
$\abs{x} = \min(x, n - x)$.  In this group $-1$ is the same as $1$,
and presumably there are no other known elements of known order.

\paragraph{Proof of security.}
We need to prove two things: 
(1) privacy: there is a simulator that can generate a properly distributed
signature just given $c$ and $m$, and 
(2) security: an attacker that can generate a valid siganture for $c$ using
some message $m' \neq m$ can be used to compute $\sqrt{t} \in \ZZ_n$
for some $2 \leq t \leq 1000$.

\paragraph{Proof of privacy.}

\paragraph{Proof of security.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A private air drop to ElGamal public keys}

\bibliographystyle{alpha}
\bibliography{paper}

\end{document}

### 2018-12-24 paper.tex
edits

@@
 From here we use the following notations:
-$\range{\ell}$ denotes the set $\{0,1,\ldots,\ell-1\}$ and 
-$\textsf{Primes}(\lambda)$ is a set of size $2^\lambda$ 
+$\lambda$ is the security parameter (e.g., $\lambda = 128$), 
+$\range{\ell}$ denotes the set of integers $\{0,1,\ldots,\ell-1\}$ and 
+$\primes$ is a set of size $2^\lambda$ 
 containing the smallest $2^\lambda$ odd primes. 
-
+%
 We will also need a set of public parameters that include the description
@@
 random generators of $\GG$ where the discrete-log of $g$ base $h$ is unknown.
-We assume that an upper bound $G$ on $\abs{\GG}$ is known.
 
-\noindent
-With this setup, the private air drop system works as follows:
+\subsection{Proving knowledge of the factorization of a hidden integer}
+
+We first develop a zero knowledge protocol for proving
+knowledge of the factorization of an integer $n$ given
+as a commitment to $n$.
+We let $N$ be a known upper bound on $n$, so that $n \in \range{N}$.
+For simplicity we will also assume that $\abs{\GG} < N$. 
+The given commitment to $n$ is $c \deq g^n \cdot h^s \in \GG$,
+where $s \rgets \range{N}$.
+
+To prove knowledge of the factorization of $n$ the prover
+proves knowledge of a $w \in \range{N}$ such that $w^2 \equiv t \pmod{n}$
+for some small public prime $t \in \ZZ$, namely $2 \leq t \leq \lambda$.
+That is, we provide a ZKPK for the relation
+\begin{equation} \label{eq:lang}
+  {\cal R} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
+                              (n, s, w, a) \in \range{N}^4 \Bigr)  \ \ 
+        \text{s.t.}\ \ 
+                \begin{split}
+                        c   & = g^n \cdot h^s \ \ \text{in $\GG$}, \\
+                        w^2 & = t + a \cdot n \ \ \text{in $\ZZ$}, \\
+                        t   & \ \textrm{a prime}
+                \end{split}  \right\}.
+\end{equation}
+Here $(c, t)$ is the statement and $(n, s, w, a)$ is the witness.
+The integer relation $w^2 = t + a n$ proves that 
+$w^2 \equiv t \pmod{n}$, as required.
+We note that a ZKPK for~\eqref{eq:lang} proves that $t \in \ZZ$ is a quadratic
+residue modulo the committed $n$.  Leaking this bit of information about $n$
+does not interfere with the application to a secure air drop.
+
+\medskip\noindent
+The ZKPK protocol for~\eqref{eq:lang} 
+between the prover $P$ and the verifier $V$ works as follows:
+\begin{itemize}
+\item input:  the verifier has $(c, t) \in \GG \times \range{\lambda}$ and 
+the prover has $(c, t, n, s, w, a) \in \GG \times \range{N}^5$
+
+\item Prover $P$ chooses a random integer $s_1 \rgets \range{N}$ and computes
+       $c_1 \gets g^w \cdot h^{s_1} \in \GG$.
+
+\item Next, define a homomorphism $\phi:\ZZ^7 \to \GG^3 \times \ZZ$ as follows:
+\begin{equation} \label{eq:hom}
+  \phi(w, \mathit{w2}, s_1, a, \mathit{an}, \mathit{s1w}, \mathit{sa}) \deq
+      \Bigl(\ 
+       g^w \cdot h^{\mathit{s1}},\ \ \ 
+       g^{\mathit{w2}} \cdot h^{\mathit{s1w}} / c_1^w,\ \ \ 
+       g^{\mathit{an}} \cdot h^{\mathit{sa}} / c^a,\ \ \ 
+       \mathit{w2} - \mathit{an}\ \Bigr)
+\end{equation}
+It is easy to see that $\phi$ is a group homomorphism.
+The range of $\phi$ is the group $\GG^3 \times \ZZ$.  
+We will write the group operation in this group multiplicatively.
+That is, if $(a_i, b_i, c_i, d_i) \in \GG^3 \times \ZZ$ for $i=1,2$
+then 
+\[  (a_1, b_1, c_1, d_1) \cdot (a_2, b_2, c_2, d_2) \deq 
+      (a_1 a_2,\ b_1 b_2,\ c_1 c_2,\ d_1 + d_2).  \]
+
+We need a ZKPK for a $\phi$-preimage of 
+$T \deq (c_1, 1, 1, t) \in \GG^3 \times \ZZ$. 
+In other words, we need a zero-knowledge proof of knowledge for a vector 
+$\vv' = (w', \mathit{w2}', s_1', a', \mathit{an}', 
+              \mathit{s1w}', \mathit{sa}') \in \ZZ^7$ 
+such that 
+\[   \phi(\vv') = T = (c_1, 1, 1, t) \in \GG^3 \times \ZZ.  \]
+Doing so proves 
+that $c_1$ is a commitment to $w' \in \ZZ$, 
+that $\mathit{w2}' = (w')^2$, and 
+that $\mathit{an}' = a' \cdot n$ for some integer $a'$.
+Then the last relation proves that $(w')^2 - a' \cdot n = t$ in $\ZZ$,
+as required.
+
+We design a ZKPK for a $\phi$-preimage 
+using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}:
+\begin{enumerate}
+\item The prover chooses a random $\rv \rgets \range{N}^7$
+and computes $\Rv \gets \phi(\rv) \in \GG^3 \times \ZZ$. \\
+It sends $(c_1, \Rv)$ to the verifier.
+
+\item The verifier chooses challenges $\mathit{ch} \rgets \range{2^\lambda}$
+and $\ell \rgets \primes$. \\
+It sends $(\mathit{ch}, \ell)$ to the prover.
+
+\item The prover computes:
+\[  \xv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^7, \quad
+    \zv_\ell \gets (\xv \bmod \ell) \in \range{\ell}^7, \quad
+    \zv_q \gets \lfloor \xv / \ell \rfloor \in \ZZ^7, \quad
+    \Zv_q \gets \phi(\zv_q)  
+\]
+and sends $(\Zv_q, \zv_\ell) \in \GG^3 \times \ZZ \times \range{\ell}^7$ 
+to the verifier.
+
+\item The verifier accepts if 
+$\ \Zv_q^\ell \cdot \phi(\zv_\ell) = T^\mathit{ch} \cdot \Rv\ $ in 
+$\GG^3 \times \ZZ$.
+\end{enumerate}
+\end{itemize}
+
+\paragraph{Comment.}
+There is a seemingly simpler method to prove that one knows the
+factorization of~$n$, namely, prove that one knows $p$ such that $p$
+divides $n$.  That is, instead of committing to $w$ we would commit to
+$p$ and then prove that the committed value divides $n$. But we would
+also need to prove that the committed factor is not one of 
+$\{1, -1, n, -n\}$, and that results in a longer proof.
+
+\paragraph{Proof of security.}
+We need to prove the protocol above is zero-knowledge and a 
+proof of knowledge.
+
+\paragraph{Proof of zero-knowledge.}
+
+\paragraph{Proof of extractability.}
+
+\subsection{The concrete air drop system}
+
+The air drop system is obtained by applying the Fiat-Shamir
+heuristic to the protocol from the previous section. 
+The concrete private air drop system works as follows:
 
@@
 \begin{itemize}
-\item Find a prime $2 \leq t \leq 1000$  such that $t$ is a quadratic 
+\item find a prime $2 \leq t \leq \lambda$  such that $t$ is a quadratic 
 residue in $\ZZ_n$.
 
-\item The user proves possession of $\SK$ by proving knowledge of 
-$w \deq \sqrt{t} \in \ZZ_n$ without revealing $w$ or $n$. 
-The user does so as follows:
-\begin{enumerate}
 \item find integers $(w,a)$ such that $w^2 = t + a n$ in $\ZZ$
@@
 
-\item choose a random $G$-bit integer $s_1$ and compute
+\item choose a random $s_1 \rgets \range{N}$ and compute
            $c_1 \gets g^w \cdot h^{s_1} \in \GG$.
 
-\item with $(c_1, t)$ public, the computed signature is a
-  signature of knowledge of seven integers 
-%$(n, w, a, s, s_1)$ where
-%\begin{align*}
-%  c & = g^n h^s         \quad\in \GG,  \\
-%  c_1 & = g^w h^{s_1}      \quad\in \GG,   \\
-%  w^2 & = t + a \cdot n  \quad\in \ZZ.
-%\end{align*}
-%The ZKPK works by proving knowledge of integers
-   $\textit{witness} = (w, \textit{w2}, s_1, a, \textit{an}, \textit{s1w}, \textit{sa}) \in \ZZ^7$
-satisfying:
-\begin{align} \label{eq:proofeq}
-\begin{split}
-     c_1 & = g^w h^{\textit{s1}} \\
-     g^{\textit{w2}} h^{\textit{s1w}} & = c_1^w \\
-     g^{\textit{an}} \cdot h^{\textit{sa}} & = c^a \\
-     \textit{w2} & = t + \textit{an}
-\end{split}
-\end{align}
-\end{enumerate}
-\end{itemize}
-If~\eqref{eq:proofeq} holds then $w2 = w^2$ and $\mathit{an} = a \cdot n$
-in $\ZZ$.
-The last equation in~\eqref{eq:proofeq} 
-ensures that $w^2 = t + a \cdot n$ in $\ZZ$,
-as required.
+\item choose a random $\rv \rgets \range{N}^7$
+and compute $\Rv \gets \phi(\rv) \in \GG^3 \times \ZZ$.
 
-To implement the ZKPK for~\eqref{eq:proofeq} let us define a 
-homomorphism $\phi:\ZZ^7 \to \GG^3 \times \ZZ$ as follows:
-\[ 
-  \phi(w, \textit{w2}, s_1, a, \textit{an}, \textit{s1w}, \textit{sa}) \deq
-      \Big(\ 
-       g^w \cdot h^{\textit{s1}},\ \ \ 
-       g^{\textit{w2}} \cdot h^{\textit{s1w}} / c_1^w,\ \ \ 
-       g^{\textit{an}} \cdot h^{\textit{sa}} / c^a,\ \ \ 
-       \textit{w2} - \textit{an}\ \Big)
+\item compute $\mathit{seed} \gets \text{Hash}(m, \GG, g, h, c, c_1, t, \Rv$).
+
+\item
+use a $\text{PRNG}(\mathit{seed})$ to generate $(\mathit{ch}, \ell)$, 
+where $\mathit{ch} \in \range{2^\lambda}$ and $\ell \in \primes$.
+
+\item compute:
+\[  \xv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^7, \quad
+    \zv_\ell \gets (\xv \bmod \ell) \in \range{\ell}^7, \quad
+    \zv_q \gets \lfloor \xv / \ell \rfloor \in \ZZ^7, \quad
+    \Zv_q \gets \phi(\zv_q) \in \GG^3 \times \ZZ.
 \]
-Then we need a ZKPK for a vector $v \in \ZZ^7$
-such that $\phi(v) = (c_1, 1, 1, t) \in \GG^3 \times \ZZ$. 
-We to so using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper} 
-and convert it
-into a signature scheme using Fiat-Shamir.  
-The resulting signature scheme works as follows:
-\begin{itemize}
-\item choose seven random integers
-            $r_w, r_\textit{w2}, r_\textit{s1}, r_a, r_\textit{an}, r_\textit{s1w}, r_\textit{sa} \rgets \range{B}$ and compute
-\[ (A,B,C,D) \gets \phi(r_w, r_\textit{w2}, r_\textit{s1}, r_a, r_\textit{an}, r_\textit{s1w}, r_\textit{sa}) \in \GG^3 \times \ZZ. \]
-The range $\range{B}$ needs to be chosen so that the
-random values are sufficiently big to ensure that the vector $z \in \ZZ^7$ below
-is statistically independent of the vector $\textit{witness} \in \ZZ^7$.
-
-\item compute
-            $\textit{PRNGKey} = \text{Hash}(m, G, g, h, c, c_1, t, A, B, C, D)$.
-Use a PRNG seeded with $\textit{PRNGKey}$ to generate a random
-  128-bit $\textit{chal}$ and a random 128-bit prime $\ell$.
-
-\item compute the integer vector
-   \[  z \gets \textit{chal} \cdot (w, \textit{w2}, \textit{s1}, a, \textit{an}, \textit{s1w}, \textit{sa}) +
-                   (r_w, r_\textit{w2}, r_\textit{s1}, r_a, r_\textit{an}, r_\textit{s1w}, r_\textit{sa})  \in \ZZ^7  \]
-Let $z \gets (z_w, z_\textit{w2}, z_\textit{s1}, z_a, z_\textit{an}, z_\textit{s1w}, z_\textit{sa})$
-and $z' \gets (z \bmod \ell) \in \ZZ^7$.
-
-\item compute 
-\[  (A_q, B_q, C_q, D_q) \gets \phi\Big(
-        \lfloor z_w / \ell \rfloor, 
-        \lfloor z_\textit{w2} / \ell \rfloor, 
-        \lfloor z_\textit{s1} / \ell \rfloor, 
-        \lfloor z_a / \ell \rfloor, 
-        \lfloor z_\textit{an} / \ell \rfloor, 
-        \lfloor z_\textit{s1w} / \ell \rfloor, 
-        \lfloor z_\textit{sa} / \ell \rfloor \Big) \in \GG^3 \times \ZZ. \]
 
 \item output the signature 
-$\text{sig} = (c_1, t, \textit{chal}, \ell, A_q, B_q, C_q, D_q, z')$.
+$\mathit{sig} = (c_1, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$.
 \end{itemize}
 
-\paragraph{Algorithm $\text{verify}(c, m, \text{sig}):$}
-Verify that $\text{sig}$ is a valid signature for
-token $c$ on the message $m$.
+\paragraph{Algorithm $\text{verify}(c, m, \mathit{sig}):$}
+Verify that $\mathit{sig} = (c_1, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$ 
+is a valid signature for token~$c$ on the message~$m$.
 \begin{itemize}
-\item compute $(A_\ell, B_\ell, C_\ell, D_\ell) \gets \phi(z') \in \GG^3 \times \ZZ$.
-\item compute 
-\begin{align*}
-     A & \gets A_q^\ell \cdot A_\ell  / c_1^{\textit{chal}} \\
-     B & \gets B_q^\ell \cdot B_\ell  \\
-     C & \gets C_q^\ell \cdot C_\ell  \\
-     D & \gets D_q \cdot \ell + D_\ell - (t \cdot \textit{chal}) \\
-     \textit{PRNGkey} & \gets \text{Hash}(m, G, g, h, c, c_1, t, A, B, C, D)
-\end{align*}
+\item reject if $t \notin \range{\lambda}$ or $t$ is not a prime.
 
-\item use a PRNG seeded with $\textit{PRNGkey}$ to generate $\text{chal}'$ and
-  $\ell'$ as described in the sign algorithm. Since $\ell$ is
+\item with $T \deq (c_1, 1, 1, t) \in \GG^3 \times \ZZ$, 
+compute $\Rv' \gets \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^3 \times \ZZ$.
+
+\item compute $\mathit{seed}' \gets \text{Hash}(m, \GG, g, h, c, c_1, t, \Rv'$)
+
+\item use a $\text{PRNG}(\mathit{seed}')$ to generate 
+  $\mathit{ch}' \in \range{2^\lambda}$ and $\ell' \in \primes$. \\
+Since $\ell$ is
   included in the signature, the verifier does not need to search for
@@
 
-\item accept iff $\text{chal}' = \text{chal}$ and $\ell' = \ell$.
+\item accept iff $\mathit{ch}' = \mathit{ch}$ and $\ell' = \ell$.
 \end{itemize}
@@
 \paragraph{Comments.}
-There is a seemingly simpler method to prove that one knows the
-factorization of $n$, namely, prove that one knows $p$ such that $p$
-divides $n$.  That is, instead of committing to $w$ we would commit to
-$p$ and then prove that the committed value divides $n$. But we would
-also need to prove that the committed factor is not one of 
-$\{1, -1, n, -n\}$, and that will result in a longer proof.
-
 This scheme is only secure is a group where there are no known

### 2019-01-05 paper.tex
pre update

@@
 Generates a token $c$ to be posted on the blockchain,
-and a secret $s$ given to the recipient via a private channel
-(e.g., by posting an encryption of $s$ encrypted under $\PK$ 
-to the blockchain).
+and a secret~$s$ given to the recipient via a private channel.
+For example, an encryption of $s$ under $\PK$ can be posted
+to the blockchain.   The posted encrypted $s$ is not associated with 
+the token $c$.
 
@@
 \item $\text{verify}(c, m, \text{sig}) \to \{\text{yes},\text{no}\}:$
-Verifier that a signature $\text{sig}$ on token $c$ is valid.
+Verify that a signature $\text{sig}$ on token $c$ is valid.
 \end{itemize}
@@
 (1) $c$ and $\text{sig}$ should reveal nothing about $\PK$,
-(2) without $\SK$: existential unforgeability under a 
+(2) without $\SK$ we have existential unforgeability under a 
 (one-time) chosen message attack.
@@
 $\lambda$ is the security parameter (e.g., $\lambda = 128$), 
-$\range{\ell}$ denotes the set of integers $\{0,1,\ldots,\ell-1\}$ and 
+$\range{\ell}$ denotes the set of integers $\{0,1,\ldots,\ell-1\}$, and 
 $\primes$ is a set of size $2^\lambda$ 
@@
 
-We first develop a zero knowledge protocol for proving
-knowledge of the factorization of an integer $n$ given
-as a commitment to $n$.
-We let $N$ be a known upper bound on $n$, so that $n \in \range{N}$.
+Let $n \in \range{N}$ be a secret integer 
+where $N$ is a public upper bound on~$n$.
 For simplicity we will also assume that $\abs{\GG} < N$.
-The given commitment to $n$ is $c \deq g^n \cdot h^s \in \GG$,
+Let $c \deq g^n \cdot h^s \in \GG$ be a commitment to $n$, 
 where $s \rgets \range{N}$.  
+We first develop a zero knowledge protocol for proving knowledge of the
+factorization of~$n$ given only $c$.
 
@@
 \begin{equation} \label{eq:lang}
-  {\cal R} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
+  {\cal R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
                               (n, s, w, a) \in \range{N}^4 \Bigr)  \ \ 
@@
                         w^2 & = t + a \cdot n \ \ \text{in $\ZZ$}, \\
-                        t   & \ \textrm{a prime}
+                        2 & \leq t \leq \lambda  \ \textrm{a prime}
                 \end{split}  \right\}.
 \end{equation}
-Here $(c, t)$ is the statement and $(n, s, w, a)$ is the witness.
-The integer relation $w^2 = t + a n$ proves that 
+Here $(c, t)$ is a statement and $(n, s, w, a)$ is a witness.
+The integer relation $w^2 = t + a\cdot n$ proves that 
 $w^2 \equiv t \pmod{n}$, as required.
@@
 \medskip\noindent
-The ZKPK protocol for~\eqref{eq:lang} 
+Protocol $\prot{P}$: The ZKPK protocol for~\eqref{eq:lang} 
 between the prover $P$ and the verifier $V$ works as follows:
@@
 and $\ell \rgets \primes$. \\
-It sends $(\mathit{ch}, \ell)$ to the prover.
+It sends $(\ell, \mathit{ch})$ to the prover.
 
 \item The prover computes:
-\[  \xv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^7, \quad
-    \zv_\ell \gets (\xv \bmod \ell) \in \range{\ell}^7, \quad
-    \zv_q \gets \lfloor \xv / \ell \rfloor \in \ZZ^7, \quad
+\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^7, \quad
+    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^7, \quad
+    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^7, \quad
     \Zv_q \gets \phi(\zv_q)  
 \]
-and sends $(\Zv_q, \zv_\ell) \in \GG^3 \times \ZZ \times \range{\ell}^7$ 
+and sends $(\Zv_q, \zv_\ell) \in (\GG^3 \times \ZZ) \times \range{\ell}^7$ 
 to the verifier.
@@
 
-\paragraph{Proof of zero-knowledge.}
+\begin{theorem}
+Protocol $\prot{P}$ is a zero-knowledge protocol
+for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang}.
+\end{theorem}
 
-\paragraph{Proof of extractability.}
+\begin{proof}
+
+\end{proof}
+
+We say that ${\cal G}$ is an honest instance
+generator for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}
+if it chooses some integers $n, s, t$, and outputs $(c, t)$ where
+$c = g^n h^s \in \GG$.
+
+\begin{theorem}
+Protocol $\prot{P}$ is an argument of knowledge
+for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang} with negligible
+soundness error for instances $(c,t)$ generated by an honest instance
+generator ${\cal G}$,
+when $\GG$ is a modeled as a generic group of unknown order. 
+\end{theorem}
+
+\begin{proof}
+We construct an extractor that given an instance $(c,t)$ 
+generated by ${\cal G}$,
+interacts with a convincing prover and outputs a witness $(n, s, w, a)$ 
+for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}. 
+The protocol transcript is $(c_1, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
+The extractor rewinds the prover and obtains two
+accepting conversations
+${\cal T}_1 \deq (c_1, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
+and 
+${\cal T}_2 \deq (c_1, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
+Dividing the corresponding verification equations one by the other
+we obtain
+\[   (\Zv_q / \Zv_q')^\ell \cdot \phi(\zv_\ell - \zv_\ell') = 
+          T^{\mathit{ch} - \mathit{ch}'}. \]
+Let $\zv_\ell - \zv_\ell' = \Big(\Delta w,\ \Delta \mathit{w2},\ \Delta \mathit{s1},\ \Delta a,\ \Delta \mathit{an},\ \Delta \mathit{s1w},\ \Delta \mathit{sa} \Big) \in \ZZ^7$ and let $\Delta \mathit{ch} = \mathit{ch} - \mathit{ch}' \in \ZZ$.
+Then plugging this into the definition of $\phi$ we obtain
+\begin{equation} \label{eq:messy}
+      (\Zv_q / \Zv_q')^\ell \cdot
+      \Bigl(\ 
+       g^{\Delta w} \cdot h^{\Delta \mathit{s1}},\ \ \ 
+       g^{\Delta \mathit{w2}} \cdot h^{\Delta \mathit{s1w}} / c_1^{\Delta w},\ \ \ 
+       g^{\Delta \mathit{an}} \cdot h^{\Delta \mathit{sa}} / c^{\Delta a},\ \ \ 
+       \Delta \mathit{w2} - \Delta \mathit{an}\ \Bigr)
+          = (c_1, 1, 1, t)^{\Delta \mathit{ch}}.
+\end{equation}
+Let $\Zv_q / \Zv_q' = (z_1,z_2,z_3,z_4)$ 
+where $z_1,z_2,z_3 \in \GG$ and $z_4 \in \ZZ$.  
+In a generic group $\GG$, the group elements $z_1,z_2,z_3$ 
+must satisfy $z_i = g^{\alpha_i} h^{\beta_i} c^{\gamma_i} \prod_{j=1}^m g_j^{\delta_{i,j}}$
+for $i=1,2,3$, 
+and $c_1 = g^{\alpha} h^{\beta} c^\gamma \prod_{j=1}^m g_j^{\delta_{j}}$,
+where the extractor knows all the listed integer exponents.
+Here $g_1,\ldots,g_m$ are random group elements produced in response
+to a generic group oracle query for a random group element.
+
+It now folows from~\eqref{eq:messy}, and from $c = g^n h^s$, 
+and by uniquness of representation in generic groups,
+that the following equations must hold over the integers:
+\begin{align*}
+  \ell \cdot (\alpha_1 + n \cdot \gamma_1) + \Delta w & = (\alpha + n \cdot \gamma) \cdot \Delta \mathit{ch},  &
+  \ell \cdot (\beta_1 + s \cdot \gamma_1) + \Delta \mathit{s1} & = (\beta + s \cdot \gamma) \cdot \Delta \mathit{ch}  
+\\
+  \ell \cdot (\alpha_2 + n \cdot \gamma_2) + \Delta \mathit{w2} & = (\alpha + n \cdot \gamma) \cdot \Delta w,  &
+  \ell \cdot (\beta_2 + s \cdot \gamma_2) + \Delta \mathit{s1w} & = (\beta + s \cdot \gamma) \cdot \Delta w   
+\\
+  \ell \cdot (\alpha_3 + n \cdot \gamma_3) + \Delta \mathit{an} & = n \cdot \Delta a,  & 
+  \ell \cdot (\beta_3 + s \cdot \gamma_3) + \Delta \mathit{sa} & = s \cdot \Delta a   
+\\
+  \ell \cdot z_4 + \Delta \mathit{w2} - \Delta \mathit{an} & = t \cdot \Delta \mathit{ch} 
+\end{align*}
+The extractor knows all these values except for $n$ and $s$.
+Reducing these equations modulo $\ell$ gives:
+\begin{align}
+  \Delta w & \equiv (\alpha + n \cdot \gamma) \cdot \Delta \mathit{ch}  &
+  \Delta \mathit{s1} & \equiv (\beta + s \cdot \gamma) \cdot \Delta \mathit{ch}  & \pmod{\ell} 
+\label{eq:first} \\
+  \Delta \mathit{w2} & \equiv (\alpha + n \cdot \gamma) \cdot \Delta w  &
+  \Delta \mathit{s1w} & \equiv (\beta + s \cdot \gamma) \cdot \Delta w   & \pmod{\ell} 
+\label{eq:second} \\
+  \Delta \mathit{an} & \equiv n \cdot \Delta a  & 
+  \Delta \mathit{sa} & \equiv s \cdot \Delta a   & \pmod{\ell} 
+\label{eq:third} \\
+  \Delta \mathit{w2} - \Delta \mathit{an} & = t \cdot \Delta \mathit{ch} 
+      &&& \pmod{\ell} 
+\label{eq:fourth} 
+\end{align}
+
+Consider the left equation in~\eqref{eq:first}
+and define $w \deq \alpha + n \cdot \gamma \in \ZZ$.
+For any pair of accepting conversations such as $({\cal T}_1, {\cal T}_2)$,
+it must be the case that 
+$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$.
+The extractor knows $\Delta w$ and $\Delta \mathit{ch}$.
+Hence, by constructing a polynomial number of such accepting transcript pairs, 
+the extractor can recover $w \in \ZZ$ using the chinese remainder theorem. 
+%In the same way, the extractor can recover 
+%$s_1 \deq \beta + s \cdot \gamma \in \ZZ$  
+%from the right equation in~\eqref{eq:first}.
+
+Next, consider the left equation in~\eqref{eq:second}.
+Using $w = \alpha + n \cdot \gamma$ and
+$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ gives
+$\Delta \mathit{w2} \equiv w^2 \cdot \Delta \mathit{ch} \pmod{\ell}$.
+
+Using $\Delta \mathit{w2} \equiv w^2 \cdot \Delta \mathit{ch} \pmod{\ell}$
+in~\eqref{eq:fourth}
+gives $\Delta \mathit{an} \equiv (w^2 - t) \cdot \Delta \mathit{ch} \pmod{\ell}$. 
+Finally, the left equality in~\eqref{eq:third} 
+gives $(w^2 - t)\cdot \Delta \mathit{ch} \equiv n \cdot \Delta a \pmod{\ell}$.
+
+\end{proof}
 

### 2019-01-05 paper.tex
updated

@@
 
-\item Prover $P$ chooses a random integer $s_1 \rgets \range{N}$ and computes
-       $c_1 \gets g^w \cdot h^{s_1} \in \GG$.
+\item Prover $P$ chooses a random integers $s_1, s_2 \rgets \range{N}$ and computes
+       $c_1 \gets g^w \cdot h^{s_1} \in \GG$ and $c_2 \gets g^a \cdot h^{s_2}$.
 
-\item Next, define a homomorphism $\phi:\ZZ^7 \to \GG^3 \times \ZZ$ as follows:
+\item Next, define a homomorphism $\phi:\ZZ^8 \to \GG^4 \times \ZZ$ 
+parameterized by $g, h, c, c_1, c_2$ as follows:
 \begin{equation} \label{eq:hom}
-  \phi(w, \mathit{w2}, s_1, a, \mathit{an}, \mathit{s1w}, \mathit{sa}) \deq
+  \phi\left(\!\!\!\begin{array}{l}
+                w, \mathit{w2}, s_1, a, \\
+                \mathit{an}, \mathit{s1w}, \mathit{sa}, s_2
+      \end{array}  \!\!\!\right) \deq
       \Bigl(\ 
        g^w \cdot h^{\mathit{s1}},\ \ \ 
+       g^a \cdot h^{\mathit{s2}},\ \ \ 
        g^{\mathit{w2}} \cdot h^{\mathit{s1w}} / c_1^w,\ \ \ 
@@
 It is easy to see that $\phi$ is a group homomorphism.
-The range of $\phi$ is the group $\GG^3 \times \ZZ$.  
+The range of $\phi$ is the group $\GG^4 \times \ZZ$.  
 We will write the group operation in this group multiplicatively.
-That is, if $(a_i, b_i, c_i, d_i) \in \GG^3 \times \ZZ$ for $i=1,2$
+That is, if $(a_i, b_i, c_i, d_i, e_i) \in \GG^4 \times \ZZ$ for $i=1,2$
 then 
-\[  (a_1, b_1, c_1, d_1) \cdot (a_2, b_2, c_2, d_2) \deq 
-      (a_1 a_2,\ b_1 b_2,\ c_1 c_2,\ d_1 + d_2).  \]
+\[  (a_1, b_1, c_1, d_1, e_1) \cdot (a_2, b_2, c_2, d_2, e_2) \deq 
+      (a_1 a_2,\ b_1 b_2,\ c_1 c_2,\ d_1 d_2,\ e_1 + e_2).  \]
 
 We need a ZKPK for a $\phi$-preimage of 
-$T \deq (c_1, 1, 1, t) \in \GG^3 \times \ZZ$. 
+$T \deq (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ$. 
 In other words, we need a zero-knowledge proof of knowledge for a vector 
 $\vv' = (w', \mathit{w2}', s_1', a', \mathit{an}', 
-              \mathit{s1w}', \mathit{sa}') \in \ZZ^7$ 
+              \mathit{s1w}', \mathit{sa}', s_2') \in \ZZ^8$ 
 such that 
-\[   \phi(\vv') = T = (c_1, 1, 1, t) \in \GG^3 \times \ZZ.  \]
+\[   \phi(\vv') = T = (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ.  \]
 Doing so proves 
 that $c_1$ is a commitment to $w' \in \ZZ$, 
+that $c_2$ is a commitment to $a' \in \ZZ$,
 that $\mathit{w2}' = (w')^2$, and 
@@
 \begin{enumerate}
-\item The prover chooses a random $\rv \rgets \range{N}^7$
-and computes $\Rv \gets \phi(\rv) \in \GG^3 \times \ZZ$. \\
-It sends $(c_1, \Rv)$ to the verifier.
+\item The prover chooses a random $\rv \rgets \range{N}^8$
+and computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$. \\
+It sends $(c_1, c_2, \Rv)$ to the verifier.
 
@@
 \item The prover computes:
-\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^7, \quad
-    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^7, \quad
-    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^7, \quad
+\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
+    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^8, \quad
+    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^8, \quad
     \Zv_q \gets \phi(\zv_q)  
 \]
-and sends $(\Zv_q, \zv_\ell) \in (\GG^3 \times \ZZ) \times \range{\ell}^7$ 
+and sends $(\Zv_q, \zv_\ell) \in (\GG^4 \times \ZZ) \times \range{\ell}^8$ 
 to the verifier.
@@
 $\ \Zv_q^\ell \cdot \phi(\zv_\ell) = T^\mathit{ch} \cdot \Rv\ $ in 
-$\GG^3 \times \ZZ$.
+$\GG^4 \times \ZZ$.
 \end{enumerate}
@@
 
-\paragraph{Comment.}
+\paragraph{Comment 1.}
+The commitment $c_2$ to the integer $a$ is necessary for soundness,
+and in particular to ensure that $a$ is an integer.  If $c_2$ along
+with $s_2$ and the second coordinate of $\phi$ are eliminated then there
+is an attack where an adversarial prover can prove knowledge of
+$(\sqrt{3} \bmod n)$ using $a = 1/n$ and $w = 2$.
+
+\paragraph{Comment 2.}
 There is a seemingly simpler method to prove that one knows the
@@
 generator for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}
-if it chooses some integers $n, s, t$, and outputs $(c, t)$ where
-$c = g^n h^s \in \GG$.
+if it chooses integers $n, s, t$, and outputs $(c, t)$ where
+$c \deq g^n h^s \in \GG$.
 
@@
 for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}. 
-The protocol transcript is $(c_1, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
+The protocol transcript is $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
 The extractor rewinds the prover and obtains two
-accepting conversations
-${\cal T}_1 \deq (c_1, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
+accepting transcripts
+${\cal T}_1 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
 and 
-${\cal T}_2 \deq (c_1, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
+${\cal T}_2 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
 Dividing the corresponding verification equations one by the other
@@
           T^{\mathit{ch} - \mathit{ch}'}. \]
-Let $\zv_\ell - \zv_\ell' = \Big(\Delta w,\ \Delta \mathit{w2},\ \Delta \mathit{s1},\ \Delta a,\ \Delta \mathit{an},\ \Delta \mathit{s1w},\ \Delta \mathit{sa} \Big) \in \ZZ^7$ and let $\Delta \mathit{ch} = \mathit{ch} - \mathit{ch}' \in \ZZ$.
+Let $\zv_\ell - \zv_\ell' = \Big(\Delta w,\ \Delta \mathit{w2},\ \Delta \mathit{s1},\ \Delta a,\ \Delta \mathit{an},\ \Delta \mathit{s1w},\ \Delta \mathit{sa},\ \Delta \mathit{s2} \Big) \in \ZZ^8$ and let $\Delta \mathit{ch} = \mathit{ch} - \mathit{ch}' \in \ZZ$.
 Then plugging this into the definition of $\phi$ we obtain
@@
        g^{\Delta w} \cdot h^{\Delta \mathit{s1}},\ \ \ 
+       g^{\Delta a} \cdot h^{\Delta \mathit{s2}},\ \ \ 
        g^{\Delta \mathit{w2}} \cdot h^{\Delta \mathit{s1w}} / c_1^{\Delta w},\ \ \ 
@@
        \Delta \mathit{w2} - \Delta \mathit{an}\ \Bigr)
-          = (c_1, 1, 1, t)^{\Delta \mathit{ch}}.
+          = (c_1, c_2, 1, 1, t)^{\Delta \mathit{ch}}.
 \end{equation}
-Let $\Zv_q / \Zv_q' = (z_1,z_2,z_3,z_4)$ 
-where $z_1,z_2,z_3 \in \GG$ and $z_4 \in \ZZ$.  
-In a generic group $\GG$, the group elements $z_1,z_2,z_3$ 
+Let $\Zv_q / \Zv_q' = (z_1, z_2, z_3, z_4, z_5)$ 
+where $z_1, z_2, z_3, z_4 \in \GG$ and $z_5 \in \ZZ$.  
+In a generic group $\GG$, the group elements $z_1, z_2, z_3, z_4$ 
 must satisfy $z_i = g^{\alpha_i} h^{\beta_i} c^{\gamma_i} \prod_{j=1}^m g_j^{\delta_{i,j}}$
-for $i=1,2,3$, 
+for $i=1,2,3,4$, 
 and $c_1 = g^{\alpha} h^{\beta} c^\gamma \prod_{j=1}^m g_j^{\delta_{j}}$,
+and $c_2 = g^{\alpha_0} h^{\beta_0} c^\gamma \prod_{j=1}^m g_j^{\delta_{0,j}}$,
 where the extractor knows all the listed integer exponents.
@@
 
-It now folows from~\eqref{eq:messy}, and from $c = g^n h^s$, 
-and by uniquness of representation in generic groups,
+It now follows from~\eqref{eq:messy}, and from $c = g^n h^s$, 
+and by uniqueness of representation in generic groups,
 that the following equations must hold over the integers:
@@
 \\
-  \ell \cdot (\alpha_2 + n \cdot \gamma_2) + \Delta \mathit{w2} & = (\alpha + n \cdot \gamma) \cdot \Delta w,  &
-  \ell \cdot (\beta_2 + s \cdot \gamma_2) + \Delta \mathit{s1w} & = (\beta + s \cdot \gamma) \cdot \Delta w   
+  \ell \cdot (\alpha_2 + n \cdot \gamma_2) + \Delta a & = (\alpha_0 + n \cdot \gamma_0) \cdot \Delta \mathit{ch},  &
+  \ell \cdot (\beta_2 + s \cdot \gamma_2) + \Delta \mathit{s2} & = (\beta_0 + s \cdot \gamma_0) \cdot \Delta \mathit{ch}  
 \\
-  \ell \cdot (\alpha_3 + n \cdot \gamma_3) + \Delta \mathit{an} & = n \cdot \Delta a,  & 
-  \ell \cdot (\beta_3 + s \cdot \gamma_3) + \Delta \mathit{sa} & = s \cdot \Delta a   
+  \ell \cdot (\alpha_3 + n \cdot \gamma_3) + \Delta \mathit{w2} & = (\alpha + n \cdot \gamma) \cdot \Delta w,  &
+  \ell \cdot (\beta_3 + s \cdot \gamma_3) + \Delta \mathit{s1w} & = (\beta + s \cdot \gamma) \cdot \Delta w   
+\\
+  \ell \cdot (\alpha_4 + n \cdot \gamma_4) + \Delta \mathit{an} & = n \cdot \Delta a,  & 
+  \ell \cdot (\beta_4 + s \cdot \gamma_4) + \Delta \mathit{sa} & = s \cdot \Delta a   
 \\
@@
 \label{eq:first} \\
+  \Delta a & \equiv (\alpha_0 + n \cdot \gamma_0) \cdot \Delta \mathit{ch}  &
+  \Delta \mathit{s2} & \equiv (\beta_0 + s \cdot \gamma_0) \cdot \Delta \mathit{ch}  & \pmod{\ell} 
+\label{eq:firsta} \\
   \Delta \mathit{w2} & \equiv (\alpha + n \cdot \gamma) \cdot \Delta w  &
@@
 \label{eq:third} \\
-  \Delta \mathit{w2} - \Delta \mathit{an} & = t \cdot \Delta \mathit{ch} 
+  \Delta \mathit{w2} - \Delta \mathit{an} & \equiv t \cdot \Delta \mathit{ch} 
       &&& \pmod{\ell} 
@@
 and define $w \deq \alpha + n \cdot \gamma \in \ZZ$.
-For any pair of accepting conversations such as $({\cal T}_1, {\cal T}_2)$,
+For any pair of accepting transcripts such as $({\cal T}_1, {\cal T}_2)$,
 it must be the case that 
@@
 the extractor can recover $w \in \ZZ$ using the chinese remainder theorem.
-%In the same way, the extractor can recover 
-%$s_1 \deq \beta + s \cdot \gamma \in \ZZ$  
-%from the right equation in~\eqref{eq:first}.
+
+In exactly the same way, the extractor can recover 
+$a \deq \alpha_0 + n \cdot \gamma_0 \in \ZZ$  
+from the left equation in~\eqref{eq:firsta}.
+For any pair of accepting transcripts 
+it must be the case that 
+$\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$.
 
@@
 gives $(w^2 - t)\cdot \Delta \mathit{ch} \equiv n \cdot \Delta a \pmod{\ell}$.
-
+Using $\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$
+we obtain that the extracted integers $w$ and $a$ must satisfy
+$(w^2 - t)\cdot \Delta \mathit{ch} \equiv 
+      n \cdot a \cdot \Delta \mathit{ch} \pmod{\ell}$.  
+Since $\ell$ does not divide $\Delta \mathit{ch}$ with overwhelming
+probability we obtain that $w^2 - t \equiv n \cdot a \pmod{\ell}$.
+Since this equality holds modulo a random $\ell \in \primes$ 
+with overwhelming probability, 
+the equality $w^2 - t = n \cdot a$ must hold over the integers,
+as required. 
 \end{proof}
@@
 To withdraw the funds associated with the token $c$ the user
-signs a withdrawl message $m$ using the RSA secret key $\SK = (n,p,q)$ 
+signs a withdrawal message $m$ using the RSA secret key $\SK = (n,p,q)$ 
 as follows:
@@
 signature just given $c$ and $m$, and 
-(2) security: an attacker that can generate a valid siganture for $c$ using
+(2) security: an attacker that can generate a valid signature for $c$ using
 some message $m' \neq m$ can be used to compute $\sqrt{t} \in \ZZ_n$

### 2019-01-05 paper.tex
edits

@@
 
+\subsection{Zero-knowledge proofs in generic groups}
+
+Let $\adv$ be an algorithm that outputs 
+a generic group element $u \in \GG$.
+The following lemma shows that there is an extractor that
+can extract from $\adv$ an integer representation of $u$
+relative to a supplied set of group generators.
+Moreover, this integer representation is unique.
+
+\begin{lemma}[Uniqueness of representation in generic groups]
+\label{lem:unique}
+Let $\adv_1, \adv_2$ be two randomized algorithms that interact
+with generic group oracles for the group $\GG$ and 
+output $u_1, u_2 \in \GG$, respectively. 
+Suppose that each algorithm makes at most $q$ type-1 queries
+and let $g_1,\ldots,g_q \in \GG$ be the returned random group elements.
+
+There is an extractor $\bdv$ that emulates 
+the generic group oracles for $\adv_1$ and $\adv_2$, 
+and for $i=1,2$ when $\bdv$ interacts with $\adv_i$ 
+the following holds with overwhelming probability:
+if $\adv_i$ outputs $u_i \in \GG$ 
+then the extractor $\bdv_i$ outputs a representation
+$\alpha_{i,1},\ldots,\alpha_{i,q} \in \ZZ$
+such that $u_i = g_1^{\alpha_{i,1}} \cdots g_q^{\alpha_{i,q}}$.
+Moreover, if $u_1 = u_2$ then the two representations are the same,
+namely $\alpha_{1,j} = \alpha_{2,j}$ for $j=1,\ldots,q$. 
+\end{lemma}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 where $N$ is a public upper bound on~$n$.
-For simplicity we will also assume that $\abs{\GG} < N$.
+For simplicity we will also assume that $\abs{\GG} < N/2^{2 \lambda}$.
 Let $c \deq g^n \cdot h^s \in \GG$ be a commitment to $n$, 
@@
 \begin{proof}
+The simulator takes $(c, t)$ as input and outputs the simulated transcript
+$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
+\begin{alg}
+choose random $c_1, c_2 \rgets \GG$ and $\ell \rgets \primes$, 
+$\mathit{ch} \rgets \range{2^\lambda}$, \\
+choose random $\zv_\ell \rgets \range{\ell}^8$, \\
+choose random $Z_1,Z_2,Z_3,Z_4 \rgets \GG$,\  $Z_5 \rgets \range{N}$,\ 
+and set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5) \in \GG^4 \times \ZZ$, \\
+compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$. 
+\end{alg}
+We show the simulated transcript is distributed statistically close
+to an accepting transcript of a real protocol execution.
+First observe that $c_1, c_2, \Rv, \ell, \mathit{ch}$ are all distributed 
+as in a real transcript.  It remains to show that the same holds
+for $\zv_\ell$ and $\Zv_q$. 
+In an interaction with a real prover 
+the vector $\rv$ is chosen uniformly in $\range{N}^8$.
+Consider one value $r \rgets \range{N}$.
+Because $N$ is much larger than $\ell \cdot \abs{\GG}$
+we know that the pair 
+$\big((\lfloor r/\ell \rfloor \bmod \abs{\GG}),\ (r \bmod \ell) \big)$
+is statistically close to uniform in $\range{\abs{\GG}} \times \range{\ell}$.
+It follows that $\zv_\ell$ is statistically close to uniform 
+in $\range{\ell}^8$ and 
+$Z_1,Z_2,Z_3,Z_4 \in \GG$ are statistically close to uniform in $\GG$, 
+as in the simulation.
+It remains to argue that $Z_5$ is simulated correctly.
 
@@
 It now follows from~\eqref{eq:messy}, and from $c = g^n h^s$, 
-and by uniqueness of representation in generic groups,
+and by uniqueness of representation in generic groups (\Lemma{lem:unique}),
 that the following equations must hold over the integers:

### 2019-01-06 paper.tex
edits

@@
 
-Informal security properties: 
+TODO: Need to state security properties formally: 
 (1) $c$ and $\text{sig}$ should reveal nothing about $\PK$,
@@
 
+TODO: Need overview of zero-knowledge in generic groups.
+
+\paragraph{The representation extraction lemma.}
 Let $\adv$ be an algorithm that outputs 
@@
 
-\begin{lemma}[Uniqueness of representation in generic groups]
+\begin{lemma}[Unique representation extraction in generic groups]
 \label{lem:unique}
@@
 There is an extractor $\bdv$ that emulates 
-the generic group oracles for $\adv_1$ and $\adv_2$, 
-and for $i=1,2$ when $\bdv$ interacts with $\adv_i$ 
+the generic group oracles for $\adv_1$ and $\adv_2$
+such that for $i=1,2$ when $\bdv$ interacts with $\adv_i$ 
 the following holds with overwhelming probability:
@@
 \begin{equation} \label{eq:hom}
-  \phi\left(\!\!\!\begin{array}{l}
+  \phi\left(\!\!\begin{array}{l}
                 w, \mathit{w2}, s_1, a, \\
@@
 \begin{alg}
-choose random $c_1, c_2 \rgets \GG$ and $\ell \rgets \primes$, 
-$\mathit{ch} \rgets \range{2^\lambda}$, \\
-choose random $\zv_\ell \rgets \range{\ell}^8$, \\
-choose random $Z_1,Z_2,Z_3,Z_4 \rgets \GG$,\  $Z_5 \rgets \range{N}$,\ 
-and set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5) \in \GG^4 \times \ZZ$, \\
+choose random $c_1, c_2 \rgets \GG,\ \ \ell \rgets \primes$, and
+$\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
+choose random $\zv_\ell \rgets \range{\ell}^8$ 
+and random $Z_1,Z_2,Z_3,Z_4 \rgets \GG$ \AlgSep
+choose $r_\text{w2}, r_\text{an} \rgets \range{N}$ and
+set $Z_5 \gets \lfloor (r_\text{w2} - r_\text{an}) / \ell \rfloor \in \ZZ$, \AlgSep
+set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5) \in \GG^4 \times \ZZ$, \AlgSep
 compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$. 
@@
 $\big((\lfloor r/\ell \rfloor \bmod \abs{\GG}),\ (r \bmod \ell) \big)$
-is statistically close to uniform in $\range{\abs{\GG}} \times \range{\ell}$.
-It follows that $\zv_\ell$ is statistically close to uniform 
-in $\range{\ell}^8$ and 
-$Z_1,Z_2,Z_3,Z_4 \in \GG$ are statistically close to uniform in $\GG$, 
-as in the simulation.
+is statistically close to uniform in $\range{\,\abs{\GG}\,} \times \range{\ell}$.
+It directly follows that $\zv_\ell$ is statistically close to uniform 
+in $\range{\ell}^8$, as in the simulation.
+It also follows that $Z_1,Z_2,Z_3,Z_4 \in \GG$ are statistically close to 
+uniform in $\GG$ because each of these four terms is randomized by
+a fresh uniform randomizer,
+$r_\text{s1}, r_\text{s2}, r_\text{w}, r_\text{a} \in \range{\,\abs{\GG}\,}$ respectively. 
+Hence, these values are distributed as in
+the simulation.
 It remains to argue that $Z_5$ is simulated correctly. 
-
+In the real protocol $Z_5$ is equal to
+$\lfloor (t \cdot \mathit{ch} + r_\text{w2} - r_\text{an})/\ell \rfloor \in \ZZ$
+plus or minus one.
+Note that $(t \cdot \mathit{ch})/\ell$ is negligibly small compared
+to $(r_\text{w2} - r_\text{an})/\ell$.
+Hence, because in the real transcript $r_\text{w2}$ and $r_\text{an}$ 
+are fresh uniform values in $\range{N}$, this $Z_5$ is distributed 
+statistically close to its distribution in the simulation.
 \end{proof}
@@
       (\Zv_q / \Zv_q')^\ell \cdot
-      \Bigl(\ 
+      \left(\begin{array}{l}
        g^{\Delta w} \cdot h^{\Delta \mathit{s1}},\ \ \ 
        g^{\Delta a} \cdot h^{\Delta \mathit{s2}},\ \ \ 
-       g^{\Delta \mathit{w2}} \cdot h^{\Delta \mathit{s1w}} / c_1^{\Delta w},\ \ \ 
+       g^{\Delta \mathit{w2}} \cdot h^{\Delta \mathit{s1w}} / c_1^{\Delta w}, \\
        g^{\Delta \mathit{an}} \cdot h^{\Delta \mathit{sa}} / c^{\Delta a},\ \ \ 
-       \Delta \mathit{w2} - \Delta \mathit{an}\ \Bigr)
-          = (c_1, c_2, 1, 1, t)^{\Delta \mathit{ch}}.
+       \Delta \mathit{w2} - \Delta \mathit{an}\ 
+       \end{array} \right)
+          = \left(\begin{array}{l}c_1, \ c_2, \ 1, \\ 1,\ t \end{array}\right)^{\Delta \mathit{ch}}.
 \end{equation}
@@
 In a generic group $\GG$, the group elements $z_1, z_2, z_3, z_4$ 
-must satisfy $z_i = g^{\alpha_i} h^{\beta_i} c^{\gamma_i} \prod_{j=1}^m g_j^{\delta_{i,j}}$
+must satisfy $z_i = g^{\alpha_i} h^{\beta_i} c^{\gamma_i} \prod_{j=1}^q g_j^{\delta_{i,j}}$
 for $i=1,2,3,4$, 
-and $c_1 = g^{\alpha} h^{\beta} c^\gamma \prod_{j=1}^m g_j^{\delta_{j}}$,
-and $c_2 = g^{\alpha_0} h^{\beta_0} c^\gamma \prod_{j=1}^m g_j^{\delta_{0,j}}$,
+and $c_1 = g^{\alpha} h^{\beta} c^\gamma \prod_{j=1}^q g_j^{\delta_{j}}$,
+and $c_2 = g^{\alpha_0} h^{\beta_0} c^\gamma \prod_{j=1}^q g_j^{\delta_{0,j}}$,
 where the extractor knows all the listed integer exponents.
-Here $g_1,\ldots,g_m$ are random group elements produced in response
+Here $g_1,\ldots,g_q \in \GG$ are random group elements produced in response
 to a generic group oracle query for a random group element.
@@
 
-Consider the left equation in~\eqref{eq:first}
-and define $w \deq \alpha + n \cdot \gamma \in \ZZ$.
+Consider the left equalities in~\eqref{eq:first} and~\eqref{eq:firsta}.
+Define $w \deq \alpha + n \cdot \gamma \in \ZZ$ 
+and $a \deq \alpha_0 + n \cdot \gamma_0 \in \ZZ$.
 For any pair of accepting transcripts such as $({\cal T}_1, {\cal T}_2)$,
 it must be the case that 
-$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$.
-The extractor knows $\Delta w$ and $\Delta \mathit{ch}$.
+$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ and
+$\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$. 
+The extractor knows $\Delta w,\ \Delta a$, and $\Delta \mathit{ch}$.
 Hence, by constructing a polynomial number of such accepting transcript pairs, 
-the extractor can recover $w \in \ZZ$ using the chinese remainder theorem.
-
-In exactly the same way, the extractor can recover 
-$a \deq \alpha_0 + n \cdot \gamma_0 \in \ZZ$  
-from the left equation in~\eqref{eq:firsta}.
-For any pair of accepting transcripts 
-it must be the case that 
-$\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$.
+the extractor can recover $w, a \in \ZZ$ using the chinese remainder theorem.
 
@@
 Since $\ell$ does not divide $\Delta \mathit{ch}$ with overwhelming
-probability we obtain that $w^2 - t \equiv n \cdot a \pmod{\ell}$.
+probability, we obtain that $w^2 - t \equiv n \cdot a \pmod{\ell}$.
 Since this equality holds modulo a random $\ell \in \primes$ 
@@
 the equality $w^2 - t = n \cdot a$ must hold over the integers,
-as required. 
+as required.   Note that this implies that $a \neq 0$.
+
+Because $a \neq 0$, the extractor can obtain $(n \bmod \ell)$
+from the left equality in~\eqref{eq:third}, and thus extract $n \in \ZZ$ by
+repeating over several $\ell$.  Similarly, it can extract $s \in \ZZ$ from
+the right equality in~\eqref{eq:third}.   
+It thus obtains a witness $(n, s, w, a)$ 
+for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}, as required.
 \end{proof}
@@
 
-\item choose a random $\rv \rgets \range{N}^7$
-and compute $\Rv \gets \phi(\rv) \in \GG^3 \times \ZZ$.
+\item choose a random $s_2 \rgets \range{N}$ and compute
+           $c_2 \gets g^a \cdot h^{s_2} \in \GG$.
 
-\item compute $\mathit{seed} \gets \text{Hash}(m, \GG, g, h, c, c_1, t, \Rv$).
+\item choose a random $\rv \rgets \range{N}^8$
+and compute $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$.
+
+\item compute $\mathit{seed} \gets \text{Hash}(m, \GG, g, h, c, c_1, c_2, t, \Rv$).
 
@@
 \item compute:
-\[  \xv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^7, \quad
-    \zv_\ell \gets (\xv \bmod \ell) \in \range{\ell}^7, \quad
-    \zv_q \gets \lfloor \xv / \ell \rfloor \in \ZZ^7, \quad
-    \Zv_q \gets \phi(\zv_q) \in \GG^3 \times \ZZ.
+\[  \xv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
+    \zv_\ell \gets (\xv \bmod \ell) \in \range{\ell}^8, \quad
+    \zv_q \gets \lfloor \xv / \ell \rfloor \in \ZZ^8, \quad
+    \Zv_q \gets \phi(\zv_q) \in \GG^4 \times \ZZ.
 \]
@@
 \item output the signature 
-$\mathit{sig} = (c_1, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$.
+$\mathit{sig} = (c_1, c_2, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$.
 \end{itemize}
@@
 \paragraph{Algorithm $\text{verify}(c, m, \mathit{sig}):$}
-Verify that $\mathit{sig} = (c_1, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$ 
+Verify that $\mathit{sig} = (c_1, c_2, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$ 
 is a valid signature for token~$c$ on the message~$m$.
@@
 
-\item with $T \deq (c_1, 1, 1, t) \in \GG^3 \times \ZZ$, 
-compute $\Rv' \gets \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^3 \times \ZZ$.
+\item with $T \deq (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ$, 
+compute $\Rv' \gets \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$.
 
-\item compute $\mathit{seed}' \gets \text{Hash}(m, \GG, g, h, c, c_1, t, \Rv'$)
+\item compute $\mathit{seed}' \gets \text{Hash}(m, \GG, g, h, c, c_1, c_2, t, \Rv'$)
 
@@
 We need to prove two things: 
-(1) privacy: there is a simulator that can generate a properly distributed
+(1) privacy in the random oracle model:
+there is a simulator that can generate a properly distributed
 signature just given $c$ and $m$, and 
-(2) security: an attacker that can generate a valid signature for $c$ using
+(2) security: an attacker that is given $c$ along with a 
+signature on some message $m$
+with respect to $c$ and can generate a valid signature for $c$ on
 some message $m' \neq m$ can be used to compute $\sqrt{t} \in \ZZ_n$
@@
 \paragraph{Proof of privacy.}
+TODO: Use the ZK proof of the interactive protocol.
 
 \paragraph{Proof of security.}
+TODO: Use the extractor of the interactive protocol.
 

### 2019-01-06 paper.tex
edits

@@
 where $N$ is a public upper bound on~$n$.
-For simplicity we will also assume that $\abs{\GG} < N/2^{2 \lambda}$.
+We will also assume that $N > \abs{\GG} \cdot 2^{2 \lambda}$.
 Let $c \deq g^n \cdot h^s \in \GG$ be a commitment to $n$, 
@@
 \paragraph{Comment 1.}
+The protocol is insecure if the group $\GG$ contains a non-identity
+element of known order.  In the multiplicative group $(\ZZ/n)^*$ the
+element $-1$ has order~$2$, and hence the protocol is insecure in this
+group.  Instead, we can work in the quotient group $(\ZZ/n)/\{\pm 1\}$, 
+where elements are represented as integers in the interval $[1,n/2]$
+and the product of $x$ and $y$ is defined as 
+$\abs{x \cdot y} = \min(z, n-z)$ where $z = (x \cdot y \bmod n)$.
+In this group $-1$ is the same as $1$, and presumably there are
+no other known elements of known order.
+
+\paragraph{Comment 2.}
 The commitment $c_2$ to the integer $a$ is necessary for soundness,
@@
 
-\paragraph{Comment 2.}
+\paragraph{Comment 3.}
 There is a seemingly simpler method to prove that one knows the
@@
 divides $n$.  That is, instead of committing to $w$ we would commit to
-$p$ and then prove that the committed value divides $n$. But we would
-also need to prove that the committed factor is not one of 
+$p$ and $q$ and then prove that $p \cdot q = n$. But we would
+also need to prove that the committed $p$ is not one of 
 $\{1, -1, n, -n\}$, and that results in a longer proof.
@@
 choose $r_\text{w2}, r_\text{an} \rgets \range{N}$ and
-set $Z_5 \gets \lfloor (r_\text{w2} - r_\text{an}) / \ell \rfloor \in \ZZ$, \AlgSep
+set $Z_5 \gets \lfloor (t \cdot \mathit{ch} + r_\text{w2} - r_\text{an}) / \ell \rfloor \in \ZZ$, \AlgSep
 set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5) \in \GG^4 \times \ZZ$, \AlgSep
@@
 a fresh uniform randomizer,
-$r_\text{s1}, r_\text{s2}, r_\text{w}, r_\text{a} \in \range{\,\abs{\GG}\,}$ respectively. 
+$h^{\lfloor r_\text{s1} / \ell \rfloor}, h^{\lfloor r_\text{s2} / \ell \rfloor}, h^{\lfloor r_\text{s1w} / \ell \rfloor}, h^{\lfloor r_\text{sa} / \ell \rfloor} \in \GG$ respectively. 
 Hence, these values are distributed as in
@@
 In the real protocol $Z_5$ is equal to
-$\lfloor (t \cdot \mathit{ch} + r_\text{w2} - r_\text{an})/\ell \rfloor \in \ZZ$
-plus or minus one.
-Note that $(t \cdot \mathit{ch})/\ell$ is negligibly small compared
-to $(r_\text{w2} - r_\text{an})/\ell$.
-Hence, because in the real transcript $r_\text{w2}$ and $r_\text{an}$ 
-are fresh uniform values in $\range{N}$, this $Z_5$ is distributed 
+$\lfloor (t \cdot \mathit{ch} + r_\text{w2} - r_\text{an})/\ell \rfloor \in \ZZ$,
+possibly plus or minus one.
+Hence, because in the real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
+and $\lfloor r_\text{an} / \ell \rfloor$ 
+are fresh uniform values in $\range{N/\ell}$, this $Z_5$ is distributed 
 statistically close to its distribution in the simulation.
@@
 
-We say that ${\cal G}$ is an honest instance
-generator for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}
+An optimization: the transcript elements $Z_3, Z_4 \in \GG$ can be simulated
+in a similar fashion to how we simulated $Z_5$ in the proof above.
+That is, 
+$Z_3 = g^{\lfloor r_\text{w2} / \ell \rfloor} h^{\lfloor r_\text{s1w} / \ell \rfloor} / c_1^{\lfloor r_\text{w} / \ell \rfloor} \in \GG$
+and 
+$Z_4 = g^{\lfloor r_\text{an} / \ell \rfloor} h^{\lfloor r_\text{sa} / \ell \rfloor} / c^{\lfloor r_\text{a} / \ell \rfloor} \in \GG$,
+where 
+$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{an}, r_\text{s1w}, r_\text{sa}$
+are chosen uniformly in $\range{N}$. 
+It is not difficult to see that these $Z_3$ and $Z_4$ 
+are distributed as in a real transcript.
+This method of simulation can be used to make the protocol slightly more
+efficient because the randomizers 
+$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{an}, r_\text{s1w}, r_\text{sa} \in \ZZ$
+do not need to be uniform in the entire interval $\range{N}$.
+It suffices to choose these six values 
+uniformly in $\range{2^{2 \lambda}}$, which is a smaller interval
+than $\range{N}$.  Only $r_\text{s1}$ and $r_\text{s2}$ need to be chosen
+uniformly in the full interval $\range{N}$ so that $Z_1$ and $Z_2$ are uniform
+in $\GG$. 
+However, if the simulator chooses $c_1, c_2 \in \GG$ randomly in $\GG$
+so that it knows
+their $\ell$-th root, then even $Z_1$ and $Z_2$ can also be simulated as above.
+Then $r_\text{s1}$ and $r_\text{s2}$ can also be chosen uniformly
+in the range $\range{2^{2 \lambda}}$.
+In other words, the simulator works by first 
+choosing a random $\rv \gets \range{2^{2\lambda}}^8$,
+computing $\Rv \gets \phi(\rv)$, and then
+solving for $\Zv_q \in \GG^4 \times \ZZ$.
+
+\begin{definition}
+We say that algorithm ${\cal G}$ is an \defn{honest instance
+generator} for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}
 if it chooses integers $n, s, t$, and outputs $(c, t)$ where
 $c \deq g^n h^s \in \GG$. 
+\end{definition}
 
@@
 Protocol $\prot{P}$ is an argument of knowledge
-for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang} with negligible
-soundness error for instances $(c,t)$ generated by an honest instance
+for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang} 
+for instances $(c,t)$ generated by an honest instance
 generator ${\cal G}$,
-when $\GG$ is a modeled as a generic group of unknown order. 
+when the group $\GG$ is a modeled as a generic group of unknown order. 
 \end{theorem}
@@
 \item choose a random $\rv \rgets \range{N}^8$
-and compute $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$.
+and compute $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$,
+where $\phi$ is the homomrphism defined in~\eqref{eq:hom}.
 
@@
 
-\paragraph{Comments.}
-This scheme is only secure is a group where there are no known
-elements of low order.  The group $\ZZ/n$ is not such a group because
-of the element $-1$ of order $2$.  To eliminate this element we work
-in the quotient group $(\ZZ/n)/\{\pm 1\}$, representing elements as
-$\abs{x} = \min(x, n - x)$.  In this group $-1$ is the same as $1$,
-and presumably there are no other known elements of known order.
-
 \paragraph{Proof of security.}
@@
 \paragraph{Proof of privacy.}
-TODO: Use the ZK proof of the interactive protocol.
+TODO: Use the ZK proof of the interactive protocol. Easy corrolary.
 
 \paragraph{Proof of security.}
-TODO: Use the extractor of the interactive protocol.
+TODO: Use the extractor of the interactive protocol. Easy corrolary.
 
@@
 \section{A private air drop to ElGamal public keys}
+
+TODO: needs to be written.  Maybe put this first because it is so much
+simpler?
 

### 2019-01-07 paper.tex
edits

@@
                 w, \mathit{w2}, s_1, a, \\
-                \mathit{an}, \mathit{s1w}, \mathit{sa}, s_2
+                \mathit{na}, \mathit{s1w}, \mathit{sa}, s_2
       \end{array}  \!\!\!\right) \deq
@@
        g^{\mathit{w2}} \cdot h^{\mathit{s1w}} / c_1^w,\ \ \ 
-       g^{\mathit{an}} \cdot h^{\mathit{sa}} / c^a,\ \ \ 
-       \mathit{w2} - \mathit{an}\ \Bigr)
+       g^{\mathit{na}} \cdot h^{\mathit{sa}} / c^a,\ \ \ 
+       \mathit{w2} - \mathit{na}\ \Bigr)
 \end{equation}
@@
 In other words, we need a zero-knowledge proof of knowledge for a vector 
-$\vv' = (w', \mathit{w2}', s_1', a', \mathit{an}', 
+$\vv' = (w', \mathit{w2}', s_1', a', \mathit{na}', 
               \mathit{s1w}', \mathit{sa}', s_2') \in \ZZ^8$ 
@@
 that $\mathit{w2}' = (w')^2$, and 
-that $\mathit{an}' = a' \cdot n$ for some integer $a'$.
+that $\mathit{na}' = a' \cdot n$ for some integer $a'$.
 Then the last relation proves that $(w')^2 - a' \cdot n = t$ in $\ZZ$,
@@
 \begin{enumerate}
-\item The prover chooses a random $\rv \rgets \range{N}^8$
+\item The prover chooses a random $\rv \rgets \range{2^{2\lambda}}^8$
 and computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$. \\
@@
 \begin{alg}
-choose random $c_1, c_2 \rgets \GG,\ \ \ell \rgets \primes$, and
+choose random $\hat{c}_1, \hat{c}_2 \rgets \GG,\ \ \ell \rgets \primes$, and
 $\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
-choose random $\zv_\ell \rgets \range{\ell}^8$ 
-and random $Z_1,Z_2,Z_3,Z_4 \rgets \GG$ \AlgSep
-choose $r_\text{w2}, r_\text{an} \rgets \range{N}$ and
-set $Z_5 \gets \lfloor (t \cdot \mathit{ch} + r_\text{w2} - r_\text{an}) / \ell \rfloor \in \ZZ$, \AlgSep
-set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5) \in \GG^4 \times \ZZ$, \AlgSep
-compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$. 
+set $c_1 \gets \hat{c}_1^\ell$ and $c_2 \gets \hat{c}_2^\ell$, \AlgSep
+choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
+choose random $\hat{\rv} \rgets \range{2^{2\lambda}}^8$
+and define $\hat{T} \deq \Big(\hat{c}_1^\mathit{ch}, \hat{c}_2^\mathit{ch}, 1, 1, \lfloor (t \cdot \mathit{ch})/\ell \rfloor\Big) \in \GG^4 \times \ZZ$, \AlgSep
+%and write $\hat{\rv} = \big(r_\text{w}, r_\text{w2}, r_\text{s1}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}, r_\text{s2} \big)$
+set $\Zv_q \deq \hat{T} \cdot \phi(\lfloor \hat{\rv}/\ell \rfloor) \in \GG^4 \times \ZZ$, \AlgSep
+% \left(\begin{array}{l}
+% Z_1 \gets \hat{c}_1^\mathit{ch} \cdot g^{\lfloor r_\text{w}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1}/\ell \rfloor} ,\quad
+% Z_2 \gets \hat{c}_2^\mathit{ch} \cdot g^{\lfloor r_\text{a}/\ell \rfloor} \cdot h^{\lfloor r_\text{s2}/\ell \rfloor} , \AlgSep
+% Z_3 \gets g^{\lfloor r_\text{w2}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1w}/\ell \rfloor} / \hat{c}_1^{\lfloor r_\text{w}/\ell \rfloor},\quad
+% Z_4 \gets g^{\lfloor r_\text{na}/\ell \rfloor} \cdot h^{\lfloor r_\text{sa}/\ell \rfloor} / \hat{c}^{\lfloor r_\text{a}/\ell \rfloor}, \AlgSep
+% Z_5 \gets \lfloor (t \cdot \mathit{ch} + r_\text{w2} - r_\text{na})/\ell \rfloor 
+% \end{array}\right) \in \GG^4 \times \ZZ$, \AlgSep
+compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
+output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
 \end{alg}
@@
 to an accepting transcript of a real protocol execution.
-First observe that $c_1, c_2, \Rv, \ell, \mathit{ch}$ are all distributed 
-as in a real transcript.  It remains to show that the same holds
+Because $\ell$ does not divide $\abs{\GG}$ with overwhelming probability,
+we know that $c_1$ and $c_2$ are uniform in $\GG$. 
+Hence, observe that $c_1, c_2, \Rv, \ell, \mathit{ch}$ are all distributed 
+exactly as in a real transcript.  It remains to show that the same holds
 for $\zv_\ell$ and $\Zv_q$. 
 In an interaction with a real prover 
-the vector $\rv$ is chosen uniformly in $\range{N}^8$.
-Consider one value $r \rgets \range{N}$.
-Because $N$ is much larger than $\ell \cdot \abs{\GG}$
+the vector $\rv$ is chosen uniformly in $\range{2^{2\lambda}}^8$.
+Consider one value $r \rgets \range{2^{2\lambda}}$.
+Because $2^{2\lambda}$ is much larger than $\ell$
 we know that the pair 
-$\big((\lfloor r/\ell \rfloor \bmod \abs{\GG}),\ (r \bmod \ell) \big)$
-is statistically close to uniform in $\range{\,\abs{\GG}\,} \times \range{\ell}$.
+$\big(\lfloor r/\ell \rfloor,\ (r \bmod \ell) \big)$
+is statistically close to uniform in $\range{2^{2\lambda}/\ell} \times \range{\ell}$.
 It directly follows that $\zv_\ell$ is statistically close to uniform 
 in $\range{\ell}^8$, as in the simulation.
-It also follows that $Z_1,Z_2,Z_3,Z_4 \in \GG$ are statistically close to 
-uniform in $\GG$ because each of these four terms is randomized by
-a fresh uniform randomizer,
-$h^{\lfloor r_\text{s1} / \ell \rfloor}, h^{\lfloor r_\text{s2} / \ell \rfloor}, h^{\lfloor r_\text{s1w} / \ell \rfloor}, h^{\lfloor r_\text{sa} / \ell \rfloor} \in \GG$ respectively. 
-Hence, these values are distributed as in
-the simulation.
-It remains to argue that $Z_5$ is simulated correctly. 
-In the real protocol $Z_5$ is equal to
-$\lfloor (t \cdot \mathit{ch} + r_\text{w2} - r_\text{an})/\ell \rfloor \in \ZZ$,
-possibly plus or minus one.
+It remains to argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly. 
+Let's start with the last component of~$\Zv_q$, namely $Z_5 \in \ZZ$.  
+In a real transcript 
+$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
+          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
+Therefore, because $\mathit{w2} - \mathit{na} = t$ we have
+\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
+where $\Delta \in \{0, \pm 1, \pm 2\}$. 
 Hence, because in the real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
-and $\lfloor r_\text{an} / \ell \rfloor$ 
-are fresh uniform values in $\range{N/\ell}$, this $Z_5$ is distributed 
+and $\lfloor r_\text{na} / \ell \rfloor$ 
+are fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
+as in the simulation, 
+this $Z_5$ is distributed 
 statistically close to its distribution in the simulation.
+Essentially the same argument shows that $Z_1, Z_2, Z_3, Z_4$ are
+also simulated correctly. 
+{\bf TODO:} explain why.
 \end{proof}
 
+\iffalse
 An optimization: the transcript elements $Z_3, Z_4 \in \GG$ can be simulated
@@
 and 
-$Z_4 = g^{\lfloor r_\text{an} / \ell \rfloor} h^{\lfloor r_\text{sa} / \ell \rfloor} / c^{\lfloor r_\text{a} / \ell \rfloor} \in \GG$,
+$Z_4 = g^{\lfloor r_\text{na} / \ell \rfloor} h^{\lfloor r_\text{sa} / \ell \rfloor} / c^{\lfloor r_\text{a} / \ell \rfloor} \in \GG$,
 where 
-$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{an}, r_\text{s1w}, r_\text{sa}$
+$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}$
 are chosen uniformly in $\range{N}$. 
@@
 efficient because the randomizers 
-$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{an}, r_\text{s1w}, r_\text{sa} \in \ZZ$
+$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa} \in \ZZ$
 do not need to be uniform in the entire interval $\range{N}$.
@@
 solving for $\Zv_q \in \GG^4 \times \ZZ$. 
+\fi
 
@@
           T^{\mathit{ch} - \mathit{ch}'}. \]
-Let $\zv_\ell - \zv_\ell' = \Big(\Delta w,\ \Delta \mathit{w2},\ \Delta \mathit{s1},\ \Delta a,\ \Delta \mathit{an},\ \Delta \mathit{s1w},\ \Delta \mathit{sa},\ \Delta \mathit{s2} \Big) \in \ZZ^8$ and let $\Delta \mathit{ch} = \mathit{ch} - \mathit{ch}' \in \ZZ$.
+Let $\zv_\ell - \zv_\ell' = \Big(\Delta w,\ \Delta \mathit{w2},\ \Delta \mathit{s1},\ \Delta a,\ \Delta \mathit{na},\ \Delta \mathit{s1w},\ \Delta \mathit{sa},\ \Delta \mathit{s2} \Big) \in \ZZ^8$ and let $\Delta \mathit{ch} = \mathit{ch} - \mathit{ch}' \in \ZZ$.
 Then plugging this into the definition of $\phi$ we obtain
@@
        g^{\Delta \mathit{w2}} \cdot h^{\Delta \mathit{s1w}} / c_1^{\Delta w}, \\
-       g^{\Delta \mathit{an}} \cdot h^{\Delta \mathit{sa}} / c^{\Delta a},\ \ \ 
-       \Delta \mathit{w2} - \Delta \mathit{an}\ 
+       g^{\Delta \mathit{na}} \cdot h^{\Delta \mathit{sa}} / c^{\Delta a},\ \ \ 
+       \Delta \mathit{w2} - \Delta \mathit{na}\ 
        \end{array} \right)
@@
 \\
-  \ell \cdot (\alpha_4 + n \cdot \gamma_4) + \Delta \mathit{an} & = n \cdot \Delta a,  & 
+  \ell \cdot (\alpha_4 + n \cdot \gamma_4) + \Delta \mathit{na} & = n \cdot \Delta a,  & 
   \ell \cdot (\beta_4 + s \cdot \gamma_4) + \Delta \mathit{sa} & = s \cdot \Delta a   
 \\
-  \ell \cdot z_4 + \Delta \mathit{w2} - \Delta \mathit{an} & = t \cdot \Delta \mathit{ch} 
+  \ell \cdot z_4 + \Delta \mathit{w2} - \Delta \mathit{na} & = t \cdot \Delta \mathit{ch} 
 \end{align*}
@@
 \label{eq:second} \\
-  \Delta \mathit{an} & \equiv n \cdot \Delta a  & 
+  \Delta \mathit{na} & \equiv n \cdot \Delta a  & 
   \Delta \mathit{sa} & \equiv s \cdot \Delta a   & \pmod{\ell} 
 \label{eq:third} \\
-  \Delta \mathit{w2} - \Delta \mathit{an} & \equiv t \cdot \Delta \mathit{ch} 
+  \Delta \mathit{w2} - \Delta \mathit{na} & \equiv t \cdot \Delta \mathit{ch} 
       &&& \pmod{\ell} 
@@
 in~\eqref{eq:fourth}
-gives $\Delta \mathit{an} \equiv (w^2 - t) \cdot \Delta \mathit{ch} \pmod{\ell}$. 
+gives $\Delta \mathit{na} \equiv (w^2 - t) \cdot \Delta \mathit{ch} \pmod{\ell}$. 
 Finally, the left equality in~\eqref{eq:third} 
@@
 
-\item choose a random $\rv \rgets \range{N}^8$
+\item choose a random $\rv \rgets \range{2^{2\lambda}}^8$
 and compute $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$,
-where $\phi$ is the homomrphism defined in~\eqref{eq:hom}.
+where $\phi$ is the homomorphism defined in~\eqref{eq:hom}.
 
@@
 \item compute:
-\[  \xv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
-    \zv_\ell \gets (\xv \bmod \ell) \in \range{\ell}^8, \quad
-    \zv_q \gets \lfloor \xv / \ell \rfloor \in \ZZ^8, \quad
+\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
+    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^8, \quad
+    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^8, \quad
     \Zv_q \gets \phi(\zv_q) \in \GG^4 \times \ZZ.
@@
 \paragraph{Proof of privacy.}
-TODO: Use the ZK proof of the interactive protocol. Easy corrolary.
+TODO: Use the ZK proof of the interactive protocol. Easy corollary.
 
 \paragraph{Proof of security.}
-TODO: Use the extractor of the interactive protocol. Easy corrolary.
+TODO: Use the extractor of the interactive protocol. Easy corollary.
 

### 2019-01-07 paper.tex
edits

@@
 \begin{alg}
-choose random $\hat{c}_1, \hat{c}_2 \rgets \GG,\ \ \ell \rgets \primes$, and
+\> choose random $\hat{c}_1, \hat{c}_2 \rgets \GG,\ \ \ell \rgets \primes$, and
 $\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
-set $c_1 \gets \hat{c}_1^\ell$ and $c_2 \gets \hat{c}_2^\ell$, \AlgSep
-choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
-choose random $\hat{\rv} \rgets \range{2^{2\lambda}}^8$
+\> set $c_1 \gets \hat{c}_1^\ell$ and $c_2 \gets \hat{c}_2^\ell$, \AlgSep
+\> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
+\lnum \label{ln:randv}
+\> choose random $\hat{\rv} \rgets \range{2^{2\lambda}}^8$
 and define $\hat{T} \deq \Big(\hat{c}_1^\mathit{ch}, \hat{c}_2^\mathit{ch}, 1, 1, \lfloor (t \cdot \mathit{ch})/\ell \rfloor\Big) \in \GG^4 \times \ZZ$, \AlgSep
-%and write $\hat{\rv} = \big(r_\text{w}, r_\text{w2}, r_\text{s1}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}, r_\text{s2} \big)$
-set $\Zv_q \deq \hat{T} \cdot \phi(\lfloor \hat{\rv}/\ell \rfloor) \in \GG^4 \times \ZZ$, \AlgSep
-% \left(\begin{array}{l}
-% Z_1 \gets \hat{c}_1^\mathit{ch} \cdot g^{\lfloor r_\text{w}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1}/\ell \rfloor} ,\quad
-% Z_2 \gets \hat{c}_2^\mathit{ch} \cdot g^{\lfloor r_\text{a}/\ell \rfloor} \cdot h^{\lfloor r_\text{s2}/\ell \rfloor} , \AlgSep
-% Z_3 \gets g^{\lfloor r_\text{w2}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1w}/\ell \rfloor} / \hat{c}_1^{\lfloor r_\text{w}/\ell \rfloor},\quad
-% Z_4 \gets g^{\lfloor r_\text{na}/\ell \rfloor} \cdot h^{\lfloor r_\text{sa}/\ell \rfloor} / \hat{c}^{\lfloor r_\text{a}/\ell \rfloor}, \AlgSep
-% Z_5 \gets \lfloor (t \cdot \mathit{ch} + r_\text{w2} - r_\text{na})/\ell \rfloor 
-% \end{array}\right) \in \GG^4 \times \ZZ$, \AlgSep
-compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
-output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
+\> set $\Zv_q \deq \hat{T} \cdot \phi(\lfloor \hat{\rv}/\ell \rfloor) \in \GG^4 \times \ZZ$, \AlgSep
+\lnum \label{ln:computeR}
+\> compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
+\> output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
 \end{alg}
@@
 we know that $c_1$ and $c_2$ are uniform in $\GG$. 
-Hence, observe that $c_1, c_2, \Rv, \ell, \mathit{ch}$ are all distributed 
+Hence, observe that $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
 exactly as in a real transcript.  It remains to show that the same holds
-for $\zv_\ell$ and $\Zv_q$. 
+for $\zv_\ell, \Zv_q$, and $\Rv$. 
 In an interaction with a real prover 
@@
 is statistically close to uniform in $\range{2^{2\lambda}/\ell} \times \range{\ell}$.
-It directly follows that $\zv_\ell$ is statistically close to uniform 
+It directly follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
+in a real transcript, is statistically close to uniform 
 in $\range{\ell}^8$, as in the simulation.
-It remains to argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly. 
-Let's start with the last component of~$\Zv_q$, namely $Z_5 \in \ZZ$.  
+
+Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly. 
+Write $\hat{\rv}$ generated on line~\eqref{ln:randv} in the simulation
+as $\hat{\rv} = \big(r_\text{w}, r_\text{w2}, r_\text{s1}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}, r_\text{s2} \big)$.
+Then the simulated $\Zv_q$ is computed as:
+\begin{equation} \label{eq:sim}
+\Zv_q \deq \left(\begin{array}{l}
+Z_1 \gets \hat{c}_1^\mathit{ch} \cdot g^{\lfloor r_\text{w}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1}/\ell \rfloor} ,\quad
+Z_2 \gets \hat{c}_2^\mathit{ch} \cdot g^{\lfloor r_\text{a}/\ell \rfloor} \cdot h^{\lfloor r_\text{s2}/\ell \rfloor} , \AlgSep
+Z_3 \gets g^{\lfloor r_\text{w2}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1w}/\ell \rfloor} / \hat{c}_1^{\lfloor r_\text{w}/\ell \rfloor},\quad
+Z_4 \gets g^{\lfloor r_\text{na}/\ell \rfloor} \cdot h^{\lfloor r_\text{sa}/\ell \rfloor} / \hat{c}^{\lfloor r_\text{a}/\ell \rfloor}, \AlgSep
+Z_5 \gets \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2}/\ell \rfloor - \lfloor r_\text{na}/\ell \rfloor 
+\end{array}\right) \in \GG^4 \times \ZZ.  
+\end{equation}
+Let's start with $Z_5 \in \ZZ$.  
 In a real transcript 
@@
           \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
-Therefore, because $\mathit{w2} - \mathit{na} = t$ we have
+Therefore, because $\mathit{w2} - \mathit{na} = t$, we have
+that $Z_5$ is a real transcript satifies
 \[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
 where $\Delta \in \{0, \pm 1, \pm 2\}$. 
-Hence, because in the real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
+In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
 and $\lfloor r_\text{na} / \ell \rfloor$ 
-are fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
-as in the simulation, 
-this $Z_5$ is distributed 
-statistically close to its distribution in the simulation.
+are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
+as in the the simulated $Z_5$ in~\eqref{eq:sim}.
+The only difference is that the real distribution is shifted by $\Delta$
+where as the simulated distribution is not.  
+Because $\Delta$ is small, $\Delta \in \{0, \pm 1, \pm 2\}$,
+this difference only negligibly affects the statistical distance. 
+We thus conclude that the simulated $Z_5$ in~\eqref{eq:sim} 
+is statistically close to its real distribution.
 Essentially the same argument shows that $Z_1, Z_2, Z_3, Z_4$ are
 also simulated correctly. 
+{\bf TODO:} explain why.
+
+Finally, it is not difficult to see that the computed $\Rv$ 
+on line~\eqref{ln:computeR} is, with overwhelming probability,
+the image under $\phi$ of some element $\rv' \in \range{2^{2\lambda}}^8$,
+as in a real transcript.
 {\bf TODO:} explain why.

### 2019-01-07 paper.tex
edits

@@
 
-Finally, it is not difficult to see that the computed $\Rv$ 
-on line~\eqref{ln:computeR} is, with overwhelming probability,
-the image under $\phi$ of some element $\rv' \in \range{2^{2\lambda}}^8$,
-as in a real transcript.
-{\bf TODO:} explain why.
+Finally, because the simulated $c_1, c_2, \ell, \mathit{ch}, \Zv_q, \zv_\ell$
+are all distributed statistically close to a real transcript, 
+it must be the case that the computed $\Rv$ 
+on line~\eqref{ln:computeR} is also distributed as in 
+a real transcript. 
 \end{proof}

### 2019-01-09 paper.tex
edits

@@
 
-\title{An Air Drop That Preserves Recipient Privacy}
+\title{An Airdrop That Preserves Recipient Privacy}
 \author{Dan Boneh \and Riad Wahby}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Private air drop: definitions}
+\section{Private airdrop: definitions}
 
-A private air drop (PAD) system is a triple of efficient algorithms:
+A private airdrop (PAD) system is a triple of efficient algorithms:
 \begin{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A private air drop to RSA public keys}
+\section{A private airdrop to ECDSA and Schnorr public keys}
+
+TODO: needs to be written.  Maybe put this first because it is so much
+simpler?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{A private airdrop to RSA public keys}
 
@@
 residue modulo the committed $n$.  Leaking this bit of information about $n$
-does not interfere with the application to a secure air drop.
+does not interfere with the application to a secure airdrop.
 
@@
 that $Z_5$ is a real transcript satifies
-\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
-where $\Delta \in \{0, \pm 1, \pm 2\}$. 
+\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor - \Delta \]
+where $\Delta \in \{0, 1\}$. 
 In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
@@
 where as the simulated distribution is not.  
-Because $\Delta$ is small, $\Delta \in \{0, \pm 1, \pm 2\}$,
+Because $\Delta$ is small, $\Delta \in \{0,1\}$,
 this difference only negligibly affects the statistical distance. 
@@
 
-\subsection{The concrete air drop system}
+\subsection{The concrete airdrop system}
 
-The air drop system is obtained by applying the Fiat-Shamir
+The airdrop system is obtained by applying the Fiat-Shamir
 heuristic to the protocol from the previous section. 
-The concrete private air drop system works as follows:
+The concrete private airdrop system works as follows:
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A private air drop to ElGamal public keys}
-
-TODO: needs to be written.  Maybe put this first because it is so much
-simpler?
-
 \bibliographystyle{alpha}

### 2019-01-09 paper.tex
edits

@@
 Let $\adv_1, \adv_2$ be two randomized algorithms that interact
-with generic group oracles for the group $\GG$ and 
-output $u_1, u_2 \in \GG$, respectively. 
+with group oracles for a generic group $\GG$ of unknown order.
+For $i=1,2$, algorithm $\adv_i$ outputs $u_i \in \GG$.
 Suppose that each algorithm makes at most $q$ type-1 queries
@@
 
-\item Prover $P$ chooses a random integers $s_1, s_2 \rgets \range{N}$ and computes
-       $c_1 \gets g^w \cdot h^{s_1} \in \GG$ and $c_2 \gets g^a \cdot h^{s_2}$.
+\item Prover $P$ chooses two random integers $s_1, s_2 \rgets \range{N}$ and computes
+       $c_1 \gets g^w \cdot h^{s_1} \in \GG$ and $c_2 \gets g^a \cdot h^{s_2} \in \GG$.
 
@@
 We design a ZKPK for a $\phi$-preimage 
-using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}:
+using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}.
+Here the verifier is given $T \in \GG^4 \times \ZZ$ 
+and the prover is given $T$ and $\vv \in \ZZ^8$
+where $\phi(\vv) = T$. 
+The protocol works as follows:
 \begin{enumerate}
@@
 Therefore, because $\mathit{w2} - \mathit{na} = t$, we have
-that $Z_5$ is a real transcript satifies
+that $Z_5$ in a real transcript satifies
 \[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor - \Delta \]
@@
 Because $\Delta$ is small, $\Delta \in \{0,1\}$,
-this difference only negligibly affects the statistical distance. 
+this difference only negligibly affects the statistical distance
+between the real and simulated distributions. 
 We thus conclude that the simulated $Z_5$ in~\eqref{eq:sim} 
 is statistically close to its real distribution.
+
 Essentially the same argument shows that $Z_1, Z_2, Z_3, Z_4$ are
 also simulated correctly. 
+For example, in a real transcript 
+\begin{align*}
+    Z_1 & \deq g^{\lfloor (\mathit{ch}\cdot w + r_\text{w}) / \ell \rfloor} \cdot 
+             h^{\lfloor (\mathit{ch}\cdot \mathit{s1} + r_\text{s1}) / \ell \rfloor} = \\
+       & =   g^{\lfloor (\mathit{ch}\cdot w) / \ell \rfloor} \cdot
+             h^{\lfloor (\mathit{ch}\cdot s1) / \ell \rfloor} \cdot
+             g^{\lfloor r_\text{w} / \ell \rfloor - \Delta_\text{w}} \cdot 
+             h^{\lfloor r_\text{s1} / \ell \rfloor - \Delta_\text{s1}} =  \\
+       & = (\tilde{c}_1)^\mathit{ch} \cdot
+             g^{\lfloor r_\text{w} / \ell \rfloor} \cdot 
+             h^{\lfloor r_\text{s1} / \ell \rfloor} \cdot 
+             \left[ (g^{1/\ell})^{\delta_\text{w} - \ell \cdot \Delta_\text{w}} \cdot 
+               (h^{1/\ell})^{\delta_\text{s1} - \ell \cdot \Delta_\text{s1}} \right].
+\end{align*}
+where $\Delta_\text{w}, \Delta_\text{s1} \in \{0,1\}$
+and $\delta_\text{w} \deq ((\mathit{ch} \cdot w) \bmod \ell) \in \range{\ell}$
+and $\delta_\text{s1} \deq ((\mathit{ch} \cdot \mathit{s1}) \bmod \ell) \in \range{\ell}$.
+Hence, $Z_1$ in a real transcript is distributed as 
+the simulated $Z_1$ in~\eqref{eq:sim}, where the only
+difference is the quantity 
+$\Delta \deq (g^{1/\ell})^{\delta_\text{w} - \ell \cdot \Delta_\text{w}} \cdot 
+               (h^{1/\ell})^{\delta_\text{s1} - \ell \cdot \Delta_\text{s1}} \in \GG$. 
+We claim that this $\Delta$ only negligibly affects the statistical distance
+between the real and simulated distributions. 
 {\bf TODO:} explain why.
@@
 from the left equality in~\eqref{eq:third}, and thus extract $n \in \ZZ$ by
-repeating over several $\ell$.  Similarly, it can extract $s \in \ZZ$ from
+repeating this procedure over several $\ell$ and then using the chinese
+remainder theorem.  
+Similarly, it can extract $s \in \ZZ$ from
 the right equality in~\eqref{eq:third}.   

### 2019-01-10 paper/paper.tex
add 'peanut gallery' package
question about delivering Enc(s) to signer in \S2
question about 'secure' vs 'private' in \S3.1

--- 2019-01-09 paper.tex
@@
 \documentclass[11pt]{article}
+\usepackage[dvipsnames]{xcolor}
 \usepackage[hidelinks]{hyperref}
@@
 \usepackage{macros}
+\usepackage[normalem]{ulem}
+\usepackage{peanutgallery}
 
@@
 the token $c$. 
+\RSW{is it necessary to suggest that Enc(s) appear on the blockchain? It could just be posted publicly, since it doesn't need to be remembered for long.}
 
@@
 residue modulo the committed $n$.  Leaking this bit of information about $n$
-does not interfere with the application to a secure airdrop.
+does not interfere with the application to a secure
+\RSW{``secure'' $\rightarrow$ ``private''?}
+airdrop.
 

### 2019-01-10 paper/paper.tex
move 'warm-up' ECDSA airdrop before RSA airdrop
also: break into separate file
translate notes into skeleton of ECDSA section

@@
 
+\rsw{stashed note from talk with DB}
+Simultaneously using the schemes of \S\ref{sec:dsa} and \S\ref{sec:rsa}
+    on the same blockchain allows distinguishing between users based on
+    key type.
+Can work around this using generic ZKPK, at substantial performance cost.
+(Alt narrative: talk about generic ZKPK first, then specialize to get better
+    perf. at cost of distinguishing.)
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Private airdrop: definitions}
+\section{Private airdrop: definitions}\label{sec:defs}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A private airdrop to ECDSA and Schnorr public keys}
-
-TODO: needs to be written.  Maybe put this first because it is so much
-simpler?
+\input{pad_ecdsa.tex}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A private airdrop to RSA public keys}
+\section{A private airdrop to RSA public keys}\label{sec:rsa}
 
@@
 
-\subsection{Proving knowledge of the factorization of a hidden integer}
+\subsection{Proving knowledge of the factorization of a hidden integer}\label{sec:rsa:proving}
 
@@
 
-\subsection{The concrete airdrop system}
+\subsection{The concrete airdrop system}\label{sec:rsa:airdrop}
 

### 2019-01-12 paper/paper.tex
stash note from chat with Dima and Henry

@@
     perf. at cost of distinguishing.)
+
+\rsw{stashed note from chat with Henry and Dima}
+Possible objection: why doesn't sender just generate a bunch of phony keys
+    and send all money to self?
+In other words, why is this scheme better, from the verifiers' point of view,
+    than the naive approach, i.e., sender generating a fresh key pair and
+    sending secret key to recipient?
+(Note that while the naive approach does not have existential unforgeability,
+    that property does not prevent self-dealing if sender knows secret key.
+Another way to say this is that the security property we need for the
+    airdrop-to-Github-users case is stronger than existential unforgeability.)
+
+One answer: for each RSA key $\PK = (n, e)$ to be paid, sender publishes
+    the challenge $c = g^nh^s$ and (separately, i.e., without revealing
+    correspondence) sender also publishes
+$(\PK, s')$, $s' = E(\PK, (c',s)))$, $c' = H(g^nh^s)$.
+In other words, the sender publishes a list of purported airdrop recipients
+    separately from the list of airdrop challenge tokens.
+
+If sender was dishonest with respect to any key, i.e., if for some $(\PK,
+    s')$, any of $s', c', c, s$ is invalid, key's owner can reveal $(\hat{c}',
+    \hat{s}) = D(\PK, s')$.
+Then verifiers check that $s' = E(\PK, (\hat{c}', \hat{s}))$, and that
+    either no corresponding $c$ exists, or that $c$ is not a commitment
+    to $n$ with opening $s$.
+
+\emph{Question:} do we need to make $E()$ deterministic for this to work
+    (say, $r = H(\PK)$ in OAEP)?
 

### 2019-01-12 paper/paper.tex
edits

--- 2019-01-10 paper/paper.tex
@@
 \> choose random $\hat{\rv} \rgets \range{2^{2\lambda}}^8$
-and define $\hat{T} \deq \Big(\hat{c}_1^\mathit{ch}, \hat{c}_2^\mathit{ch}, 1, 1, \lfloor (t \cdot \mathit{ch})/\ell \rfloor\Big) \in \GG^4 \times \ZZ$, \AlgSep
+and define $\hat{T} \deq \Big(\hat{c}_1^\mathit{ch},\ \hat{c}_2^\mathit{ch},\ 1,\ 1,\ \lfloor (t \cdot \mathit{ch})/\ell \rfloor\Big) \in \GG^4 \times \ZZ$, \AlgSep
 \> set $\Zv_q \deq \hat{T} \cdot \phi(\lfloor \hat{\rv}/\ell \rfloor) \in \GG^4 \times \ZZ$, \AlgSep
@@
 that $Z_5$ in a real transcript satifies
-\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor - \Delta \]
-where $\Delta \in \{0, 1\}$. 
+\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
+where $\Delta \in \{0, \pm 1\}$. 
 In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
@@
 where as the simulated distribution is not.  
-Because $\Delta$ is small, $\Delta \in \{0,1\}$,
-this difference only negligibly affects the statistical distance
+However this $\Delta$ only negligibly affects the statistical distance
 between the real and simulated distributions. 
+The reason is that in both distributions 
+every possible value in the range of $Z_5$, 
+except possibly at the edges, 
+is obtained from exactly $\ell^2$ values of $(r_\text{w2}, r_\text{na})$. 
 We thus conclude that the simulated $Z_5$ in~\eqref{eq:sim} 
@@
              h^{\lfloor (\mathit{ch}\cdot s1) / \ell \rfloor} \cdot
-             g^{\lfloor r_\text{w} / \ell \rfloor - \Delta_\text{w}} \cdot 
-             h^{\lfloor r_\text{s1} / \ell \rfloor - \Delta_\text{s1}} =  \\
+             g^{\lfloor r_\text{w} / \ell \rfloor + \Delta_\text{w}} \cdot 
+             h^{\lfloor r_\text{s1} / \ell \rfloor + \Delta_\text{s1}} =  \\
        & = (\tilde{c}_1)^\mathit{ch} \cdot
@@
              h^{\lfloor r_\text{s1} / \ell \rfloor} \cdot 
-             \left[ (g^{1/\ell})^{\delta_\text{w} - \ell \cdot \Delta_\text{w}} \cdot 
-               (h^{1/\ell})^{\delta_\text{s1} - \ell \cdot \Delta_\text{s1}} \right].
+             \left[ (g^{1/\ell})^{\delta_\text{w} + \ell \cdot \Delta_\text{w}} \cdot 
+               (h^{1/\ell})^{\delta_\text{s1} + \ell \cdot \Delta_\text{s1}} \right]
 \end{align*}
-where $\Delta_\text{w}, \Delta_\text{s1} \in \{0,1\}$
-and $\delta_\text{w} \deq ((\mathit{ch} \cdot w) \bmod \ell) \in \range{\ell}$
-and $\delta_\text{s1} \deq ((\mathit{ch} \cdot \mathit{s1}) \bmod \ell) \in \range{\ell}$.
+where $\Delta_\text{w}, \Delta_\text{s1} \in \{0,1\}$ as for $Z_5$, 
+and $\delta_\text{w} \deq (\mathit{ch} \cdot w \bmod \ell) \in \range{\ell}$
+and $\delta_\text{s1} \deq (\mathit{ch} \cdot \mathit{s1} \bmod \ell) \in \range{\ell}$.
 Hence, $Z_1$ in a real transcript is distributed as 

### 2019-01-12 paper/paper.tex
edits

@@
 between the real and simulated distributions. 
-The reason is that in both distributions 
+The reason is that in both distributions, 
 every possible value in the range of $Z_5$, 
 except possibly at the edges, 
-is obtained from exactly $\ell^2$ values of $(r_\text{w2}, r_\text{na})$. 
+is obtained from the same number of values 
+for the pair $(r_\text{w2}, r_\text{na})$. 
+%%  would be good to prove this as a general lemma.
 We thus conclude that the simulated $Z_5$ in~\eqref{eq:sim} 
@@
 also simulated correctly. 
-For example, in a real transcript 
+For example, in a real transcript, where $c_1 = g^w h^\mathit{s1}$, we have
 \begin{align*}
@@
              h^{\lfloor r_\text{s1} / \ell \rfloor + \Delta_\text{s1}} =  \\
-       & = (\tilde{c}_1)^\mathit{ch} \cdot
+       & = (c_1^{1/\ell})^\mathit{ch} \cdot
              g^{\lfloor r_\text{w} / \ell \rfloor} \cdot 
@@
 \end{align*}
-where $\Delta_\text{w}, \Delta_\text{s1} \in \{0,1\}$ as for $Z_5$, 
+where $\Delta_\text{w}, \Delta_\text{s1} \in \{0,1\}$,
 and $\delta_\text{w} \deq (\mathit{ch} \cdot w \bmod \ell) \in \range{\ell}$

### 2019-01-18 paper/paper.tex
add switch to turn on CCS style

@@
+%\def\useacmstyle{}
+\def\submissionpapernumber{$\infty$}
+
+\ifx\useacmstyle\undefined
     \documentclass[11pt]{article}
+    \usepackage{fullpage}
+    \usepackage[hidelinks]{hyperref}
+\else
+    \documentclass[sigconf,anonymous]{acmart}
+    \fancyhf{}
+    \fancyhead[C]{Anonymous submission \submissionpapernumber\ to ACM CCS 2019}
+    \fancyfoot[C]{\thepage}
+    \setcopyright{none}
+    \acmConference{ACM CCS Submission}{2019 Feb 05}{}
+    \acmYear{2019}
+    \settopmatter{printacmref=false, printccs=false, printfolios=false}
+\fi
+
 \usepackage[dvipsnames]{xcolor}
-\usepackage[hidelinks]{hyperref}
 \usepackage{amsthm,amsmath,amsfonts,amssymb,amstext,mathtools}
-\usepackage{fullpage}
 \usepackage{macros}
@@
 \title{An Airdrop That Preserves Recipient Privacy}
-\author{Dan Boneh \and Riad Wahby}
+\author{Dan Boneh \and Chris Jeffrey \and Joseph Poon \and Riad Wahby}
 
@@
 \begin{equation} \label{eq:lang}
-  {\cal R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
+  \mathcal{R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
                               (n, s, w, a) \in \range{N}^4 \Bigr)  \ \ 
         \text{s.t.}\ \ 
-                \begin{split}
+                \begin{aligned}
                         c   & = g^n \cdot h^s \ \ \text{in $\GG$}, \\
@@
                         2 & \leq t \leq \lambda  \ \textrm{a prime}
-                \end{split}  \right\}.
+                \end{aligned}  \right\}.
 \end{equation}
@@
   \phi\left(\!\!\begin{array}{l}
-                w, \mathit{w2}, s_1, a, \\
-                \mathit{na}, \mathit{s1w}, \mathit{sa}, s_2
+                w, \mathit{w2}, \mathit{s1}, a, \\
+                \mathit{na}, \mathit{s1w}, \mathit{sa}, \mathit{s2}
       \end{array}  \!\!\!\right) \deq
@@
 \begin{enumerate}
-\item The prover chooses a random $\rv \rgets \range{2^{2\lambda}}^8$
-and computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$. \\
-It sends $(c_1, c_2, \Rv)$ to the verifier.
+\item The prover sets
+    $\rv \deq (r_w, r_\mathit{w2}, r_\mathit{s1}, r_a, r_\mathit{na}, 
+                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$ where
+\[ r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}} 
+    \quad\text{and}\quad
+   r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N}.
+\]
+The prover computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
+and sends $(c_1, c_2, \Rv)$ to the verifier.
 
@@
 The protocol is insecure if the group $\GG$ contains a non-identity
-element of known order.  In the multiplicative group $(\ZZ/n)^*$ the
+element of known order.  {\bf TODO: describe an attack.}
+In the multiplicative group $(\ZZ/n)^*$ the
 element $-1$ has order~$2$, and hence the protocol is insecure in this
@@
 Protocol $\prot{P}$ is a zero-knowledge protocol
-for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang}.
+for the relation $\mathcal{R}_{g,h}$ in \eqref{eq:lang}.
 \end{theorem}
@@
 \begin{alg}
-\> choose random $\hat{c}_1, \hat{c}_2 \rgets \GG,\ \ \ell \rgets \primes$, and
-$\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
-\> set $c_1 \gets \hat{c}_1^\ell$ and $c_2 \gets \hat{c}_2^\ell$, \AlgSep
+\> choose random $c_1, c_2 \rgets \GG,\ \ \ell \rgets \primes$, and
+\ \ $\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
+\lnum \label{ln:randvell}
 \> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
-\lnum \label{ln:randv}
-\> choose random $\hat{\rv} \rgets \range{2^{2\lambda}}^8$
-and define $\hat{T} \deq \Big(\hat{c}_1^\mathit{ch},\ \hat{c}_2^\mathit{ch},\ 1,\ 1,\ \lfloor (t \cdot \mathit{ch})/\ell \rfloor\Big) \in \GG^4 \times \ZZ$, \AlgSep
-\> set $\Zv_q \deq \hat{T} \cdot \phi(\lfloor \hat{\rv}/\ell \rfloor) \in \GG^4 \times \ZZ$, \AlgSep
+\lnum \label{ln:randZ}
+\> choose random $Z_1, Z_2, Z_3, Z_4 \rgets \GG$, \\
+\lnum \label{ln:sim}
+\> choose random $\hat{r}_\text{w2}, \hat{r}_\text{na} \rgets \range{2^{2\lambda}}$
+and set $Z_5 \deq \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor \hat{r}_\text{w2} / \ell \rfloor - \lfloor \hat{r}_\text{na} / \ell \rfloor \in \ZZ$, \\
+\> set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5)  \in \GG^4 \times \ZZ$, \AlgSep
 \lnum \label{ln:computeR}
@@
 to an accepting transcript of a real protocol execution.
-Because $\ell$ does not divide $\abs{\GG}$ with overwhelming probability,
-we know that $c_1$ and $c_2$ are uniform in $\GG$. 
-Hence, observe that $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
+In a real transcript we know that $c_1$ and $c_2$ are uniform in $\GG$. 
+Hence, observe that the simulated $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
 exactly as in a real transcript.  It remains to show that the same holds
 for $\zv_\ell, \Zv_q$, and $\Rv$. 
-In an interaction with a real prover 
-the vector $\rv$ is chosen uniformly in $\range{2^{2\lambda}}^8$.
-Consider one value $r \rgets \range{2^{2\lambda}}$.
-Because $2^{2\lambda}$ is much larger than $\ell$
+In an interaction with a real prover the quantities
+$r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
+are chosen uniformly in $\range{N}$.
+Consider one such value $r \rgets \range{N}$.
+Because $N$ is much larger than $\abs{\GG} \cdot \ell$
 we know that the pair
-$\big(\lfloor r/\ell \rfloor,\ (r \bmod \ell) \big)$
-is statistically close to uniform in $\range{2^{2\lambda}/\ell} \times \range{\ell}$.
-It directly follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
+$\big(\lfloor r/\ell \rfloor \bmod \abs{\GG},\ (r \bmod \ell) \big)$
+is statistically close to uniform in $\range{\,\abs{\GG}\,} \times \range{\ell}$.
+Similarly,  in a real transcript
+each of $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa}$
+is chosen uniformly in $\range{2^{2 \lambda}}$ and therefore
+each of these four values modulo $\ell$
+is statistically close to uniform in $\range{\ell}$.
+It follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
 in a real transcript, is statistically close to uniform 
-in $\range{\ell}^8$, as in the simulation.
+in $\range{\ell}^8$, as in line~\eqref{ln:randvell} in the simulation.
 
 Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly.
-Write $\hat{\rv}$ generated on line~\eqref{ln:randv} in the simulation
-as $\hat{\rv} = \big(r_\text{w}, r_\text{w2}, r_\text{s1}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}, r_\text{s2} \big)$.
-Then the simulated $\Zv_q$ is computed as:
-\begin{equation} \label{eq:sim}
-\Zv_q \deq \left(\begin{array}{l}
-Z_1 \gets \hat{c}_1^\mathit{ch} \cdot g^{\lfloor r_\text{w}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1}/\ell \rfloor} ,\quad
-Z_2 \gets \hat{c}_2^\mathit{ch} \cdot g^{\lfloor r_\text{a}/\ell \rfloor} \cdot h^{\lfloor r_\text{s2}/\ell \rfloor} , \AlgSep
-Z_3 \gets g^{\lfloor r_\text{w2}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1w}/\ell \rfloor} / \hat{c}_1^{\lfloor r_\text{w}/\ell \rfloor},\quad
-Z_4 \gets g^{\lfloor r_\text{na}/\ell \rfloor} \cdot h^{\lfloor r_\text{sa}/\ell \rfloor} / \hat{c}^{\lfloor r_\text{a}/\ell \rfloor}, \AlgSep
-Z_5 \gets \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2}/\ell \rfloor - \lfloor r_\text{na}/\ell \rfloor 
-\end{array}\right) \in \GG^4 \times \ZZ.  
-\end{equation}
-Let's start with $Z_5 \in \ZZ$.  
-In a real transcript 
+Observe that each of the first four components of $\Zv_q$ is a group
+element in $\GG$ that is randomized by
+$h^{\lfloor r_\mathit{s1} / \ell \rfloor},\
+ h^{\lfloor r_\mathit{s2} / \ell \rfloor},\
+ h^{\lfloor r_\mathit{s1w} / \ell \rfloor},\
+ h^{\lfloor r_\mathit{sa} / \ell \rfloor}$ respectively.
+Because these four exponents are close to uniform in $\range{\,\abs{\GG}\,}$ and are
+independent of everything else in the transcript, it follows that
+in a real transcript $Z_1, Z_2, Z_3, Z_4$ are independent and close to uniform elements in $\GG$.  This is also how these elements are chosen 
+on line~\eqref{ln:randZ} in the simulation.
+
+It remains to argue that $Z_5 \in \ZZ$ is simulated correctly. 
+In a real transcript this $Z_5$ is computed as 
 $Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
           \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
-Therefore, because $\mathit{w2} - \mathit{na} = t$, we have
-that $Z_5$ in a real transcript satifies
+Because $\mathit{w2} - \mathit{na} = t$, we have
+that $Z_5$ in a real transcript satisfies
 \[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
@@
 are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
-as in the the simulated $Z_5$ in~\eqref{eq:sim}.
+as in the simulated $Z_5$ on line~\eqref{ln:sim}.
 The only difference is that the real distribution is shifted by $\Delta$
@@
 %%  would be good to prove this as a general lemma.
-We thus conclude that the simulated $Z_5$ in~\eqref{eq:sim} 
+We thus conclude that the simulated $Z_5$ in~\eqref{ln:sim} 
 is statistically close to its real distribution.
-
-Essentially the same argument shows that $Z_1, Z_2, Z_3, Z_4$ are
-also simulated correctly. 
-For example, in a real transcript, where $c_1 = g^w h^\mathit{s1}$, we have
-\begin{align*}
-    Z_1 & \deq g^{\lfloor (\mathit{ch}\cdot w + r_\text{w}) / \ell \rfloor} \cdot 
-             h^{\lfloor (\mathit{ch}\cdot \mathit{s1} + r_\text{s1}) / \ell \rfloor} = \\
-       & =   g^{\lfloor (\mathit{ch}\cdot w) / \ell \rfloor} \cdot
-             h^{\lfloor (\mathit{ch}\cdot s1) / \ell \rfloor} \cdot
-             g^{\lfloor r_\text{w} / \ell \rfloor + \Delta_\text{w}} \cdot 
-             h^{\lfloor r_\text{s1} / \ell \rfloor + \Delta_\text{s1}} =  \\
-       & = (c_1^{1/\ell})^\mathit{ch} \cdot
-             g^{\lfloor r_\text{w} / \ell \rfloor} \cdot 
-             h^{\lfloor r_\text{s1} / \ell \rfloor} \cdot 
-             \left[ (g^{1/\ell})^{\delta_\text{w} + \ell \cdot \Delta_\text{w}} \cdot 
-               (h^{1/\ell})^{\delta_\text{s1} + \ell \cdot \Delta_\text{s1}} \right]
-\end{align*}
-where $\Delta_\text{w}, \Delta_\text{s1} \in \{0,1\}$,
-and $\delta_\text{w} \deq (\mathit{ch} \cdot w \bmod \ell) \in \range{\ell}$
-and $\delta_\text{s1} \deq (\mathit{ch} \cdot \mathit{s1} \bmod \ell) \in \range{\ell}$.
-Hence, $Z_1$ in a real transcript is distributed as 
-the simulated $Z_1$ in~\eqref{eq:sim}, where the only
-difference is the quantity 
-$\Delta \deq (g^{1/\ell})^{\delta_\text{w} - \ell \cdot \Delta_\text{w}} \cdot 
-               (h^{1/\ell})^{\delta_\text{s1} - \ell \cdot \Delta_\text{s1}} \in \GG$. 
-We claim that this $\Delta$ only negligibly affects the statistical distance
-between the real and simulated distributions. 
-{\bf TODO:} explain why.
 
@@
 \begin{definition}
-We say that algorithm ${\cal G}$ is an \defn{honest instance
-generator} for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}
+We say that algorithm $\mathcal{G}$ is an \defn{honest instance
+generator} for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}
 if it chooses integers $n, s, t$, and outputs $(c, t)$ where
@@
 Protocol $\prot{P}$ is an argument of knowledge
-for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang} 
+for the relation $\mathcal{R}_{g,h}$ in \eqref{eq:lang} 
 for instances $(c,t)$ generated by an honest instance
-generator ${\cal G}$,
+generator $\mathcal{G}$,
 when the group $\GG$ is a modeled as a generic group of unknown order. 
@@
 We construct an extractor that given an instance $(c,t)$ 
-generated by ${\cal G}$,
+generated by $\mathcal{G}$,
 interacts with a convincing prover and outputs a witness $(n, s, w, a)$ 
-for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}. 
+for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}. 
 The protocol transcript is $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
@@
 accepting transcripts
-${\cal T}_1 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
+$\mathcal{T}_1 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
 and 
-${\cal T}_2 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
+$\mathcal{T}_2 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
 Dividing the corresponding verification equations one by the other
@@
 and $a \deq \alpha_0 + n \cdot \gamma_0 \in \ZZ$.
-For any pair of accepting transcripts such as $({\cal T}_1, {\cal T}_2)$,
+For any pair of accepting transcripts such as $(\mathcal{T}_1, \mathcal{T}_2)$,
 it must be the case that 
@@
 It thus obtains a witness $(n, s, w, a)$ 
-for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}, as required.
+for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}, as required.
 \end{proof}

### 2019-01-18 paper/defs.tex
split paper into separate files per section

--- 2019-01-18 paper/paper.tex
@@
-%\def\useacmstyle{}
-\def\submissionpapernumber{$\infty$}
-
-\ifx\useacmstyle\undefined
-    \documentclass[11pt]{article}
-    \usepackage{fullpage}
-    \usepackage[hidelinks]{hyperref}
-\else
-    \documentclass[sigconf,anonymous]{acmart}
-    \fancyhf{}
-    \fancyhead[C]{Anonymous submission \submissionpapernumber\ to ACM CCS 2019}
-    \fancyfoot[C]{\thepage}
-    \setcopyright{none}
-    \acmConference{ACM CCS Submission}{2019 Feb 05}{}
-    \acmYear{2019}
-    \settopmatter{printacmref=false, printccs=false, printfolios=false}
-\fi
-
-\usepackage[dvipsnames]{xcolor}
-\usepackage{amsthm,amsmath,amsfonts,amssymb,amstext,mathtools}
-\usepackage{macros}
-\usepackage[normalem]{ulem}
-\usepackage{peanutgallery}
-
-\begin{document}
-
-\title{An Airdrop That Preserves Recipient Privacy}
-\author{Dan Boneh \and Chris Jeffrey \and Joseph Poon \and Riad Wahby}
-
-\maketitle
-
-\begin{abstract}
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-
-More to come.
-
-\rsw{stashed note from talk with DB}
-Simultaneously using the schemes of \S\ref{sec:dsa} and \S\ref{sec:rsa}
-    on the same blockchain allows distinguishing between users based on
-    key type.
-Can work around this using generic ZKPK, at substantial performance cost.
-(Alt narrative: talk about generic ZKPK first, then specialize to get better
-    perf. at cost of distinguishing.)
-
-\rsw{stashed note from chat with Henry and Dima}
-Possible objection: why doesn't sender just generate a bunch of phony keys
-    and send all money to self?
-In other words, why is this scheme better, from the verifiers' point of view,
-    than the naive approach, i.e., sender generating a fresh key pair and
-    sending secret key to recipient?
-(Note that while the naive approach does not have existential unforgeability,
-    that property does not prevent self-dealing if sender knows secret key.
-Another way to say this is that the security property we need for the
-    airdrop-to-Github-users case is stronger than existential unforgeability.)
-
-One answer: for each RSA key $\PK = (n, e)$ to be paid, sender publishes
-    the challenge $c = g^nh^s$ and (separately, i.e., without revealing
-    correspondence) sender also publishes
-$(\PK, s')$, $s' = E(\PK, (c',s)))$, $c' = H(g^nh^s)$.
-In other words, the sender publishes a list of purported airdrop recipients
-    separately from the list of airdrop challenge tokens.
-
-If sender was dishonest with respect to any key, i.e., if for some $(\PK,
-    s')$, any of $s', c', c, s$ is invalid, key's owner can reveal $(\hat{c}',
-    \hat{s}) = D(\PK, s')$.
-Then verifiers check that $s' = E(\PK, (\hat{c}', \hat{s}))$, and that
-    either no corresponding $c$ exists, or that $c$ is not a commitment
-    to $n$ with opening $s$.
-
-\emph{Question:} do we need to make $E()$ deterministic for this to work
-    (say, $r = H(\PK)$ in OAEP)?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Private airdrop: definitions}\label{sec:defs}
@@
 
-\item $\text{sign}(\SK, (c, s), m) \to \text{sig}$:
+\item $\text{sign}(\SK, (c, s), m) \to \sig$:
 Signs a message $m$ indicating that the token $c$ is spent.
 
-\item $\text{verify}(c, m, \text{sig}) \to \{\text{yes},\text{no}\}:$
-Verify that a signature $\text{sig}$ on token $c$ is valid.
+\item $\text{verify}(c, m, \sig) \to \{\text{yes},\text{no}\}:$
+Verify that a signature $\sig$ on token $c$ is valid.
 \end{itemize}
@@
 \end{lemma}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{pad_ecdsa.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A private airdrop to RSA public keys}\label{sec:rsa}
-
-From here we use the following notations:
-$\lambda$ is the security parameter (e.g., $\lambda = 128$), 
-$\range{\ell}$ denotes the set of integers $\{0,1,\ldots,\ell-1\}$, and 
-$\primes$ is a set of size $2^\lambda$ 
-containing the smallest $2^\lambda$ odd primes. 
-%
-We will also need a set of public parameters that include the description
-of a cyclic group $\GG$ of unknown order.  We let $g$ and $h$ be two
-random generators of $\GG$ where the discrete-log of $g$ base $h$ is unknown.
-
-\subsection{Proving knowledge of the factorization of a hidden integer}\label{sec:rsa:proving}
-
-Let $n \in \range{N}$ be a secret integer 
-where $N$ is a public upper bound on~$n$.
-We will also assume that $N > \abs{\GG} \cdot 2^{2 \lambda}$.
-Let $c \deq g^n \cdot h^s \in \GG$ be a commitment to $n$, 
-where $s \rgets \range{N}$.  
-We first develop a zero knowledge protocol for proving knowledge of the
-factorization of~$n$ given only $c$.
-
-To prove knowledge of the factorization of $n$ the prover
-proves knowledge of a $w \in \range{N}$ such that $w^2 \equiv t \pmod{n}$
-for some small public prime $t \in \ZZ$, namely $2 \leq t \leq \lambda$.
-That is, we provide a ZKPK for the relation
-\begin{equation} \label{eq:lang}
-  \mathcal{R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
-                              (n, s, w, a) \in \range{N}^4 \Bigr)  \ \ 
-        \text{s.t.}\ \ 
-                \begin{aligned}
-                        c   & = g^n \cdot h^s \ \ \text{in $\GG$}, \\
-                        w^2 & = t + a \cdot n \ \ \text{in $\ZZ$}, \\
-                        2 & \leq t \leq \lambda  \ \textrm{a prime}
-                \end{aligned}  \right\}.
-\end{equation}
-Here $(c, t)$ is a statement and $(n, s, w, a)$ is a witness.
-The integer relation $w^2 = t + a\cdot n$ proves that 
-$w^2 \equiv t \pmod{n}$, as required.
-We note that a ZKPK for~\eqref{eq:lang} proves that $t \in \ZZ$ is a quadratic
-residue modulo the committed $n$.  Leaking this bit of information about $n$
-does not interfere with the application to a secure
-\RSW{``secure'' $\rightarrow$ ``private''?}
-airdrop.
-
-\medskip\noindent
-Protocol $\prot{P}$: The ZKPK protocol for~\eqref{eq:lang} 
-between the prover $P$ and the verifier $V$ works as follows:
-\begin{itemize}
-\item input:  the verifier has $(c, t) \in \GG \times \range{\lambda}$ and 
-the prover has $(c, t, n, s, w, a) \in \GG \times \range{N}^5$
-
-\item Prover $P$ chooses two random integers $s_1, s_2 \rgets \range{N}$ and computes
-       $c_1 \gets g^w \cdot h^{s_1} \in \GG$ and $c_2 \gets g^a \cdot h^{s_2} \in \GG$.
-
-\item Next, define a homomorphism $\phi:\ZZ^8 \to \GG^4 \times \ZZ$ 
-parameterized by $g, h, c, c_1, c_2$ as follows:
-\begin{equation} \label{eq:hom}
-  \phi\left(\!\!\begin{array}{l}
-                w, \mathit{w2}, \mathit{s1}, a, \\
-                \mathit{na}, \mathit{s1w}, \mathit{sa}, \mathit{s2}
-      \end{array}  \!\!\!\right) \deq
-      \Bigl(\ 
-       g^w \cdot h^{\mathit{s1}},\ \ \ 
-       g^a \cdot h^{\mathit{s2}},\ \ \ 
-       g^{\mathit{w2}} \cdot h^{\mathit{s1w}} / c_1^w,\ \ \ 
-       g^{\mathit{na}} \cdot h^{\mathit{sa}} / c^a,\ \ \ 
-       \mathit{w2} - \mathit{na}\ \Bigr)
-\end{equation}
-It is easy to see that $\phi$ is a group homomorphism.
-The range of $\phi$ is the group $\GG^4 \times \ZZ$.  
-We will write the group operation in this group multiplicatively.
-That is, if $(a_i, b_i, c_i, d_i, e_i) \in \GG^4 \times \ZZ$ for $i=1,2$
-then 
-\[  (a_1, b_1, c_1, d_1, e_1) \cdot (a_2, b_2, c_2, d_2, e_2) \deq 
-      (a_1 a_2,\ b_1 b_2,\ c_1 c_2,\ d_1 d_2,\ e_1 + e_2).  \]
-
-We need a ZKPK for a $\phi$-preimage of 
-$T \deq (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ$. 
-In other words, we need a zero-knowledge proof of knowledge for a vector 
-$\vv' = (w', \mathit{w2}', s_1', a', \mathit{na}', 
-              \mathit{s1w}', \mathit{sa}', s_2') \in \ZZ^8$ 
-such that 
-\[   \phi(\vv') = T = (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ.  \]
-Doing so proves 
-that $c_1$ is a commitment to $w' \in \ZZ$, 
-that $c_2$ is a commitment to $a' \in \ZZ$,
-that $\mathit{w2}' = (w')^2$, and 
-that $\mathit{na}' = a' \cdot n$ for some integer $a'$.
-Then the last relation proves that $(w')^2 - a' \cdot n = t$ in $\ZZ$,
-as required.
-
-We design a ZKPK for a $\phi$-preimage 
-using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}.
-Here the verifier is given $T \in \GG^4 \times \ZZ$ 
-and the prover is given $T$ and $\vv \in \ZZ^8$
-where $\phi(\vv) = T$. 
-The protocol works as follows:
-\begin{enumerate}
-\item The prover sets
-    $\rv \deq (r_w, r_\mathit{w2}, r_\mathit{s1}, r_a, r_\mathit{na}, 
-                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$ where
-\[ r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}} 
-    \quad\text{and}\quad
-   r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N}.
-\]
-The prover computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
-and sends $(c_1, c_2, \Rv)$ to the verifier.
-
-\item The verifier chooses challenges $\mathit{ch} \rgets \range{2^\lambda}$
-and $\ell \rgets \primes$. \\
-It sends $(\ell, \mathit{ch})$ to the prover.
-
-\item The prover computes:
-\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
-    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^8, \quad
-    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^8, \quad
-    \Zv_q \gets \phi(\zv_q)  
-\]
-and sends $(\Zv_q, \zv_\ell) \in (\GG^4 \times \ZZ) \times \range{\ell}^8$ 
-to the verifier.
-
-\item The verifier accepts if 
-$\ \Zv_q^\ell \cdot \phi(\zv_\ell) = T^\mathit{ch} \cdot \Rv\ $ in 
-$\GG^4 \times \ZZ$.
-\end{enumerate}
-\end{itemize}
-
-\paragraph{Comment 1.}
-The protocol is insecure if the group $\GG$ contains a non-identity
-element of known order.  {\bf TODO: describe an attack.}
-In the multiplicative group $(\ZZ/n)^*$ the
-element $-1$ has order~$2$, and hence the protocol is insecure in this
-group.  Instead, we can work in the quotient group $(\ZZ/n)/\{\pm 1\}$, 
-where elements are represented as integers in the interval $[1,n/2]$
-and the product of $x$ and $y$ is defined as 
-$\abs{x \cdot y} = \min(z, n-z)$ where $z = (x \cdot y \bmod n)$.
-In this group $-1$ is the same as $1$, and presumably there are
-no other known elements of known order.
-
-\paragraph{Comment 2.}
-The commitment $c_2$ to the integer $a$ is necessary for soundness,
-and in particular to ensure that $a$ is an integer.  If $c_2$ along
-with $s_2$ and the second coordinate of $\phi$ are eliminated then there
-is an attack where an adversarial prover can prove knowledge of
-$(\sqrt{3} \bmod n)$ using $a = 1/n$ and $w = 2$.
-
-\paragraph{Comment 3.}
-There is a seemingly simpler method to prove that one knows the
-factorization of~$n$, namely, prove that one knows $p$ such that $p$
-divides $n$.  That is, instead of committing to $w$ we would commit to
-$p$ and $q$ and then prove that $p \cdot q = n$. But we would
-also need to prove that the committed $p$ is not one of 
-$\{1, -1, n, -n\}$, and that results in a longer proof.
-
-\paragraph{Proof of security.}
-We need to prove the protocol above is zero-knowledge and a 
-proof of knowledge.
-
-\begin{theorem}
-Protocol $\prot{P}$ is a zero-knowledge protocol
-for the relation $\mathcal{R}_{g,h}$ in \eqref{eq:lang}.
-\end{theorem}
-
-\begin{proof}
-The simulator takes $(c, t)$ as input and outputs the simulated transcript
-$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
-\begin{alg}
-\> choose random $c_1, c_2 \rgets \GG,\ \ \ell \rgets \primes$, and
-\ \ $\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
-\lnum \label{ln:randvell}
-\> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
-\lnum \label{ln:randZ}
-\> choose random $Z_1, Z_2, Z_3, Z_4 \rgets \GG$, \\
-\lnum \label{ln:sim}
-\> choose random $\hat{r}_\text{w2}, \hat{r}_\text{na} \rgets \range{2^{2\lambda}}$
-and set $Z_5 \deq \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor \hat{r}_\text{w2} / \ell \rfloor - \lfloor \hat{r}_\text{na} / \ell \rfloor \in \ZZ$, \\
-\> set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5)  \in \GG^4 \times \ZZ$, \AlgSep
-\lnum \label{ln:computeR}
-\> compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
-\> output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
-\end{alg}
-We show the simulated transcript is distributed statistically close
-to an accepting transcript of a real protocol execution.
-In a real transcript we know that $c_1$ and $c_2$ are uniform in $\GG$. 
-Hence, observe that the simulated $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
-exactly as in a real transcript.  It remains to show that the same holds
-for $\zv_\ell, \Zv_q$, and $\Rv$. 
-In an interaction with a real prover the quantities
-$r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
-are chosen uniformly in $\range{N}$.
-Consider one such value $r \rgets \range{N}$.
-Because $N$ is much larger than $\abs{\GG} \cdot \ell$
-we know that the pair
-$\big(\lfloor r/\ell \rfloor \bmod \abs{\GG},\ (r \bmod \ell) \big)$
-is statistically close to uniform in $\range{\,\abs{\GG}\,} \times \range{\ell}$.
-Similarly,  in a real transcript
-each of $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa}$
-is chosen uniformly in $\range{2^{2 \lambda}}$ and therefore
-each of these four values modulo $\ell$
-is statistically close to uniform in $\range{\ell}$.
-It follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
-in a real transcript, is statistically close to uniform 
-in $\range{\ell}^8$, as in line~\eqref{ln:randvell} in the simulation.
-
-Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly.
-Observe that each of the first four components of $\Zv_q$ is a group
-element in $\GG$ that is randomized by
-$h^{\lfloor r_\mathit{s1} / \ell \rfloor},\
- h^{\lfloor r_\mathit{s2} / \ell \rfloor},\
- h^{\lfloor r_\mathit{s1w} / \ell \rfloor},\
- h^{\lfloor r_\mathit{sa} / \ell \rfloor}$ respectively.
-Because these four exponents are close to uniform in $\range{\,\abs{\GG}\,}$ and are
-independent of everything else in the transcript, it follows that
-in a real transcript $Z_1, Z_2, Z_3, Z_4$ are independent and close to uniform elements in $\GG$.  This is also how these elements are chosen 
-on line~\eqref{ln:randZ} in the simulation.
-
-It remains to argue that $Z_5 \in \ZZ$ is simulated correctly. 
-In a real transcript this $Z_5$ is computed as 
-$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
-          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
-Because $\mathit{w2} - \mathit{na} = t$, we have
-that $Z_5$ in a real transcript satisfies
-\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
-where $\Delta \in \{0, \pm 1\}$. 
-In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
-and $\lfloor r_\text{na} / \ell \rfloor$ 
-are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
-as in the simulated $Z_5$ on line~\eqref{ln:sim}.
-The only difference is that the real distribution is shifted by $\Delta$
-where as the simulated distribution is not.  
-However this $\Delta$ only negligibly affects the statistical distance
-between the real and simulated distributions. 
-The reason is that in both distributions, 
-every possible value in the range of $Z_5$, 
-except possibly at the edges, 
-is obtained from the same number of values 
-for the pair $(r_\text{w2}, r_\text{na})$. 
-%%  would be good to prove this as a general lemma.
-We thus conclude that the simulated $Z_5$ in~\eqref{ln:sim} 
-is statistically close to its real distribution.
-
-Finally, because the simulated $c_1, c_2, \ell, \mathit{ch}, \Zv_q, \zv_\ell$
-are all distributed statistically close to a real transcript, 
-it must be the case that the computed $\Rv$ 
-on line~\eqref{ln:computeR} is also distributed as in 
-a real transcript. 
-\end{proof}
-
-\iffalse
-An optimization: the transcript elements $Z_3, Z_4 \in \GG$ can be simulated
-in a similar fashion to how we simulated $Z_5$ in the proof above.
-That is, 
-$Z_3 = g^{\lfloor r_\text{w2} / \ell \rfloor} h^{\lfloor r_\text{s1w} / \ell \rfloor} / c_1^{\lfloor r_\text{w} / \ell \rfloor} \in \GG$
-and 
-$Z_4 = g^{\lfloor r_\text{na} / \ell \rfloor} h^{\lfloor r_\text{sa} / \ell \rfloor} / c^{\lfloor r_\text{a} / \ell \rfloor} \in \GG$,
-where 
-$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}$
-are chosen uniformly in $\range{N}$. 
-It is not difficult to see that these $Z_3$ and $Z_4$ 
-are distributed as in a real transcript.
-This method of simulation can be used to make the protocol slightly more
-efficient because the randomizers 
-$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa} \in \ZZ$
-do not need to be uniform in the entire interval $\range{N}$.
-It suffices to choose these six values 
-uniformly in $\range{2^{2 \lambda}}$, which is a smaller interval
-than $\range{N}$.  Only $r_\text{s1}$ and $r_\text{s2}$ need to be chosen
-uniformly in the full interval $\range{N}$ so that $Z_1$ and $Z_2$ are uniform
-in $\GG$. 
-However, if the simulator chooses $c_1, c_2 \in \GG$ randomly in $\GG$
-so that it knows
-their $\ell$-th root, then even $Z_1$ and $Z_2$ can also be simulated as above.
-Then $r_\text{s1}$ and $r_\text{s2}$ can also be chosen uniformly
-in the range $\range{2^{2 \lambda}}$.
-In other words, the simulator works by first 
-choosing a random $\rv \gets \range{2^{2\lambda}}^8$,
-computing $\Rv \gets \phi(\rv)$, and then
-solving for $\Zv_q \in \GG^4 \times \ZZ$. 
-\fi
-
-\begin{definition}
-We say that algorithm $\mathcal{G}$ is an \defn{honest instance
-generator} for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}
-if it chooses integers $n, s, t$, and outputs $(c, t)$ where
-$c \deq g^n h^s \in \GG$. 
-\end{definition}
-
-\begin{theorem}
-Protocol $\prot{P}$ is an argument of knowledge
-for the relation $\mathcal{R}_{g,h}$ in \eqref{eq:lang} 
-for instances $(c,t)$ generated by an honest instance
-generator $\mathcal{G}$,
-when the group $\GG$ is a modeled as a generic group of unknown order. 
-\end{theorem}
-
-\begin{proof}
-We construct an extractor that given an instance $(c,t)$ 
-generated by $\mathcal{G}$,
-interacts with a convincing prover and outputs a witness $(n, s, w, a)$ 
-for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}. 
-The protocol transcript is $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
-The extractor rewinds the prover and obtains two
-accepting transcripts
-$\mathcal{T}_1 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
-and 
-$\mathcal{T}_2 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
-Dividing the corresponding verification equations one by the other
-we obtain
-\[   (\Zv_q / \Zv_q')^\ell \cdot \phi(\zv_\ell - \zv_\ell') = 
-          T^{\mathit{ch} - \mathit{ch}'}. \]
-Let $\zv_\ell - \zv_\ell' = \Big(\Delta w,\ \Delta \mathit{w2},\ \Delta \mathit{s1},\ \Delta a,\ \Delta \mathit{na},\ \Delta \mathit{s1w},\ \Delta \mathit{sa},\ \Delta \mathit{s2} \Big) \in \ZZ^8$ and let $\Delta \mathit{ch} = \mathit{ch} - \mathit{ch}' \in \ZZ$.
-Then plugging this into the definition of $\phi$ we obtain
-\begin{equation} \label{eq:messy}
-      (\Zv_q / \Zv_q')^\ell \cdot
-      \left(\begin{array}{l}
-       g^{\Delta w} \cdot h^{\Delta \mathit{s1}},\ \ \ 
-       g^{\Delta a} \cdot h^{\Delta \mathit{s2}},\ \ \ 
-       g^{\Delta \mathit{w2}} \cdot h^{\Delta \mathit{s1w}} / c_1^{\Delta w}, \\
-       g^{\Delta \mathit{na}} \cdot h^{\Delta \mathit{sa}} / c^{\Delta a},\ \ \ 
-       \Delta \mathit{w2} - \Delta \mathit{na}\ 
-       \end{array} \right)
-          = \left(\begin{array}{l}c_1, \ c_2, \ 1, \\ 1,\ t \end{array}\right)^{\Delta \mathit{ch}}.
-\end{equation}
-Let $\Zv_q / \Zv_q' = (z_1, z_2, z_3, z_4, z_5)$ 
-where $z_1, z_2, z_3, z_4 \in \GG$ and $z_5 \in \ZZ$.  
-In a generic group $\GG$, the group elements $z_1, z_2, z_3, z_4$ 
-must satisfy $z_i = g^{\alpha_i} h^{\beta_i} c^{\gamma_i} \prod_{j=1}^q g_j^{\delta_{i,j}}$
-for $i=1,2,3,4$, 
-and $c_1 = g^{\alpha} h^{\beta} c^\gamma \prod_{j=1}^q g_j^{\delta_{j}}$,
-and $c_2 = g^{\alpha_0} h^{\beta_0} c^\gamma \prod_{j=1}^q g_j^{\delta_{0,j}}$,
-where the extractor knows all the listed integer exponents.
-Here $g_1,\ldots,g_q \in \GG$ are random group elements produced in response
-to a generic group oracle query for a random group element.
-
-It now follows from~\eqref{eq:messy}, and from $c = g^n h^s$, 
-and by uniqueness of representation in generic groups (\Lemma{lem:unique}),
-that the following equations must hold over the integers:
-\begin{align*}
-  \ell \cdot (\alpha_1 + n \cdot \gamma_1) + \Delta w & = (\alpha + n \cdot \gamma) \cdot \Delta \mathit{ch},  &
-  \ell \cdot (\beta_1 + s \cdot \gamma_1) + \Delta \mathit{s1} & = (\beta + s \cdot \gamma) \cdot \Delta \mathit{ch}  
-\\
-  \ell \cdot (\alpha_2 + n \cdot \gamma_2) + \Delta a & = (\alpha_0 + n \cdot \gamma_0) \cdot \Delta \mathit{ch},  &
-  \ell \cdot (\beta_2 + s \cdot \gamma_2) + \Delta \mathit{s2} & = (\beta_0 + s \cdot \gamma_0) \cdot \Delta \mathit{ch}  
-\\
-  \ell \cdot (\alpha_3 + n \cdot \gamma_3) + \Delta \mathit{w2} & = (\alpha + n \cdot \gamma) \cdot \Delta w,  &
-  \ell \cdot (\beta_3 + s \cdot \gamma_3) + \Delta \mathit{s1w} & = (\beta + s \cdot \gamma) \cdot \Delta w   
-\\
-  \ell \cdot (\alpha_4 + n \cdot \gamma_4) + \Delta \mathit{na} & = n \cdot \Delta a,  & 
-  \ell \cdot (\beta_4 + s \cdot \gamma_4) + \Delta \mathit{sa} & = s \cdot \Delta a   
-\\
-  \ell \cdot z_4 + \Delta \mathit{w2} - \Delta \mathit{na} & = t \cdot \Delta \mathit{ch} 
-\end{align*}
-The extractor knows all these values except for $n$ and $s$.
-Reducing these equations modulo $\ell$ gives:
-\begin{align}
-  \Delta w & \equiv (\alpha + n \cdot \gamma) \cdot \Delta \mathit{ch}  &
-  \Delta \mathit{s1} & \equiv (\beta + s \cdot \gamma) \cdot \Delta \mathit{ch}  & \pmod{\ell} 
-\label{eq:first} \\
-  \Delta a & \equiv (\alpha_0 + n \cdot \gamma_0) \cdot \Delta \mathit{ch}  &
-  \Delta \mathit{s2} & \equiv (\beta_0 + s \cdot \gamma_0) \cdot \Delta \mathit{ch}  & \pmod{\ell} 
-\label{eq:firsta} \\
-  \Delta \mathit{w2} & \equiv (\alpha + n \cdot \gamma) \cdot \Delta w  &
-  \Delta \mathit{s1w} & \equiv (\beta + s \cdot \gamma) \cdot \Delta w   & \pmod{\ell} 
-\label{eq:second} \\
-  \Delta \mathit{na} & \equiv n \cdot \Delta a  & 
-  \Delta \mathit{sa} & \equiv s \cdot \Delta a   & \pmod{\ell} 
-\label{eq:third} \\
-  \Delta \mathit{w2} - \Delta \mathit{na} & \equiv t \cdot \Delta \mathit{ch} 
-      &&& \pmod{\ell} 
-\label{eq:fourth} 
-\end{align}
-
-Consider the left equalities in~\eqref{eq:first} and~\eqref{eq:firsta}.
-Define $w \deq \alpha + n \cdot \gamma \in \ZZ$ 
-and $a \deq \alpha_0 + n \cdot \gamma_0 \in \ZZ$.
-For any pair of accepting transcripts such as $(\mathcal{T}_1, \mathcal{T}_2)$,
-it must be the case that 
-$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ and
-$\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$. 
-The extractor knows $\Delta w,\ \Delta a$, and $\Delta \mathit{ch}$.
-Hence, by constructing a polynomial number of such accepting transcript pairs, 
-the extractor can recover $w, a \in \ZZ$ using the chinese remainder theorem.
-
-Next, consider the left equation in~\eqref{eq:second}.
-Using $w = \alpha + n \cdot \gamma$ and
-$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ gives
-$\Delta \mathit{w2} \equiv w^2 \cdot \Delta \mathit{ch} \pmod{\ell}$.
-
-Using $\Delta \mathit{w2} \equiv w^2 \cdot \Delta \mathit{ch} \pmod{\ell}$
-in~\eqref{eq:fourth}
-gives $\Delta \mathit{na} \equiv (w^2 - t) \cdot \Delta \mathit{ch} \pmod{\ell}$. 
-Finally, the left equality in~\eqref{eq:third} 
-gives $(w^2 - t)\cdot \Delta \mathit{ch} \equiv n \cdot \Delta a \pmod{\ell}$.
-Using $\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$
-we obtain that the extracted integers $w$ and $a$ must satisfy
-$(w^2 - t)\cdot \Delta \mathit{ch} \equiv 
-      n \cdot a \cdot \Delta \mathit{ch} \pmod{\ell}$.  
-Since $\ell$ does not divide $\Delta \mathit{ch}$ with overwhelming
-probability, we obtain that $w^2 - t \equiv n \cdot a \pmod{\ell}$.
-Since this equality holds modulo a random $\ell \in \primes$ 
-with overwhelming probability, 
-the equality $w^2 - t = n \cdot a$ must hold over the integers,
-as required.   Note that this implies that $a \neq 0$.
-
-Because $a \neq 0$, the extractor can obtain $(n \bmod \ell)$
-from the left equality in~\eqref{eq:third}, and thus extract $n \in \ZZ$ by
-repeating this procedure over several $\ell$ and then using the chinese
-remainder theorem.  
-Similarly, it can extract $s \in \ZZ$ from
-the right equality in~\eqref{eq:third}.   
-It thus obtains a witness $(n, s, w, a)$ 
-for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}, as required.
-\end{proof}
-
-\subsection{The concrete airdrop system}\label{sec:rsa:airdrop}
-
-The airdrop system is obtained by applying the Fiat-Shamir
-heuristic to the protocol from the previous section. 
-The concrete private airdrop system works as follows:
-
-\paragraph{Algorithm $\text{sendTokens}(\PK)$:}
-To send tokens to an RSA public key $\PK = (n, e)$ do:
-\begin{itemize}
-\item 
-generate a random $s \rgets \range{G}$.
-
-\item 
-output $(c, s)$ where $c \gets g^n \cdot h^s \in \GG$.
-\end{itemize}
-
-\medskip\noindent 
-The following two notes can help optimize the scheme:
-\begin{itemize}
-\item[$-$] $s$ is privately sent to the owner of $\PK$, for example
-by encrypting $s$ under $\PK$ to obtain a ciphertext $c'$ and
-publishing this $c'$ somewhere, not necessarily on the blockchain.  There is
-a public association between $c'$ and $\PK$ (e.g., via a hash table),
-so that the owner of $\PK$ can easily find $c'$.  One can include
-$H(c)$ in the plaintext encrypted in $c'$ to help the owner of $\PK$
-quickly find $c$.
-
-\item[$-$] One can generate $s$ 
-as $s \gets H(s')$ where $s'$ is a random 256-bit value and $H$ is a hash
-function $H:\{0,1\}^{256} \to \range{G}$.  The ciphertext $c'$ is
-an encryption of $s'$, instead of $s$, which can shrink~$c'$.
-\end{itemize}
-
-\paragraph{Algorithm $\text{sign}(\SK, (c, s), m)$:}  
-To withdraw the funds associated with the token $c$ the user
-signs a withdrawal message $m$ using the RSA secret key $\SK = (n,p,q)$ 
-as follows:
-\begin{itemize}
-\item find a prime $2 \leq t \leq \lambda$  such that $t$ is a quadratic 
-residue in $\ZZ_n$.
-
-\item find integers $(w,a)$ such that $w^2 = t + a n$ in $\ZZ$
-           (i.e. $w$ is a square root of $t$ modulo $n$)
-
-\item choose a random $s_1 \rgets \range{N}$ and compute
-           $c_1 \gets g^w \cdot h^{s_1} \in \GG$.
-
-\item choose a random $s_2 \rgets \range{N}$ and compute
-           $c_2 \gets g^a \cdot h^{s_2} \in \GG$.
-
-\item choose a random $\rv \rgets \range{2^{2\lambda}}^8$
-and compute $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$,
-where $\phi$ is the homomorphism defined in~\eqref{eq:hom}.
-
-\item compute $\mathit{seed} \gets \text{Hash}(m, \GG, g, h, c, c_1, c_2, t, \Rv$).
-
-\item
-use a $\text{PRNG}(\mathit{seed})$ to generate $(\mathit{ch}, \ell)$, 
-where $\mathit{ch} \in \range{2^\lambda}$ and $\ell \in \primes$.
-
-\item compute:
-\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
-    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^8, \quad
-    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^8, \quad
-    \Zv_q \gets \phi(\zv_q) \in \GG^4 \times \ZZ.
-\]
-
-\item output the signature 
-$\mathit{sig} = (c_1, c_2, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$.
-\end{itemize}
-
-\paragraph{Algorithm $\text{verify}(c, m, \mathit{sig}):$}
-Verify that $\mathit{sig} = (c_1, c_2, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$ 
-is a valid signature for token~$c$ on the message~$m$.
-\begin{itemize}
-\item reject if $t \notin \range{\lambda}$ or $t$ is not a prime.
-
-\item with $T \deq (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ$, 
-compute $\Rv' \gets \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$.
-
-\item compute $\mathit{seed}' \gets \text{Hash}(m, \GG, g, h, c, c_1, c_2, t, \Rv'$)
-
-\item use a $\text{PRNG}(\mathit{seed}')$ to generate 
-  $\mathit{ch}' \in \range{2^\lambda}$ and $\ell' \in \primes$. \\
-Since $\ell$ is
-  included in the signature, the verifier does not need to search for
-  a prime, but can instead verify that the given $\ell$ is prime and
-  is not too far from the base starting point of the prime search.
-
-\item accept iff $\mathit{ch}' = \mathit{ch}$ and $\ell' = \ell$.
-\end{itemize}
-
-\paragraph{Proof of security.}
-We need to prove two things: 
-(1) privacy in the random oracle model:
-there is a simulator that can generate a properly distributed
-signature just given $c$ and $m$, and 
-(2) security: an attacker that is given $c$ along with a 
-signature on some message $m$
-with respect to $c$ and can generate a valid signature for $c$ on
-some message $m' \neq m$ can be used to compute $\sqrt{t} \in \ZZ_n$
-for some $2 \leq t \leq 1000$.
-
-\paragraph{Proof of privacy.}
-TODO: Use the ZK proof of the interactive protocol. Easy corollary.
-
-\paragraph{Proof of security.}
-TODO: Use the extractor of the interactive protocol. Easy corollary.
-
-\bibliographystyle{alpha}
-\bibliography{paper}
-
-\end{document}

### 2019-01-18 paper/ecdsa.tex
split paper into separate files per section

\section{A private airdrop to ECDSA and Schnorr public keys}\label{sec:dsa}

\rsw{this section is, for now, a quick note-stash}

As a warm-up, we present a PAD scheme for ECDSA.
\RSW{generalize to EdDSA and prime-field DSA just here, throughout, or just in a comment at the end?}
%
%\paragraph{Notation}
Let $\HH$ be a cyclic group of prime order $q$, generated by $\gHH$.
\RSW{I don't love $\HH$ and I loathe $\gHH$, but maybe it's helpful to use
    different notation here than in the next section. Or maybe this notation
    is so standard it doesn't matter.}

\rsw{maybe standardize on party names, i.e., `challenger' (or `sender'),
    `signer' (or `receiver'), and `verifier'.}

\paragraph{Algorithm $\text{sendTokens}(\PK)$:} To send tokens to public key $\PK = \gHH^x$, do:
\begin{itemize}
\item generate a random $s \rgets \range{q}$
\item output $(c, s)$ where $c \gets \PK\cdot\gHH^s$
\end{itemize}

\rsw{consider moving first optimization note from \S\ref{sec:rsa:airdrop} to
    here (and check for redundancy with sendTokens def in \S\ref{sec:defs}).}

\paragraph{Algorithm $\text{sign}(\SK, (c, s), m)$:}
To withdraw the funds associated with the token $c$ the user signs a
    withdrawal message $m$ using the fact that
$c = \PK\cdot\gHH^s = \gHH^{x+s}$.
%
That is, $c$ is a public key with corresponding secret key $x + s$, and
    $\mathit{sig}$ is an ECDSA signature on $m$ under this key.

\paragraph{Algorithm $\text{verify}(c, m, \mathit{sig}):$}
Accept iff $\mathit{sig}$ is a valid ECDSA signature on $m$ under $c$.

\paragraph{Security}
\begin{itemize}
\item Privacy: if $s$ is uniformly random, then $(c, x+s)$ is a random ECDSA key pair.

\item Unforgeability: an adversary that can forge can break ECDSA (pick $s$ s.t. $c$ is target pubkey)
\end{itemize}

### 2019-01-18 paper/intro.tex
split paper into separate files per section

--- 2019-01-18 paper/paper.tex
@@
-%\def\useacmstyle{}
-\def\submissionpapernumber{$\infty$}
-
-\ifx\useacmstyle\undefined
-    \documentclass[11pt]{article}
-    \usepackage{fullpage}
-    \usepackage[hidelinks]{hyperref}
-\else
-    \documentclass[sigconf,anonymous]{acmart}
-    \fancyhf{}
-    \fancyhead[C]{Anonymous submission \submissionpapernumber\ to ACM CCS 2019}
-    \fancyfoot[C]{\thepage}
-    \setcopyright{none}
-    \acmConference{ACM CCS Submission}{2019 Feb 05}{}
-    \acmYear{2019}
-    \settopmatter{printacmref=false, printccs=false, printfolios=false}
-\fi
-
-\usepackage[dvipsnames]{xcolor}
-\usepackage{amsthm,amsmath,amsfonts,amssymb,amstext,mathtools}
-\usepackage{macros}
-\usepackage[normalem]{ulem}
-\usepackage{peanutgallery}
-
-\begin{document}
-
-\title{An Airdrop That Preserves Recipient Privacy}
-\author{Dan Boneh \and Chris Jeffrey \and Joseph Poon \and Riad Wahby}
-
-\maketitle
-
-\begin{abstract}
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section{Introduction}\label{sec:intro}
 
@@
     to $n$ with opening $s$.
-
-\emph{Question:} do we need to make $E()$ deterministic for this to work
-    (say, $r = H(\PK)$ in OAEP)?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Private airdrop: definitions}\label{sec:defs}
-
-A private airdrop (PAD) system is a triple of efficient algorithms:
-\begin{itemize}
-\item $\text{sendTokens}(\PK) \to (c, s)$:
-Generates a token $c$ to be posted on the blockchain,
-and a secret~$s$ given to the recipient via a private channel.
-For example, an encryption of $s$ under $\PK$ can be posted
-to the blockchain.   The posted encrypted $s$ is not associated with 
-the token $c$. 
-\RSW{is it necessary to suggest that Enc(s) appear on the blockchain? It could just be posted publicly, since it doesn't need to be remembered for long.}
-
-\item $\text{sign}(\SK, (c, s), m) \to \text{sig}$:
-Signs a message $m$ indicating that the token $c$ is spent.
-
-\item $\text{verify}(c, m, \text{sig}) \to \{\text{yes},\text{no}\}:$
-Verify that a signature $\text{sig}$ on token $c$ is valid.
-\end{itemize}
-
-TODO: Need to state security properties formally: 
-(1) $c$ and $\text{sig}$ should reveal nothing about $\PK$,
-(2) without $\SK$ we have existential unforgeability under a 
-(one-time) chosen message attack.
-
-\subsection{Zero-knowledge proofs in generic groups}
-
-TODO: Need overview of zero-knowledge in generic groups.
-
-\paragraph{The representation extraction lemma.}
-Let $\adv$ be an algorithm that outputs 
-a generic group element $u \in \GG$.
-The following lemma shows that there is an extractor that
-can extract from $\adv$ an integer representation of $u$
-relative to a supplied set of group generators.
-Moreover, this integer representation is unique.
-
-\begin{lemma}[Unique representation extraction in generic groups]
-\label{lem:unique}
-Let $\adv_1, \adv_2$ be two randomized algorithms that interact
-with group oracles for a generic group $\GG$ of unknown order.
-For $i=1,2$, algorithm $\adv_i$ outputs $u_i \in \GG$.
-Suppose that each algorithm makes at most $q$ type-1 queries
-and let $g_1,\ldots,g_q \in \GG$ be the returned random group elements.
-
-There is an extractor $\bdv$ that emulates 
-the generic group oracles for $\adv_1$ and $\adv_2$
-such that for $i=1,2$ when $\bdv$ interacts with $\adv_i$ 
-the following holds with overwhelming probability:
-if $\adv_i$ outputs $u_i \in \GG$ 
-then the extractor $\bdv_i$ outputs a representation
-$\alpha_{i,1},\ldots,\alpha_{i,q} \in \ZZ$
-such that $u_i = g_1^{\alpha_{i,1}} \cdots g_q^{\alpha_{i,q}}$.
-Moreover, if $u_1 = u_2$ then the two representations are the same,
-namely $\alpha_{1,j} = \alpha_{2,j}$ for $j=1,\ldots,q$. 
-\end{lemma}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{pad_ecdsa.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A private airdrop to RSA public keys}\label{sec:rsa}
-
-From here we use the following notations:
-$\lambda$ is the security parameter (e.g., $\lambda = 128$), 
-$\range{\ell}$ denotes the set of integers $\{0,1,\ldots,\ell-1\}$, and 
-$\primes$ is a set of size $2^\lambda$ 
-containing the smallest $2^\lambda$ odd primes. 
-%
-We will also need a set of public parameters that include the description
-of a cyclic group $\GG$ of unknown order.  We let $g$ and $h$ be two
-random generators of $\GG$ where the discrete-log of $g$ base $h$ is unknown.
-
-\subsection{Proving knowledge of the factorization of a hidden integer}\label{sec:rsa:proving}
-
-Let $n \in \range{N}$ be a secret integer 
-where $N$ is a public upper bound on~$n$.
-We will also assume that $N > \abs{\GG} \cdot 2^{2 \lambda}$.
-Let $c \deq g^n \cdot h^s \in \GG$ be a commitment to $n$, 
-where $s \rgets \range{N}$.  
-We first develop a zero knowledge protocol for proving knowledge of the
-factorization of~$n$ given only $c$.
-
-To prove knowledge of the factorization of $n$ the prover
-proves knowledge of a $w \in \range{N}$ such that $w^2 \equiv t \pmod{n}$
-for some small public prime $t \in \ZZ$, namely $2 \leq t \leq \lambda$.
-That is, we provide a ZKPK for the relation
-\begin{equation} \label{eq:lang}
-  \mathcal{R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
-                              (n, s, w, a) \in \range{N}^4 \Bigr)  \ \ 
-        \text{s.t.}\ \ 
-                \begin{aligned}
-                        c   & = g^n \cdot h^s \ \ \text{in $\GG$}, \\
-                        w^2 & = t + a \cdot n \ \ \text{in $\ZZ$}, \\
-                        2 & \leq t \leq \lambda  \ \textrm{a prime}
-                \end{aligned}  \right\}.
-\end{equation}
-Here $(c, t)$ is a statement and $(n, s, w, a)$ is a witness.
-The integer relation $w^2 = t + a\cdot n$ proves that 
-$w^2 \equiv t \pmod{n}$, as required.
-We note that a ZKPK for~\eqref{eq:lang} proves that $t \in \ZZ$ is a quadratic
-residue modulo the committed $n$.  Leaking this bit of information about $n$
-does not interfere with the application to a secure
-\RSW{``secure'' $\rightarrow$ ``private''?}
-airdrop.
-
-\medskip\noindent
-Protocol $\prot{P}$: The ZKPK protocol for~\eqref{eq:lang} 
-between the prover $P$ and the verifier $V$ works as follows:
-\begin{itemize}
-\item input:  the verifier has $(c, t) \in \GG \times \range{\lambda}$ and 
-the prover has $(c, t, n, s, w, a) \in \GG \times \range{N}^5$
-
-\item Prover $P$ chooses two random integers $s_1, s_2 \rgets \range{N}$ and computes
-       $c_1 \gets g^w \cdot h^{s_1} \in \GG$ and $c_2 \gets g^a \cdot h^{s_2} \in \GG$.
-
-\item Next, define a homomorphism $\phi:\ZZ^8 \to \GG^4 \times \ZZ$ 
-parameterized by $g, h, c, c_1, c_2$ as follows:
-\begin{equation} \label{eq:hom}
-  \phi\left(\!\!\begin{array}{l}
-                w, \mathit{w2}, \mathit{s1}, a, \\
-                \mathit{na}, \mathit{s1w}, \mathit{sa}, \mathit{s2}
-      \end{array}  \!\!\!\right) \deq
-      \Bigl(\ 
-       g^w \cdot h^{\mathit{s1}},\ \ \ 
-       g^a \cdot h^{\mathit{s2}},\ \ \ 
-       g^{\mathit{w2}} \cdot h^{\mathit{s1w}} / c_1^w,\ \ \ 
-       g^{\mathit{na}} \cdot h^{\mathit{sa}} / c^a,\ \ \ 
-       \mathit{w2} - \mathit{na}\ \Bigr)
-\end{equation}
-It is easy to see that $\phi$ is a group homomorphism.
-The range of $\phi$ is the group $\GG^4 \times \ZZ$.  
-We will write the group operation in this group multiplicatively.
-That is, if $(a_i, b_i, c_i, d_i, e_i) \in \GG^4 \times \ZZ$ for $i=1,2$
-then 
-\[  (a_1, b_1, c_1, d_1, e_1) \cdot (a_2, b_2, c_2, d_2, e_2) \deq 
-      (a_1 a_2,\ b_1 b_2,\ c_1 c_2,\ d_1 d_2,\ e_1 + e_2).  \]
-
-We need a ZKPK for a $\phi$-preimage of 
-$T \deq (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ$. 
-In other words, we need a zero-knowledge proof of knowledge for a vector 
-$\vv' = (w', \mathit{w2}', s_1', a', \mathit{na}', 
-              \mathit{s1w}', \mathit{sa}', s_2') \in \ZZ^8$ 
-such that 
-\[   \phi(\vv') = T = (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ.  \]
-Doing so proves 
-that $c_1$ is a commitment to $w' \in \ZZ$, 
-that $c_2$ is a commitment to $a' \in \ZZ$,
-that $\mathit{w2}' = (w')^2$, and 
-that $\mathit{na}' = a' \cdot n$ for some integer $a'$.
-Then the last relation proves that $(w')^2 - a' \cdot n = t$ in $\ZZ$,
-as required.
-
-We design a ZKPK for a $\phi$-preimage 
-using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}.
-Here the verifier is given $T \in \GG^4 \times \ZZ$ 
-and the prover is given $T$ and $\vv \in \ZZ^8$
-where $\phi(\vv) = T$. 
-The protocol works as follows:
-\begin{enumerate}
-\item The prover sets
-    $\rv \deq (r_w, r_\mathit{w2}, r_\mathit{s1}, r_a, r_\mathit{na}, 
-                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$ where
-\[ r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}} 
-    \quad\text{and}\quad
-   r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N}.
-\]
-The prover computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
-and sends $(c_1, c_2, \Rv)$ to the verifier.
-
-\item The verifier chooses challenges $\mathit{ch} \rgets \range{2^\lambda}$
-and $\ell \rgets \primes$. \\
-It sends $(\ell, \mathit{ch})$ to the prover.
-
-\item The prover computes:
-\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
-    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^8, \quad
-    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^8, \quad
-    \Zv_q \gets \phi(\zv_q)  
-\]
-and sends $(\Zv_q, \zv_\ell) \in (\GG^4 \times \ZZ) \times \range{\ell}^8$ 
-to the verifier.
-
-\item The verifier accepts if 
-$\ \Zv_q^\ell \cdot \phi(\zv_\ell) = T^\mathit{ch} \cdot \Rv\ $ in 
-$\GG^4 \times \ZZ$.
-\end{enumerate}
-\end{itemize}
-
-\paragraph{Comment 1.}
-The protocol is insecure if the group $\GG$ contains a non-identity
-element of known order.  {\bf TODO: describe an attack.}
-In the multiplicative group $(\ZZ/n)^*$ the
-element $-1$ has order~$2$, and hence the protocol is insecure in this
-group.  Instead, we can work in the quotient group $(\ZZ/n)/\{\pm 1\}$, 
-where elements are represented as integers in the interval $[1,n/2]$
-and the product of $x$ and $y$ is defined as 
-$\abs{x \cdot y} = \min(z, n-z)$ where $z = (x \cdot y \bmod n)$.
-In this group $-1$ is the same as $1$, and presumably there are
-no other known elements of known order.
-
-\paragraph{Comment 2.}
-The commitment $c_2$ to the integer $a$ is necessary for soundness,
-and in particular to ensure that $a$ is an integer.  If $c_2$ along
-with $s_2$ and the second coordinate of $\phi$ are eliminated then there
-is an attack where an adversarial prover can prove knowledge of
-$(\sqrt{3} \bmod n)$ using $a = 1/n$ and $w = 2$.
-
-\paragraph{Comment 3.}
-There is a seemingly simpler method to prove that one knows the
-factorization of~$n$, namely, prove that one knows $p$ such that $p$
-divides $n$.  That is, instead of committing to $w$ we would commit to
-$p$ and $q$ and then prove that $p \cdot q = n$. But we would
-also need to prove that the committed $p$ is not one of 
-$\{1, -1, n, -n\}$, and that results in a longer proof.
-
-\paragraph{Proof of security.}
-We need to prove the protocol above is zero-knowledge and a 
-proof of knowledge.
-
-\begin{theorem}
-Protocol $\prot{P}$ is a zero-knowledge protocol
-for the relation $\mathcal{R}_{g,h}$ in \eqref{eq:lang}.
-\end{theorem}
-
-\begin{proof}
-The simulator takes $(c, t)$ as input and outputs the simulated transcript
-$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
-\begin{alg}
-\> choose random $c_1, c_2 \rgets \GG,\ \ \ell \rgets \primes$, and
-\ \ $\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
-\lnum \label{ln:randvell}
-\> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
-\lnum \label{ln:randZ}
-\> choose random $Z_1, Z_2, Z_3, Z_4 \rgets \GG$, \\
-\lnum \label{ln:sim}
-\> choose random $\hat{r}_\text{w2}, \hat{r}_\text{na} \rgets \range{2^{2\lambda}}$
-and set $Z_5 \deq \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor \hat{r}_\text{w2} / \ell \rfloor - \lfloor \hat{r}_\text{na} / \ell \rfloor \in \ZZ$, \\
-\> set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5)  \in \GG^4 \times \ZZ$, \AlgSep
-\lnum \label{ln:computeR}
-\> compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
-\> output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
-\end{alg}
-We show the simulated transcript is distributed statistically close
-to an accepting transcript of a real protocol execution.
-In a real transcript we know that $c_1$ and $c_2$ are uniform in $\GG$. 
-Hence, observe that the simulated $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
-exactly as in a real transcript.  It remains to show that the same holds
-for $\zv_\ell, \Zv_q$, and $\Rv$. 
-In an interaction with a real prover the quantities
-$r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
-are chosen uniformly in $\range{N}$.
-Consider one such value $r \rgets \range{N}$.
-Because $N$ is much larger than $\abs{\GG} \cdot \ell$
-we know that the pair
-$\big(\lfloor r/\ell \rfloor \bmod \abs{\GG},\ (r \bmod \ell) \big)$
-is statistically close to uniform in $\range{\,\abs{\GG}\,} \times \range{\ell}$.
-Similarly,  in a real transcript
-each of $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa}$
-is chosen uniformly in $\range{2^{2 \lambda}}$ and therefore
-each of these four values modulo $\ell$
-is statistically close to uniform in $\range{\ell}$.
-It follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
-in a real transcript, is statistically close to uniform 
-in $\range{\ell}^8$, as in line~\eqref{ln:randvell} in the simulation.
-
-Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly.
-Observe that each of the first four components of $\Zv_q$ is a group
-element in $\GG$ that is randomized by
-$h^{\lfloor r_\mathit{s1} / \ell \rfloor},\
- h^{\lfloor r_\mathit{s2} / \ell \rfloor},\
- h^{\lfloor r_\mathit{s1w} / \ell \rfloor},\
- h^{\lfloor r_\mathit{sa} / \ell \rfloor}$ respectively.
-Because these four exponents are close to uniform in $\range{\,\abs{\GG}\,}$ and are
-independent of everything else in the transcript, it follows that
-in a real transcript $Z_1, Z_2, Z_3, Z_4$ are independent and close to uniform elements in $\GG$.  This is also how these elements are chosen 
-on line~\eqref{ln:randZ} in the simulation.
-
-It remains to argue that $Z_5 \in \ZZ$ is simulated correctly. 
-In a real transcript this $Z_5$ is computed as 
-$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
-          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
-Because $\mathit{w2} - \mathit{na} = t$, we have
-that $Z_5$ in a real transcript satisfies
-\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
-where $\Delta \in \{0, \pm 1\}$. 
-In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
-and $\lfloor r_\text{na} / \ell \rfloor$ 
-are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
-as in the simulated $Z_5$ on line~\eqref{ln:sim}.
-The only difference is that the real distribution is shifted by $\Delta$
-where as the simulated distribution is not.  
-However this $\Delta$ only negligibly affects the statistical distance
-between the real and simulated distributions. 
-The reason is that in both distributions, 
-every possible value in the range of $Z_5$, 
-except possibly at the edges, 
-is obtained from the same number of values 
-for the pair $(r_\text{w2}, r_\text{na})$. 
-%%  would be good to prove this as a general lemma.
-We thus conclude that the simulated $Z_5$ in~\eqref{ln:sim} 
-is statistically close to its real distribution.
-
-Finally, because the simulated $c_1, c_2, \ell, \mathit{ch}, \Zv_q, \zv_\ell$
-are all distributed statistically close to a real transcript, 
-it must be the case that the computed $\Rv$ 
-on line~\eqref{ln:computeR} is also distributed as in 
-a real transcript. 
-\end{proof}
-
-\iffalse
-An optimization: the transcript elements $Z_3, Z_4 \in \GG$ can be simulated
-in a similar fashion to how we simulated $Z_5$ in the proof above.
-That is, 
-$Z_3 = g^{\lfloor r_\text{w2} / \ell \rfloor} h^{\lfloor r_\text{s1w} / \ell \rfloor} / c_1^{\lfloor r_\text{w} / \ell \rfloor} \in \GG$
-and 
-$Z_4 = g^{\lfloor r_\text{na} / \ell \rfloor} h^{\lfloor r_\text{sa} / \ell \rfloor} / c^{\lfloor r_\text{a} / \ell \rfloor} \in \GG$,
-where 
-$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}$
-are chosen uniformly in $\range{N}$. 
-It is not difficult to see that these $Z_3$ and $Z_4$ 
-are distributed as in a real transcript.
-This method of simulation can be used to make the protocol slightly more
-efficient because the randomizers 
-$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa} \in \ZZ$
-do not need to be uniform in the entire interval $\range{N}$.
-It suffices to choose these six values 
-uniformly in $\range{2^{2 \lambda}}$, which is a smaller interval
-than $\range{N}$.  Only $r_\text{s1}$ and $r_\text{s2}$ need to be chosen
-uniformly in the full interval $\range{N}$ so that $Z_1$ and $Z_2$ are uniform
-in $\GG$. 
-However, if the simulator chooses $c_1, c_2 \in \GG$ randomly in $\GG$
-so that it knows
-their $\ell$-th root, then even $Z_1$ and $Z_2$ can also be simulated as above.
-Then $r_\text{s1}$ and $r_\text{s2}$ can also be chosen uniformly
-in the range $\range{2^{2 \lambda}}$.
-In other words, the simulator works by first 
-choosing a random $\rv \gets \range{2^{2\lambda}}^8$,
-computing $\Rv \gets \phi(\rv)$, and then
-solving for $\Zv_q \in \GG^4 \times \ZZ$. 
-\fi
-
-\begin{definition}
-We say that algorithm $\mathcal{G}$ is an \defn{honest instance
-generator} for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}
-if it chooses integers $n, s, t$, and outputs $(c, t)$ where
-$c \deq g^n h^s \in \GG$. 
-\end{definition}
-
-\begin{theorem}
-Protocol $\prot{P}$ is an argument of knowledge
-for the relation $\mathcal{R}_{g,h}$ in \eqref{eq:lang} 
-for instances $(c,t)$ generated by an honest instance
-generator $\mathcal{G}$,
-when the group $\GG$ is a modeled as a generic group of unknown order. 
-\end{theorem}
-
-\begin{proof}
-We construct an extractor that given an instance $(c,t)$ 
-generated by $\mathcal{G}$,
-interacts with a convincing prover and outputs a witness $(n, s, w, a)$ 
-for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}. 
-The protocol transcript is $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
-The extractor rewinds the prover and obtains two
-accepting transcripts
-$\mathcal{T}_1 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
-and 
-$\mathcal{T}_2 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
-Dividing the corresponding verification equations one by the other
-we obtain
-\[   (\Zv_q / \Zv_q')^\ell \cdot \phi(\zv_\ell - \zv_\ell') = 
-          T^{\mathit{ch} - \mathit{ch}'}. \]
-Let $\zv_\ell - \zv_\ell' = \Big(\Delta w,\ \Delta \mathit{w2},\ \Delta \mathit{s1},\ \Delta a,\ \Delta \mathit{na},\ \Delta \mathit{s1w},\ \Delta \mathit{sa},\ \Delta \mathit{s2} \Big) \in \ZZ^8$ and let $\Delta \mathit{ch} = \mathit{ch} - \mathit{ch}' \in \ZZ$.
-Then plugging this into the definition of $\phi$ we obtain
-\begin{equation} \label{eq:messy}
-      (\Zv_q / \Zv_q')^\ell \cdot
-      \left(\begin{array}{l}
-       g^{\Delta w} \cdot h^{\Delta \mathit{s1}},\ \ \ 
-       g^{\Delta a} \cdot h^{\Delta \mathit{s2}},\ \ \ 
-       g^{\Delta \mathit{w2}} \cdot h^{\Delta \mathit{s1w}} / c_1^{\Delta w}, \\
-       g^{\Delta \mathit{na}} \cdot h^{\Delta \mathit{sa}} / c^{\Delta a},\ \ \ 
-       \Delta \mathit{w2} - \Delta \mathit{na}\ 
-       \end{array} \right)
-          = \left(\begin{array}{l}c_1, \ c_2, \ 1, \\ 1,\ t \end{array}\right)^{\Delta \mathit{ch}}.
-\end{equation}
-Let $\Zv_q / \Zv_q' = (z_1, z_2, z_3, z_4, z_5)$ 
-where $z_1, z_2, z_3, z_4 \in \GG$ and $z_5 \in \ZZ$.  
-In a generic group $\GG$, the group elements $z_1, z_2, z_3, z_4$ 
-must satisfy $z_i = g^{\alpha_i} h^{\beta_i} c^{\gamma_i} \prod_{j=1}^q g_j^{\delta_{i,j}}$
-for $i=1,2,3,4$, 
-and $c_1 = g^{\alpha} h^{\beta} c^\gamma \prod_{j=1}^q g_j^{\delta_{j}}$,
-and $c_2 = g^{\alpha_0} h^{\beta_0} c^\gamma \prod_{j=1}^q g_j^{\delta_{0,j}}$,
-where the extractor knows all the listed integer exponents.
-Here $g_1,\ldots,g_q \in \GG$ are random group elements produced in response
-to a generic group oracle query for a random group element.
-
-It now follows from~\eqref{eq:messy}, and from $c = g^n h^s$, 
-and by uniqueness of representation in generic groups (\Lemma{lem:unique}),
-that the following equations must hold over the integers:
-\begin{align*}
-  \ell \cdot (\alpha_1 + n \cdot \gamma_1) + \Delta w & = (\alpha + n \cdot \gamma) \cdot \Delta \mathit{ch},  &
-  \ell \cdot (\beta_1 + s \cdot \gamma_1) + \Delta \mathit{s1} & = (\beta + s \cdot \gamma) \cdot \Delta \mathit{ch}  
-\\
-  \ell \cdot (\alpha_2 + n \cdot \gamma_2) + \Delta a & = (\alpha_0 + n \cdot \gamma_0) \cdot \Delta \mathit{ch},  &
-  \ell \cdot (\beta_2 + s \cdot \gamma_2) + \Delta \mathit{s2} & = (\beta_0 + s \cdot \gamma_0) \cdot \Delta \mathit{ch}  
-\\
-  \ell \cdot (\alpha_3 + n \cdot \gamma_3) + \Delta \mathit{w2} & = (\alpha + n \cdot \gamma) \cdot \Delta w,  &
-  \ell \cdot (\beta_3 + s \cdot \gamma_3) + \Delta \mathit{s1w} & = (\beta + s \cdot \gamma) \cdot \Delta w   
-\\
-  \ell \cdot (\alpha_4 + n \cdot \gamma_4) + \Delta \mathit{na} & = n \cdot \Delta a,  & 
-  \ell \cdot (\beta_4 + s \cdot \gamma_4) + \Delta \mathit{sa} & = s \cdot \Delta a   
-\\
-  \ell \cdot z_4 + \Delta \mathit{w2} - \Delta \mathit{na} & = t \cdot \Delta \mathit{ch} 
-\end{align*}
-The extractor knows all these values except for $n$ and $s$.
-Reducing these equations modulo $\ell$ gives:
-\begin{align}
-  \Delta w & \equiv (\alpha + n \cdot \gamma) \cdot \Delta \mathit{ch}  &
-  \Delta \mathit{s1} & \equiv (\beta + s \cdot \gamma) \cdot \Delta \mathit{ch}  & \pmod{\ell} 
-\label{eq:first} \\
-  \Delta a & \equiv (\alpha_0 + n \cdot \gamma_0) \cdot \Delta \mathit{ch}  &
-  \Delta \mathit{s2} & \equiv (\beta_0 + s \cdot \gamma_0) \cdot \Delta \mathit{ch}  & \pmod{\ell} 
-\label{eq:firsta} \\
-  \Delta \mathit{w2} & \equiv (\alpha + n \cdot \gamma) \cdot \Delta w  &
-  \Delta \mathit{s1w} & \equiv (\beta + s \cdot \gamma) \cdot \Delta w   & \pmod{\ell} 
-\label{eq:second} \\
-  \Delta \mathit{na} & \equiv n \cdot \Delta a  & 
-  \Delta \mathit{sa} & \equiv s \cdot \Delta a   & \pmod{\ell} 
-\label{eq:third} \\
-  \Delta \mathit{w2} - \Delta \mathit{na} & \equiv t \cdot \Delta \mathit{ch} 
-      &&& \pmod{\ell} 
-\label{eq:fourth} 
-\end{align}
-
-Consider the left equalities in~\eqref{eq:first} and~\eqref{eq:firsta}.
-Define $w \deq \alpha + n \cdot \gamma \in \ZZ$ 
-and $a \deq \alpha_0 + n \cdot \gamma_0 \in \ZZ$.
-For any pair of accepting transcripts such as $(\mathcal{T}_1, \mathcal{T}_2)$,
-it must be the case that 
-$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ and
-$\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$. 
-The extractor knows $\Delta w,\ \Delta a$, and $\Delta \mathit{ch}$.
-Hence, by constructing a polynomial number of such accepting transcript pairs, 
-the extractor can recover $w, a \in \ZZ$ using the chinese remainder theorem.
-
-Next, consider the left equation in~\eqref{eq:second}.
-Using $w = \alpha + n \cdot \gamma$ and
-$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ gives
-$\Delta \mathit{w2} \equiv w^2 \cdot \Delta \mathit{ch} \pmod{\ell}$.
-
-Using $\Delta \mathit{w2} \equiv w^2 \cdot \Delta \mathit{ch} \pmod{\ell}$
-in~\eqref{eq:fourth}
-gives $\Delta \mathit{na} \equiv (w^2 - t) \cdot \Delta \mathit{ch} \pmod{\ell}$. 
-Finally, the left equality in~\eqref{eq:third} 
-gives $(w^2 - t)\cdot \Delta \mathit{ch} \equiv n \cdot \Delta a \pmod{\ell}$.
-Using $\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$
-we obtain that the extracted integers $w$ and $a$ must satisfy
-$(w^2 - t)\cdot \Delta \mathit{ch} \equiv 
-      n \cdot a \cdot \Delta \mathit{ch} \pmod{\ell}$.  
-Since $\ell$ does not divide $\Delta \mathit{ch}$ with overwhelming
-probability, we obtain that $w^2 - t \equiv n \cdot a \pmod{\ell}$.
-Since this equality holds modulo a random $\ell \in \primes$ 
-with overwhelming probability, 
-the equality $w^2 - t = n \cdot a$ must hold over the integers,
-as required.   Note that this implies that $a \neq 0$.
-
-Because $a \neq 0$, the extractor can obtain $(n \bmod \ell)$
-from the left equality in~\eqref{eq:third}, and thus extract $n \in \ZZ$ by
-repeating this procedure over several $\ell$ and then using the chinese
-remainder theorem.  
-Similarly, it can extract $s \in \ZZ$ from
-the right equality in~\eqref{eq:third}.   
-It thus obtains a witness $(n, s, w, a)$ 
-for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}, as required.
-\end{proof}
-
-\subsection{The concrete airdrop system}\label{sec:rsa:airdrop}
-
-The airdrop system is obtained by applying the Fiat-Shamir
-heuristic to the protocol from the previous section. 
-The concrete private airdrop system works as follows:
-
-\paragraph{Algorithm $\text{sendTokens}(\PK)$:}
-To send tokens to an RSA public key $\PK = (n, e)$ do:
-\begin{itemize}
-\item 
-generate a random $s \rgets \range{G}$.
-
-\item 
-output $(c, s)$ where $c \gets g^n \cdot h^s \in \GG$.
-\end{itemize}
-
-\medskip\noindent 
-The following two notes can help optimize the scheme:
-\begin{itemize}
-\item[$-$] $s$ is privately sent to the owner of $\PK$, for example
-by encrypting $s$ under $\PK$ to obtain a ciphertext $c'$ and
-publishing this $c'$ somewhere, not necessarily on the blockchain.  There is
-a public association between $c'$ and $\PK$ (e.g., via a hash table),
-so that the owner of $\PK$ can easily find $c'$.  One can include
-$H(c)$ in the plaintext encrypted in $c'$ to help the owner of $\PK$
-quickly find $c$.
-
-\item[$-$] One can generate $s$ 
-as $s \gets H(s')$ where $s'$ is a random 256-bit value and $H$ is a hash
-function $H:\{0,1\}^{256} \to \range{G}$.  The ciphertext $c'$ is
-an encryption of $s'$, instead of $s$, which can shrink~$c'$.
-\end{itemize}
-
-\paragraph{Algorithm $\text{sign}(\SK, (c, s), m)$:}  
-To withdraw the funds associated with the token $c$ the user
-signs a withdrawal message $m$ using the RSA secret key $\SK = (n,p,q)$ 
-as follows:
-\begin{itemize}
-\item find a prime $2 \leq t \leq \lambda$  such that $t$ is a quadratic 
-residue in $\ZZ_n$.
-
-\item find integers $(w,a)$ such that $w^2 = t + a n$ in $\ZZ$
-           (i.e. $w$ is a square root of $t$ modulo $n$)
-
-\item choose a random $s_1 \rgets \range{N}$ and compute
-           $c_1 \gets g^w \cdot h^{s_1} \in \GG$.
-
-\item choose a random $s_2 \rgets \range{N}$ and compute
-           $c_2 \gets g^a \cdot h^{s_2} \in \GG$.
-
-\item choose a random $\rv \rgets \range{2^{2\lambda}}^8$
-and compute $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$,
-where $\phi$ is the homomorphism defined in~\eqref{eq:hom}.
-
-\item compute $\mathit{seed} \gets \text{Hash}(m, \GG, g, h, c, c_1, c_2, t, \Rv$).
-
-\item
-use a $\text{PRNG}(\mathit{seed})$ to generate $(\mathit{ch}, \ell)$, 
-where $\mathit{ch} \in \range{2^\lambda}$ and $\ell \in \primes$.
-
-\item compute:
-\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
-    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^8, \quad
-    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^8, \quad
-    \Zv_q \gets \phi(\zv_q) \in \GG^4 \times \ZZ.
-\]
-
-\item output the signature 
-$\mathit{sig} = (c_1, c_2, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$.
-\end{itemize}
-
-\paragraph{Algorithm $\text{verify}(c, m, \mathit{sig}):$}
-Verify that $\mathit{sig} = (c_1, c_2, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$ 
-is a valid signature for token~$c$ on the message~$m$.
-\begin{itemize}
-\item reject if $t \notin \range{\lambda}$ or $t$ is not a prime.
-
-\item with $T \deq (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ$, 
-compute $\Rv' \gets \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$.
-
-\item compute $\mathit{seed}' \gets \text{Hash}(m, \GG, g, h, c, c_1, c_2, t, \Rv'$)
-
-\item use a $\text{PRNG}(\mathit{seed}')$ to generate 
-  $\mathit{ch}' \in \range{2^\lambda}$ and $\ell' \in \primes$. \\
-Since $\ell$ is
-  included in the signature, the verifier does not need to search for
-  a prime, but can instead verify that the given $\ell$ is prime and
-  is not too far from the base starting point of the prime search.
-
-\item accept iff $\mathit{ch}' = \mathit{ch}$ and $\ell' = \ell$.
-\end{itemize}
-
-\paragraph{Proof of security.}
-We need to prove two things: 
-(1) privacy in the random oracle model:
-there is a simulator that can generate a properly distributed
-signature just given $c$ and $m$, and 
-(2) security: an attacker that is given $c$ along with a 
-signature on some message $m$
-with respect to $c$ and can generate a valid signature for $c$ on
-some message $m' \neq m$ can be used to compute $\sqrt{t} \in \ZZ_n$
-for some $2 \leq t \leq 1000$.
-
-\paragraph{Proof of privacy.}
-TODO: Use the ZK proof of the interactive protocol. Easy corollary.
-
-\paragraph{Proof of security.}
-TODO: Use the extractor of the interactive protocol. Easy corollary.
-
-\bibliographystyle{alpha}
-\bibliography{paper}
-
-\end{document}

### 2019-01-18 paper/paper.tex
split paper into separate files per section

@@
 \usepackage[normalem]{ulem}
+\usepackage{nicefrac}
 \usepackage{peanutgallery}
-
-\begin{document}
 
@@
 
+\begin{document}
+
 \maketitle
 
-\begin{abstract}
-\end{abstract}
+\input{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\input{intro}
 
-More to come.
+\input{defs}
 
-\rsw{stashed note from talk with DB}
-Simultaneously using the schemes of \S\ref{sec:dsa} and \S\ref{sec:rsa}
-    on the same blockchain allows distinguishing between users based on
-    key type.
-Can work around this using generic ZKPK, at substantial performance cost.
-(Alt narrative: talk about generic ZKPK first, then specialize to get better
-    perf. at cost of distinguishing.)
+\input{ecdsa.tex}
 
-\rsw{stashed note from chat with Henry and Dima}
-Possible objection: why doesn't sender just generate a bunch of phony keys
-    and send all money to self?
-In other words, why is this scheme better, from the verifiers' point of view,
-    than the naive approach, i.e., sender generating a fresh key pair and
-    sending secret key to recipient?
-(Note that while the naive approach does not have existential unforgeability,
-    that property does not prevent self-dealing if sender knows secret key.
-Another way to say this is that the security property we need for the
-    airdrop-to-Github-users case is stronger than existential unforgeability.)
-
-One answer: for each RSA key $\PK = (n, e)$ to be paid, sender publishes
-    the challenge $c = g^nh^s$ and (separately, i.e., without revealing
-    correspondence) sender also publishes
-$(\PK, s')$, $s' = E(\PK, (c',s)))$, $c' = H(g^nh^s)$.
-In other words, the sender publishes a list of purported airdrop recipients
-    separately from the list of airdrop challenge tokens.
-
-If sender was dishonest with respect to any key, i.e., if for some $(\PK,
-    s')$, any of $s', c', c, s$ is invalid, key's owner can reveal $(\hat{c}',
-    \hat{s}) = D(\PK, s')$.
-Then verifiers check that $s' = E(\PK, (\hat{c}', \hat{s}))$, and that
-    either no corresponding $c$ exists, or that $c$ is not a commitment
-    to $n$ with opening $s$.
-
-\emph{Question:} do we need to make $E()$ deterministic for this to work
-    (say, $r = H(\PK)$ in OAEP)?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Private airdrop: definitions}\label{sec:defs}
-
-A private airdrop (PAD) system is a triple of efficient algorithms:
-\begin{itemize}
-\item $\text{sendTokens}(\PK) \to (c, s)$:
-Generates a token $c$ to be posted on the blockchain,
-and a secret~$s$ given to the recipient via a private channel.
-For example, an encryption of $s$ under $\PK$ can be posted
-to the blockchain.   The posted encrypted $s$ is not associated with 
-the token $c$. 
-\RSW{is it necessary to suggest that Enc(s) appear on the blockchain? It could just be posted publicly, since it doesn't need to be remembered for long.}
-
-\item $\text{sign}(\SK, (c, s), m) \to \text{sig}$:
-Signs a message $m$ indicating that the token $c$ is spent.
-
-\item $\text{verify}(c, m, \text{sig}) \to \{\text{yes},\text{no}\}:$
-Verify that a signature $\text{sig}$ on token $c$ is valid.
-\end{itemize}
-
-TODO: Need to state security properties formally: 
-(1) $c$ and $\text{sig}$ should reveal nothing about $\PK$,
-(2) without $\SK$ we have existential unforgeability under a 
-(one-time) chosen message attack.
-
-\subsection{Zero-knowledge proofs in generic groups}
-
-TODO: Need overview of zero-knowledge in generic groups.
-
-\paragraph{The representation extraction lemma.}
-Let $\adv$ be an algorithm that outputs 
-a generic group element $u \in \GG$.
-The following lemma shows that there is an extractor that
-can extract from $\adv$ an integer representation of $u$
-relative to a supplied set of group generators.
-Moreover, this integer representation is unique.
-
-\begin{lemma}[Unique representation extraction in generic groups]
-\label{lem:unique}
-Let $\adv_1, \adv_2$ be two randomized algorithms that interact
-with group oracles for a generic group $\GG$ of unknown order.
-For $i=1,2$, algorithm $\adv_i$ outputs $u_i \in \GG$.
-Suppose that each algorithm makes at most $q$ type-1 queries
-and let $g_1,\ldots,g_q \in \GG$ be the returned random group elements.
-
-There is an extractor $\bdv$ that emulates 
-the generic group oracles for $\adv_1$ and $\adv_2$
-such that for $i=1,2$ when $\bdv$ interacts with $\adv_i$ 
-the following holds with overwhelming probability:
-if $\adv_i$ outputs $u_i \in \GG$ 
-then the extractor $\bdv_i$ outputs a representation
-$\alpha_{i,1},\ldots,\alpha_{i,q} \in \ZZ$
-such that $u_i = g_1^{\alpha_{i,1}} \cdots g_q^{\alpha_{i,q}}$.
-Moreover, if $u_1 = u_2$ then the two representations are the same,
-namely $\alpha_{1,j} = \alpha_{2,j}$ for $j=1,\ldots,q$. 
-\end{lemma}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{pad_ecdsa.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A private airdrop to RSA public keys}\label{sec:rsa}
-
-From here we use the following notations:
-$\lambda$ is the security parameter (e.g., $\lambda = 128$), 
-$\range{\ell}$ denotes the set of integers $\{0,1,\ldots,\ell-1\}$, and 
-$\primes$ is a set of size $2^\lambda$ 
-containing the smallest $2^\lambda$ odd primes. 
-%
-We will also need a set of public parameters that include the description
-of a cyclic group $\GG$ of unknown order.  We let $g$ and $h$ be two
-random generators of $\GG$ where the discrete-log of $g$ base $h$ is unknown.
-
-\subsection{Proving knowledge of the factorization of a hidden integer}\label{sec:rsa:proving}
-
-Let $n \in \range{N}$ be a secret integer 
-where $N$ is a public upper bound on~$n$.
-We will also assume that $N > \abs{\GG} \cdot 2^{2 \lambda}$.
-Let $c \deq g^n \cdot h^s \in \GG$ be a commitment to $n$, 
-where $s \rgets \range{N}$.  
-We first develop a zero knowledge protocol for proving knowledge of the
-factorization of~$n$ given only $c$.
-
-To prove knowledge of the factorization of $n$ the prover
-proves knowledge of a $w \in \range{N}$ such that $w^2 \equiv t \pmod{n}$
-for some small public prime $t \in \ZZ$, namely $2 \leq t \leq \lambda$.
-That is, we provide a ZKPK for the relation
-\begin{equation} \label{eq:lang}
-  \mathcal{R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
-                              (n, s, w, a) \in \range{N}^4 \Bigr)  \ \ 
-        \text{s.t.}\ \ 
-                \begin{aligned}
-                        c   & = g^n \cdot h^s \ \ \text{in $\GG$}, \\
-                        w^2 & = t + a \cdot n \ \ \text{in $\ZZ$}, \\
-                        2 & \leq t \leq \lambda  \ \textrm{a prime}
-                \end{aligned}  \right\}.
-\end{equation}
-Here $(c, t)$ is a statement and $(n, s, w, a)$ is a witness.
-The integer relation $w^2 = t + a\cdot n$ proves that 
-$w^2 \equiv t \pmod{n}$, as required.
-We note that a ZKPK for~\eqref{eq:lang} proves that $t \in \ZZ$ is a quadratic
-residue modulo the committed $n$.  Leaking this bit of information about $n$
-does not interfere with the application to a secure
-\RSW{``secure'' $\rightarrow$ ``private''?}
-airdrop.
-
-\medskip\noindent
-Protocol $\prot{P}$: The ZKPK protocol for~\eqref{eq:lang} 
-between the prover $P$ and the verifier $V$ works as follows:
-\begin{itemize}
-\item input:  the verifier has $(c, t) \in \GG \times \range{\lambda}$ and 
-the prover has $(c, t, n, s, w, a) \in \GG \times \range{N}^5$
-
-\item Prover $P$ chooses two random integers $s_1, s_2 \rgets \range{N}$ and computes
-       $c_1 \gets g^w \cdot h^{s_1} \in \GG$ and $c_2 \gets g^a \cdot h^{s_2} \in \GG$.
-
-\item Next, define a homomorphism $\phi:\ZZ^8 \to \GG^4 \times \ZZ$ 
-parameterized by $g, h, c, c_1, c_2$ as follows:
-\begin{equation} \label{eq:hom}
-  \phi\left(\!\!\begin{array}{l}
-                w, \mathit{w2}, \mathit{s1}, a, \\
-                \mathit{na}, \mathit{s1w}, \mathit{sa}, \mathit{s2}
-      \end{array}  \!\!\!\right) \deq
-      \Bigl(\ 
-       g^w \cdot h^{\mathit{s1}},\ \ \ 
-       g^a \cdot h^{\mathit{s2}},\ \ \ 
-       g^{\mathit{w2}} \cdot h^{\mathit{s1w}} / c_1^w,\ \ \ 
-       g^{\mathit{na}} \cdot h^{\mathit{sa}} / c^a,\ \ \ 
-       \mathit{w2} - \mathit{na}\ \Bigr)
-\end{equation}
-It is easy to see that $\phi$ is a group homomorphism.
-The range of $\phi$ is the group $\GG^4 \times \ZZ$.  
-We will write the group operation in this group multiplicatively.
-That is, if $(a_i, b_i, c_i, d_i, e_i) \in \GG^4 \times \ZZ$ for $i=1,2$
-then 
-\[  (a_1, b_1, c_1, d_1, e_1) \cdot (a_2, b_2, c_2, d_2, e_2) \deq 
-      (a_1 a_2,\ b_1 b_2,\ c_1 c_2,\ d_1 d_2,\ e_1 + e_2).  \]
-
-We need a ZKPK for a $\phi$-preimage of 
-$T \deq (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ$. 
-In other words, we need a zero-knowledge proof of knowledge for a vector 
-$\vv' = (w', \mathit{w2}', s_1', a', \mathit{na}', 
-              \mathit{s1w}', \mathit{sa}', s_2') \in \ZZ^8$ 
-such that 
-\[   \phi(\vv') = T = (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ.  \]
-Doing so proves 
-that $c_1$ is a commitment to $w' \in \ZZ$, 
-that $c_2$ is a commitment to $a' \in \ZZ$,
-that $\mathit{w2}' = (w')^2$, and 
-that $\mathit{na}' = a' \cdot n$ for some integer $a'$.
-Then the last relation proves that $(w')^2 - a' \cdot n = t$ in $\ZZ$,
-as required.
-
-We design a ZKPK for a $\phi$-preimage 
-using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}.
-Here the verifier is given $T \in \GG^4 \times \ZZ$ 
-and the prover is given $T$ and $\vv \in \ZZ^8$
-where $\phi(\vv) = T$. 
-The protocol works as follows:
-\begin{enumerate}
-\item The prover sets
-    $\rv \deq (r_w, r_\mathit{w2}, r_\mathit{s1}, r_a, r_\mathit{na}, 
-                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$ where
-\[ r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}} 
-    \quad\text{and}\quad
-   r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N}.
-\]
-The prover computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
-and sends $(c_1, c_2, \Rv)$ to the verifier.
-
-\item The verifier chooses challenges $\mathit{ch} \rgets \range{2^\lambda}$
-and $\ell \rgets \primes$. \\
-It sends $(\ell, \mathit{ch})$ to the prover.
-
-\item The prover computes:
-\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
-    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^8, \quad
-    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^8, \quad
-    \Zv_q \gets \phi(\zv_q)  
-\]
-and sends $(\Zv_q, \zv_\ell) \in (\GG^4 \times \ZZ) \times \range{\ell}^8$ 
-to the verifier.
-
-\item The verifier accepts if 
-$\ \Zv_q^\ell \cdot \phi(\zv_\ell) = T^\mathit{ch} \cdot \Rv\ $ in 
-$\GG^4 \times \ZZ$.
-\end{enumerate}
-\end{itemize}
-
-\paragraph{Comment 1.}
-The protocol is insecure if the group $\GG$ contains a non-identity
-element of known order.  {\bf TODO: describe an attack.}
-In the multiplicative group $(\ZZ/n)^*$ the
-element $-1$ has order~$2$, and hence the protocol is insecure in this
-group.  Instead, we can work in the quotient group $(\ZZ/n)/\{\pm 1\}$, 
-where elements are represented as integers in the interval $[1,n/2]$
-and the product of $x$ and $y$ is defined as 
-$\abs{x \cdot y} = \min(z, n-z)$ where $z = (x \cdot y \bmod n)$.
-In this group $-1$ is the same as $1$, and presumably there are
-no other known elements of known order.
-
-\paragraph{Comment 2.}
-The commitment $c_2$ to the integer $a$ is necessary for soundness,
-and in particular to ensure that $a$ is an integer.  If $c_2$ along
-with $s_2$ and the second coordinate of $\phi$ are eliminated then there
-is an attack where an adversarial prover can prove knowledge of
-$(\sqrt{3} \bmod n)$ using $a = 1/n$ and $w = 2$.
-
-\paragraph{Comment 3.}
-There is a seemingly simpler method to prove that one knows the
-factorization of~$n$, namely, prove that one knows $p$ such that $p$
-divides $n$.  That is, instead of committing to $w$ we would commit to
-$p$ and $q$ and then prove that $p \cdot q = n$. But we would
-also need to prove that the committed $p$ is not one of 
-$\{1, -1, n, -n\}$, and that results in a longer proof.
-
-\paragraph{Proof of security.}
-We need to prove the protocol above is zero-knowledge and a 
-proof of knowledge.
-
-\begin{theorem}
-Protocol $\prot{P}$ is a zero-knowledge protocol
-for the relation $\mathcal{R}_{g,h}$ in \eqref{eq:lang}.
-\end{theorem}
-
-\begin{proof}
-The simulator takes $(c, t)$ as input and outputs the simulated transcript
-$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
-\begin{alg}
-\> choose random $c_1, c_2 \rgets \GG,\ \ \ell \rgets \primes$, and
-\ \ $\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
-\lnum \label{ln:randvell}
-\> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
-\lnum \label{ln:randZ}
-\> choose random $Z_1, Z_2, Z_3, Z_4 \rgets \GG$, \\
-\lnum \label{ln:sim}
-\> choose random $\hat{r}_\text{w2}, \hat{r}_\text{na} \rgets \range{2^{2\lambda}}$
-and set $Z_5 \deq \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor \hat{r}_\text{w2} / \ell \rfloor - \lfloor \hat{r}_\text{na} / \ell \rfloor \in \ZZ$, \\
-\> set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5)  \in \GG^4 \times \ZZ$, \AlgSep
-\lnum \label{ln:computeR}
-\> compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
-\> output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
-\end{alg}
-We show the simulated transcript is distributed statistically close
-to an accepting transcript of a real protocol execution.
-In a real transcript we know that $c_1$ and $c_2$ are uniform in $\GG$. 
-Hence, observe that the simulated $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
-exactly as in a real transcript.  It remains to show that the same holds
-for $\zv_\ell, \Zv_q$, and $\Rv$. 
-In an interaction with a real prover the quantities
-$r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
-are chosen uniformly in $\range{N}$.
-Consider one such value $r \rgets \range{N}$.
-Because $N$ is much larger than $\abs{\GG} \cdot \ell$
-we know that the pair
-$\big(\lfloor r/\ell \rfloor \bmod \abs{\GG},\ (r \bmod \ell) \big)$
-is statistically close to uniform in $\range{\,\abs{\GG}\,} \times \range{\ell}$.
-Similarly,  in a real transcript
-each of $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa}$
-is chosen uniformly in $\range{2^{2 \lambda}}$ and therefore
-each of these four values modulo $\ell$
-is statistically close to uniform in $\range{\ell}$.
-It follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
-in a real transcript, is statistically close to uniform 
-in $\range{\ell}^8$, as in line~\eqref{ln:randvell} in the simulation.
-
-Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly.
-Observe that each of the first four components of $\Zv_q$ is a group
-element in $\GG$ that is randomized by
-$h^{\lfloor r_\mathit{s1} / \ell \rfloor},\
- h^{\lfloor r_\mathit{s2} / \ell \rfloor},\
- h^{\lfloor r_\mathit{s1w} / \ell \rfloor},\
- h^{\lfloor r_\mathit{sa} / \ell \rfloor}$ respectively.
-Because these four exponents are close to uniform in $\range{\,\abs{\GG}\,}$ and are
-independent of everything else in the transcript, it follows that
-in a real transcript $Z_1, Z_2, Z_3, Z_4$ are independent and close to uniform elements in $\GG$.  This is also how these elements are chosen 
-on line~\eqref{ln:randZ} in the simulation.
-
-It remains to argue that $Z_5 \in \ZZ$ is simulated correctly. 
-In a real transcript this $Z_5$ is computed as 
-$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
-          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
-Because $\mathit{w2} - \mathit{na} = t$, we have
-that $Z_5$ in a real transcript satisfies
-\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
-where $\Delta \in \{0, \pm 1\}$. 
-In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
-and $\lfloor r_\text{na} / \ell \rfloor$ 
-are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
-as in the simulated $Z_5$ on line~\eqref{ln:sim}.
-The only difference is that the real distribution is shifted by $\Delta$
-where as the simulated distribution is not.  
-However this $\Delta$ only negligibly affects the statistical distance
-between the real and simulated distributions. 
-The reason is that in both distributions, 
-every possible value in the range of $Z_5$, 
-except possibly at the edges, 
-is obtained from the same number of values 
-for the pair $(r_\text{w2}, r_\text{na})$. 
-%%  would be good to prove this as a general lemma.
-We thus conclude that the simulated $Z_5$ in~\eqref{ln:sim} 
-is statistically close to its real distribution.
-
-Finally, because the simulated $c_1, c_2, \ell, \mathit{ch}, \Zv_q, \zv_\ell$
-are all distributed statistically close to a real transcript, 
-it must be the case that the computed $\Rv$ 
-on line~\eqref{ln:computeR} is also distributed as in 
-a real transcript. 
-\end{proof}
-
-\iffalse
-An optimization: the transcript elements $Z_3, Z_4 \in \GG$ can be simulated
-in a similar fashion to how we simulated $Z_5$ in the proof above.
-That is, 
-$Z_3 = g^{\lfloor r_\text{w2} / \ell \rfloor} h^{\lfloor r_\text{s1w} / \ell \rfloor} / c_1^{\lfloor r_\text{w} / \ell \rfloor} \in \GG$
-and 
-$Z_4 = g^{\lfloor r_\text{na} / \ell \rfloor} h^{\lfloor r_\text{sa} / \ell \rfloor} / c^{\lfloor r_\text{a} / \ell \rfloor} \in \GG$,
-where 
-$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}$
-are chosen uniformly in $\range{N}$. 
-It is not difficult to see that these $Z_3$ and $Z_4$ 
-are distributed as in a real transcript.
-This method of simulation can be used to make the protocol slightly more
-efficient because the randomizers 
-$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa} \in \ZZ$
-do not need to be uniform in the entire interval $\range{N}$.
-It suffices to choose these six values 
-uniformly in $\range{2^{2 \lambda}}$, which is a smaller interval
-than $\range{N}$.  Only $r_\text{s1}$ and $r_\text{s2}$ need to be chosen
-uniformly in the full interval $\range{N}$ so that $Z_1$ and $Z_2$ are uniform
-in $\GG$. 
-However, if the simulator chooses $c_1, c_2 \in \GG$ randomly in $\GG$
-so that it knows
-their $\ell$-th root, then even $Z_1$ and $Z_2$ can also be simulated as above.
-Then $r_\text{s1}$ and $r_\text{s2}$ can also be chosen uniformly
-in the range $\range{2^{2 \lambda}}$.
-In other words, the simulator works by first 
-choosing a random $\rv \gets \range{2^{2\lambda}}^8$,
-computing $\Rv \gets \phi(\rv)$, and then
-solving for $\Zv_q \in \GG^4 \times \ZZ$. 
-\fi
-
-\begin{definition}
-We say that algorithm $\mathcal{G}$ is an \defn{honest instance
-generator} for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}
-if it chooses integers $n, s, t$, and outputs $(c, t)$ where
-$c \deq g^n h^s \in \GG$. 
-\end{definition}
-
-\begin{theorem}
-Protocol $\prot{P}$ is an argument of knowledge
-for the relation $\mathcal{R}_{g,h}$ in \eqref{eq:lang} 
-for instances $(c,t)$ generated by an honest instance
-generator $\mathcal{G}$,
-when the group $\GG$ is a modeled as a generic group of unknown order. 
-\end{theorem}
-
-\begin{proof}
-We construct an extractor that given an instance $(c,t)$ 
-generated by $\mathcal{G}$,
-interacts with a convincing prover and outputs a witness $(n, s, w, a)$ 
-for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}. 
-The protocol transcript is $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
-The extractor rewinds the prover and obtains two
-accepting transcripts
-$\mathcal{T}_1 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
-and 
-$\mathcal{T}_2 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
-Dividing the corresponding verification equations one by the other
-we obtain
-\[   (\Zv_q / \Zv_q')^\ell \cdot \phi(\zv_\ell - \zv_\ell') = 
-          T^{\mathit{ch} - \mathit{ch}'}. \]
-Let $\zv_\ell - \zv_\ell' = \Big(\Delta w,\ \Delta \mathit{w2},\ \Delta \mathit{s1},\ \Delta a,\ \Delta \mathit{na},\ \Delta \mathit{s1w},\ \Delta \mathit{sa},\ \Delta \mathit{s2} \Big) \in \ZZ^8$ and let $\Delta \mathit{ch} = \mathit{ch} - \mathit{ch}' \in \ZZ$.
-Then plugging this into the definition of $\phi$ we obtain
-\begin{equation} \label{eq:messy}
-      (\Zv_q / \Zv_q')^\ell \cdot
-      \left(\begin{array}{l}
-       g^{\Delta w} \cdot h^{\Delta \mathit{s1}},\ \ \ 
-       g^{\Delta a} \cdot h^{\Delta \mathit{s2}},\ \ \ 
-       g^{\Delta \mathit{w2}} \cdot h^{\Delta \mathit{s1w}} / c_1^{\Delta w}, \\
-       g^{\Delta \mathit{na}} \cdot h^{\Delta \mathit{sa}} / c^{\Delta a},\ \ \ 
-       \Delta \mathit{w2} - \Delta \mathit{na}\ 
-       \end{array} \right)
-          = \left(\begin{array}{l}c_1, \ c_2, \ 1, \\ 1,\ t \end{array}\right)^{\Delta \mathit{ch}}.
-\end{equation}
-Let $\Zv_q / \Zv_q' = (z_1, z_2, z_3, z_4, z_5)$ 
-where $z_1, z_2, z_3, z_4 \in \GG$ and $z_5 \in \ZZ$.  
-In a generic group $\GG$, the group elements $z_1, z_2, z_3, z_4$ 
-must satisfy $z_i = g^{\alpha_i} h^{\beta_i} c^{\gamma_i} \prod_{j=1}^q g_j^{\delta_{i,j}}$
-for $i=1,2,3,4$, 
-and $c_1 = g^{\alpha} h^{\beta} c^\gamma \prod_{j=1}^q g_j^{\delta_{j}}$,
-and $c_2 = g^{\alpha_0} h^{\beta_0} c^\gamma \prod_{j=1}^q g_j^{\delta_{0,j}}$,
-where the extractor knows all the listed integer exponents.
-Here $g_1,\ldots,g_q \in \GG$ are random group elements produced in response
-to a generic group oracle query for a random group element.
-
-It now follows from~\eqref{eq:messy}, and from $c = g^n h^s$, 
-and by uniqueness of representation in generic groups (\Lemma{lem:unique}),
-that the following equations must hold over the integers:
-\begin{align*}
-  \ell \cdot (\alpha_1 + n \cdot \gamma_1) + \Delta w & = (\alpha + n \cdot \gamma) \cdot \Delta \mathit{ch},  &
-  \ell \cdot (\beta_1 + s \cdot \gamma_1) + \Delta \mathit{s1} & = (\beta + s \cdot \gamma) \cdot \Delta \mathit{ch}  
-\\
-  \ell \cdot (\alpha_2 + n \cdot \gamma_2) + \Delta a & = (\alpha_0 + n \cdot \gamma_0) \cdot \Delta \mathit{ch},  &
-  \ell \cdot (\beta_2 + s \cdot \gamma_2) + \Delta \mathit{s2} & = (\beta_0 + s \cdot \gamma_0) \cdot \Delta \mathit{ch}  
-\\
-  \ell \cdot (\alpha_3 + n \cdot \gamma_3) + \Delta \mathit{w2} & = (\alpha + n \cdot \gamma) \cdot \Delta w,  &
-  \ell \cdot (\beta_3 + s \cdot \gamma_3) + \Delta \mathit{s1w} & = (\beta + s \cdot \gamma) \cdot \Delta w   
-\\
-  \ell \cdot (\alpha_4 + n \cdot \gamma_4) + \Delta \mathit{na} & = n \cdot \Delta a,  & 
-  \ell \cdot (\beta_4 + s \cdot \gamma_4) + \Delta \mathit{sa} & = s \cdot \Delta a   
-\\
-  \ell \cdot z_4 + \Delta \mathit{w2} - \Delta \mathit{na} & = t \cdot \Delta \mathit{ch} 
-\end{align*}
-The extractor knows all these values except for $n$ and $s$.
-Reducing these equations modulo $\ell$ gives:
-\begin{align}
-  \Delta w & \equiv (\alpha + n \cdot \gamma) \cdot \Delta \mathit{ch}  &
-  \Delta \mathit{s1} & \equiv (\beta + s \cdot \gamma) \cdot \Delta \mathit{ch}  & \pmod{\ell} 
-\label{eq:first} \\
-  \Delta a & \equiv (\alpha_0 + n \cdot \gamma_0) \cdot \Delta \mathit{ch}  &
-  \Delta \mathit{s2} & \equiv (\beta_0 + s \cdot \gamma_0) \cdot \Delta \mathit{ch}  & \pmod{\ell} 
-\label{eq:firsta} \\
-  \Delta \mathit{w2} & \equiv (\alpha + n \cdot \gamma) \cdot \Delta w  &
-  \Delta \mathit{s1w} & \equiv (\beta + s \cdot \gamma) \cdot \Delta w   & \pmod{\ell} 
-\label{eq:second} \\
-  \Delta \mathit{na} & \equiv n \cdot \Delta a  & 
-  \Delta \mathit{sa} & \equiv s \cdot \Delta a   & \pmod{\ell} 
-\label{eq:third} \\
-  \Delta \mathit{w2} - \Delta \mathit{na} & \equiv t \cdot \Delta \mathit{ch} 
-      &&& \pmod{\ell} 
-\label{eq:fourth} 
-\end{align}
-
-Consider the left equalities in~\eqref{eq:first} and~\eqref{eq:firsta}.
-Define $w \deq \alpha + n \cdot \gamma \in \ZZ$ 
-and $a \deq \alpha_0 + n \cdot \gamma_0 \in \ZZ$.
-For any pair of accepting transcripts such as $(\mathcal{T}_1, \mathcal{T}_2)$,
-it must be the case that 
-$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ and
-$\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$. 
-The extractor knows $\Delta w,\ \Delta a$, and $\Delta \mathit{ch}$.
-Hence, by constructing a polynomial number of such accepting transcript pairs, 
-the extractor can recover $w, a \in \ZZ$ using the chinese remainder theorem.
-
-Next, consider the left equation in~\eqref{eq:second}.
-Using $w = \alpha + n \cdot \gamma$ and
-$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ gives
-$\Delta \mathit{w2} \equiv w^2 \cdot \Delta \mathit{ch} \pmod{\ell}$.
-
-Using $\Delta \mathit{w2} \equiv w^2 \cdot \Delta \mathit{ch} \pmod{\ell}$
-in~\eqref{eq:fourth}
-gives $\Delta \mathit{na} \equiv (w^2 - t) \cdot \Delta \mathit{ch} \pmod{\ell}$. 
-Finally, the left equality in~\eqref{eq:third} 
-gives $(w^2 - t)\cdot \Delta \mathit{ch} \equiv n \cdot \Delta a \pmod{\ell}$.
-Using $\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$
-we obtain that the extracted integers $w$ and $a$ must satisfy
-$(w^2 - t)\cdot \Delta \mathit{ch} \equiv 
-      n \cdot a \cdot \Delta \mathit{ch} \pmod{\ell}$.  
-Since $\ell$ does not divide $\Delta \mathit{ch}$ with overwhelming
-probability, we obtain that $w^2 - t \equiv n \cdot a \pmod{\ell}$.
-Since this equality holds modulo a random $\ell \in \primes$ 
-with overwhelming probability, 
-the equality $w^2 - t = n \cdot a$ must hold over the integers,
-as required.   Note that this implies that $a \neq 0$.
-
-Because $a \neq 0$, the extractor can obtain $(n \bmod \ell)$
-from the left equality in~\eqref{eq:third}, and thus extract $n \in \ZZ$ by
-repeating this procedure over several $\ell$ and then using the chinese
-remainder theorem.  
-Similarly, it can extract $s \in \ZZ$ from
-the right equality in~\eqref{eq:third}.   
-It thus obtains a witness $(n, s, w, a)$ 
-for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}, as required.
-\end{proof}
-
-\subsection{The concrete airdrop system}\label{sec:rsa:airdrop}
-
-The airdrop system is obtained by applying the Fiat-Shamir
-heuristic to the protocol from the previous section. 
-The concrete private airdrop system works as follows:
-
-\paragraph{Algorithm $\text{sendTokens}(\PK)$:}
-To send tokens to an RSA public key $\PK = (n, e)$ do:
-\begin{itemize}
-\item 
-generate a random $s \rgets \range{G}$.
-
-\item 
-output $(c, s)$ where $c \gets g^n \cdot h^s \in \GG$.
-\end{itemize}
-
-\medskip\noindent 
-The following two notes can help optimize the scheme:
-\begin{itemize}
-\item[$-$] $s$ is privately sent to the owner of $\PK$, for example
-by encrypting $s$ under $\PK$ to obtain a ciphertext $c'$ and
-publishing this $c'$ somewhere, not necessarily on the blockchain.  There is
-a public association between $c'$ and $\PK$ (e.g., via a hash table),
-so that the owner of $\PK$ can easily find $c'$.  One can include
-$H(c)$ in the plaintext encrypted in $c'$ to help the owner of $\PK$
-quickly find $c$.
-
-\item[$-$] One can generate $s$ 
-as $s \gets H(s')$ where $s'$ is a random 256-bit value and $H$ is a hash
-function $H:\{0,1\}^{256} \to \range{G}$.  The ciphertext $c'$ is
-an encryption of $s'$, instead of $s$, which can shrink~$c'$.
-\end{itemize}
-
-\paragraph{Algorithm $\text{sign}(\SK, (c, s), m)$:}  
-To withdraw the funds associated with the token $c$ the user
-signs a withdrawal message $m$ using the RSA secret key $\SK = (n,p,q)$ 
-as follows:
-\begin{itemize}
-\item find a prime $2 \leq t \leq \lambda$  such that $t$ is a quadratic 
-residue in $\ZZ_n$.
-
-\item find integers $(w,a)$ such that $w^2 = t + a n$ in $\ZZ$
-           (i.e. $w$ is a square root of $t$ modulo $n$)
-
-\item choose a random $s_1 \rgets \range{N}$ and compute
-           $c_1 \gets g^w \cdot h^{s_1} \in \GG$.
-
-\item choose a random $s_2 \rgets \range{N}$ and compute
-           $c_2 \gets g^a \cdot h^{s_2} \in \GG$.
-
-\item choose a random $\rv \rgets \range{2^{2\lambda}}^8$
-and compute $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$,
-where $\phi$ is the homomorphism defined in~\eqref{eq:hom}.
-
-\item compute $\mathit{seed} \gets \text{Hash}(m, \GG, g, h, c, c_1, c_2, t, \Rv$).
-
-\item
-use a $\text{PRNG}(\mathit{seed})$ to generate $(\mathit{ch}, \ell)$, 
-where $\mathit{ch} \in \range{2^\lambda}$ and $\ell \in \primes$.
-
-\item compute:
-\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
-    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^8, \quad
-    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^8, \quad
-    \Zv_q \gets \phi(\zv_q) \in \GG^4 \times \ZZ.
-\]
-
-\item output the signature 
-$\mathit{sig} = (c_1, c_2, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$.
-\end{itemize}
-
-\paragraph{Algorithm $\text{verify}(c, m, \mathit{sig}):$}
-Verify that $\mathit{sig} = (c_1, c_2, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$ 
-is a valid signature for token~$c$ on the message~$m$.
-\begin{itemize}
-\item reject if $t \notin \range{\lambda}$ or $t$ is not a prime.
-
-\item with $T \deq (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ$, 
-compute $\Rv' \gets \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$.
-
-\item compute $\mathit{seed}' \gets \text{Hash}(m, \GG, g, h, c, c_1, c_2, t, \Rv'$)
-
-\item use a $\text{PRNG}(\mathit{seed}')$ to generate 
-  $\mathit{ch}' \in \range{2^\lambda}$ and $\ell' \in \primes$. \\
-Since $\ell$ is
-  included in the signature, the verifier does not need to search for
-  a prime, but can instead verify that the given $\ell$ is prime and
-  is not too far from the base starting point of the prime search.
-
-\item accept iff $\mathit{ch}' = \mathit{ch}$ and $\ell' = \ell$.
-\end{itemize}
-
-\paragraph{Proof of security.}
-We need to prove two things: 
-(1) privacy in the random oracle model:
-there is a simulator that can generate a properly distributed
-signature just given $c$ and $m$, and 
-(2) security: an attacker that is given $c$ along with a 
-signature on some message $m$
-with respect to $c$ and can generate a valid signature for $c$ on
-some message $m' \neq m$ can be used to compute $\sqrt{t} \in \ZZ_n$
-for some $2 \leq t \leq 1000$.
-
-\paragraph{Proof of privacy.}
-TODO: Use the ZK proof of the interactive protocol. Easy corollary.
-
-\paragraph{Proof of security.}
-TODO: Use the extractor of the interactive protocol. Easy corollary.
+\input{rsa.tex}
 

### 2019-01-18 paper/rsa.tex
split paper into separate files per section

--- 2019-01-09 paper.tex
@@
-\documentclass[11pt]{article}
-\usepackage[hidelinks]{hyperref}
-\usepackage{amsthm,amsmath,amsfonts,amssymb,amstext,mathtools}
-\usepackage{fullpage}
-\usepackage{macros}
-
-\begin{document}
-
-\title{An Airdrop That Preserves Recipient Privacy}
-\author{Dan Boneh \and Riad Wahby}
-
-\maketitle
-
-\begin{abstract}
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-
-More to come.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Private airdrop: definitions}
-
-A private airdrop (PAD) system is a triple of efficient algorithms:
-\begin{itemize}
-\item $\text{sendTokens}(\PK) \to (c, s)$:
-Generates a token $c$ to be posted on the blockchain,
-and a secret~$s$ given to the recipient via a private channel.
-For example, an encryption of $s$ under $\PK$ can be posted
-to the blockchain.   The posted encrypted $s$ is not associated with 
-the token $c$.
-
-\item $\text{sign}(\SK, (c, s), m) \to \text{sig}$:
-Signs a message $m$ indicating that the token $c$ is spent.
-
-\item $\text{verify}(c, m, \text{sig}) \to \{\text{yes},\text{no}\}:$
-Verify that a signature $\text{sig}$ on token $c$ is valid.
-\end{itemize}
-
-TODO: Need to state security properties formally: 
-(1) $c$ and $\text{sig}$ should reveal nothing about $\PK$,
-(2) without $\SK$ we have existential unforgeability under a 
-(one-time) chosen message attack.
-
-\subsection{Zero-knowledge proofs in generic groups}
-
-TODO: Need overview of zero-knowledge in generic groups.
-
-\paragraph{The representation extraction lemma.}
-Let $\adv$ be an algorithm that outputs 
-a generic group element $u \in \GG$.
-The following lemma shows that there is an extractor that
-can extract from $\adv$ an integer representation of $u$
-relative to a supplied set of group generators.
-Moreover, this integer representation is unique.
-
-\begin{lemma}[Unique representation extraction in generic groups]
-\label{lem:unique}
-Let $\adv_1, \adv_2$ be two randomized algorithms that interact
-with generic group oracles for the group $\GG$ and 
-output $u_1, u_2 \in \GG$, respectively. 
-Suppose that each algorithm makes at most $q$ type-1 queries
-and let $g_1,\ldots,g_q \in \GG$ be the returned random group elements.
-
-There is an extractor $\bdv$ that emulates 
-the generic group oracles for $\adv_1$ and $\adv_2$
-such that for $i=1,2$ when $\bdv$ interacts with $\adv_i$ 
-the following holds with overwhelming probability:
-if $\adv_i$ outputs $u_i \in \GG$ 
-then the extractor $\bdv_i$ outputs a representation
-$\alpha_{i,1},\ldots,\alpha_{i,q} \in \ZZ$
-such that $u_i = g_1^{\alpha_{i,1}} \cdots g_q^{\alpha_{i,q}}$.
-Moreover, if $u_1 = u_2$ then the two representations are the same,
-namely $\alpha_{1,j} = \alpha_{2,j}$ for $j=1,\ldots,q$. 
-\end{lemma}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A private airdrop to ECDSA and Schnorr public keys}
-
-TODO: needs to be written.  Maybe put this first because it is so much
-simpler?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A private airdrop to RSA public keys}
+\section{A private airdrop to RSA public keys}\label{sec:rsa}
 
@@
 We design a ZKPK for a $\phi$-preimage 
-using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}:
+using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}.
+Here the verifier is given $T \in \GG^4 \times \ZZ$ 
+and the prover is given $T$ and $\vv \in \ZZ^8$
+where $\phi(\vv) = T$. 
+The protocol works as follows:
 \begin{enumerate}
-\item The prover chooses a random $\rv \rgets \range{2^{2\lambda}}^8$
-and computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$. \\
-It sends $(c_1, c_2, \Rv)$ to the verifier.
+\item The prover sets
+    $\rv \deq (r_w, r_\mathit{w2}, r_\mathit{s1}, r_a, r_\mathit{na}, 
+                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$ where
+\[ r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}} 
+    \quad\text{and}\quad
+   r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N}.
+\]
+The prover computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
+and sends $(c_1, c_2, \Rv)$ to the verifier.
 
@@
 \begin{alg}
-\> choose random $\hat{c}_1, \hat{c}_2 \rgets \GG,\ \ \ell \rgets \primes$, and
-$\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
-\> set $c_1 \gets \hat{c}_1^\ell$ and $c_2 \gets \hat{c}_2^\ell$, \AlgSep
+\> choose random $c_1, c_2 \rgets \GG,\ \ \ell \rgets \primes$, and
+\ \ $\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
+\lnum \label{ln:randvell}
 \> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
-\lnum \label{ln:randv}
-\> choose random $\hat{\rv} \rgets \range{2^{2\lambda}}^8$
-and define $\hat{T} \deq \Big(\hat{c}_1^\mathit{ch}, \hat{c}_2^\mathit{ch}, 1, 1, \lfloor (t \cdot \mathit{ch})/\ell \rfloor\Big) \in \GG^4 \times \ZZ$, \AlgSep
-\> set $\Zv_q \deq \hat{T} \cdot \phi(\lfloor \hat{\rv}/\ell \rfloor) \in \GG^4 \times \ZZ$, \AlgSep
+\lnum \label{ln:randZ}
+\> choose random $Z_1, Z_2, Z_3, Z_4 \rgets \GG$, \\
+\lnum \label{ln:sim}
+\> choose random $\hat{r}_\text{w2}, \hat{r}_\text{na} \rgets \range{2^{2\lambda}}$
+and set $Z_5 \deq \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor \hat{r}_\text{w2} / \ell \rfloor - \lfloor \hat{r}_\text{na} / \ell \rfloor \in \ZZ$, \\
+\> set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5)  \in \GG^4 \times \ZZ$, \AlgSep
 \lnum \label{ln:computeR}
@@
 to an accepting transcript of a real protocol execution.
-Because $\ell$ does not divide $\abs{\GG}$ with overwhelming probability,
-we know that $c_1$ and $c_2$ are uniform in $\GG$. 
-Hence, observe that $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
+In a real transcript we know that $c_1$ and $c_2$ are uniform in $\GG$. 
+Hence, observe that the simulated $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
 exactly as in a real transcript.  It remains to show that the same holds
 for $\zv_\ell, \Zv_q$, and $\Rv$. 
-In an interaction with a real prover 
-the vector $\rv$ is chosen uniformly in $\range{2^{2\lambda}}^8$.
-Consider one value $r \rgets \range{2^{2\lambda}}$.
-Because $2^{2\lambda}$ is much larger than $\ell$
+In an interaction with a real prover the quantities
+$r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
+are chosen uniformly in $\range{N}$.
+Consider one such value $r \rgets \range{N}$.
+Because $N$ is much larger than $\abs{\GG} \cdot \ell$
 we know that the pair
-$\big(\lfloor r/\ell \rfloor,\ (r \bmod \ell) \big)$
-is statistically close to uniform in $\range{2^{2\lambda}/\ell} \times \range{\ell}$.
-It directly follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
+$\big(\lfloor r/\ell \rfloor \bmod \abs{\GG},\ (r \bmod \ell) \big)$
+is statistically close to uniform in $\range{\,\abs{\GG}\,} \times \range{\ell}$.
+Similarly,  in a real transcript
+each of $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa}$
+is chosen uniformly in $\range{2^{2 \lambda}}$ and therefore
+each of these four values modulo $\ell$
+is statistically close to uniform in $\range{\ell}$.
+It follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
 in a real transcript, is statistically close to uniform 
-in $\range{\ell}^8$, as in the simulation.
+in $\range{\ell}^8$, as in line~\eqref{ln:randvell} in the simulation.
 
 Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly.
-Write $\hat{\rv}$ generated on line~\eqref{ln:randv} in the simulation
-as $\hat{\rv} = \big(r_\text{w}, r_\text{w2}, r_\text{s1}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}, r_\text{s2} \big)$.
-Then the simulated $\Zv_q$ is computed as:
-\begin{equation} \label{eq:sim}
-\Zv_q \deq \left(\begin{array}{l}
-Z_1 \gets \hat{c}_1^\mathit{ch} \cdot g^{\lfloor r_\text{w}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1}/\ell \rfloor} ,\quad
-Z_2 \gets \hat{c}_2^\mathit{ch} \cdot g^{\lfloor r_\text{a}/\ell \rfloor} \cdot h^{\lfloor r_\text{s2}/\ell \rfloor} , \AlgSep
-Z_3 \gets g^{\lfloor r_\text{w2}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1w}/\ell \rfloor} / \hat{c}_1^{\lfloor r_\text{w}/\ell \rfloor},\quad
-Z_4 \gets g^{\lfloor r_\text{na}/\ell \rfloor} \cdot h^{\lfloor r_\text{sa}/\ell \rfloor} / \hat{c}^{\lfloor r_\text{a}/\ell \rfloor}, \AlgSep
-Z_5 \gets \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2}/\ell \rfloor - \lfloor r_\text{na}/\ell \rfloor 
-\end{array}\right) \in \GG^4 \times \ZZ.  
-\end{equation}
-Let's start with $Z_5 \in \ZZ$.  
-In a real transcript 
+Observe that each of the first four components of $\Zv_q$ is a group
+element in $\GG$ that is randomized by
+$h^{\lfloor r_\mathit{s1} / \ell \rfloor},\
+ h^{\lfloor r_\mathit{s2} / \ell \rfloor},\
+ h^{\lfloor r_\mathit{s1w} / \ell \rfloor},\
+ h^{\lfloor r_\mathit{sa} / \ell \rfloor}$ respectively.
+Because these four exponents are close to uniform in $\range{\,\abs{\GG}\,}$ and are
+independent of everything else in the transcript, it follows that
+in a real transcript $Z_1, Z_2, Z_3, Z_4$ are independent and close to uniform elements in $\GG$.  This is also how these elements are chosen 
+on line~\eqref{ln:randZ} in the simulation.
+
+It remains to argue that $Z_5 \in \ZZ$ is simulated correctly. 
+In a real transcript this $Z_5$ is computed as 
 $Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
           \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
-Therefore, because $\mathit{w2} - \mathit{na} = t$, we have
-that $Z_5$ is a real transcript satifies
-\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor - \Delta \]
-where $\Delta \in \{0, 1\}$. 
+Because $\mathit{w2} - \mathit{na} = t$, we have
+that $Z_5$ in a real transcript satisfies
+\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
+where $\Delta \in \{0, \pm 1\}$. 
 In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
@@
 are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
-as in the the simulated $Z_5$ in~\eqref{eq:sim}.
+as in the simulated $Z_5$ on line~\eqref{ln:sim}.
 The only difference is that the real distribution is shifted by $\Delta$
 where as the simulated distribution is not.  
-Because $\Delta$ is small, $\Delta \in \{0,1\}$,
-this difference only negligibly affects the statistical distance. 
-We thus conclude that the simulated $Z_5$ in~\eqref{eq:sim} 
+However this $\Delta$ only negligibly affects the statistical distance
+between the real and simulated distributions. 
+The reason is that in both distributions, 
+every possible value in the range of $Z_5$, 
+except possibly at the edges, 
+is obtained from the same number of values 
+for the pair $(r_\text{w2}, r_\text{na})$. 
+%%  would be good to prove this as a general lemma.
+We thus conclude that the simulated $Z_5$ in~\eqref{ln:sim} 
 is statistically close to its real distribution.
-Essentially the same argument shows that $Z_1, Z_2, Z_3, Z_4$ are
-also simulated correctly. 
-{\bf TODO:} explain why.
 
@@
 from the left equality in~\eqref{eq:third}, and thus extract $n \in \ZZ$ by
-repeating over several $\ell$.  Similarly, it can extract $s \in \ZZ$ from
+repeating this procedure over several $\ell$ and then using the chinese
+remainder theorem.  
+Similarly, it can extract $s \in \ZZ$ from
 the right equality in~\eqref{eq:third}.   
 It thus obtains a witness $(n, s, w, a)$ 
-for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}, as required.
+for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}, as required.
 \end{proof}
 
-\subsection{The concrete airdrop system}
+\subsection{The concrete airdrop system}\label{sec:rsa:airdrop}
 
@@
 TODO: Use the extractor of the interactive protocol. Easy corollary.
-
-\bibliographystyle{alpha}
-\bibliography{paper}
-
-\end{document}

### 2019-01-18 paper/defs.tex
first cut at security definitions

@@
 
-TODO: Need to state security properties formally: 
-(1) $c$ and $\text{sig}$ should reveal nothing about $\PK$,
-(2) without $\SK$ we have existential unforgeability under a 
-(one-time) chosen message attack.
+\rsw{Needs improved typesetting, notation} PAD must satisfy two security properties:
+
+\paragraph{Privacy}
+The privacy game
+\RSW{notation for game naming}
+is defined as follows:
+
+\begin{itemize}
+\item Adversary sends $\msg$ and keys $(\PK_0, \SK_0)$, $(\PK_1, \SK_1)$ to Challenger.
+
+\item Challenger chooses $b \rgets \{0,1\}$,
+computes $(c, s) \gets \text{sendTokens}(\PK_b)$ and
+$\sig \gets \text{sign}(\SK_b, (c, s), \msg)$,
+and sends $(c, \sig)$ to Adversary.
+
+\item Adversary outputs $b'$.
+
+\end{itemize}
+An airdrop scheme is \emph{private} if $\sizeof{\probab{b' = b} - \nicefrac{1}{2}} < \text{negl}$.
+
+\paragraph{Existential unforgeability}
+The existential forgery game is defined as follows:
+
+\begin{itemize}
+\item Challenger chooses a key $(\PK, \SK)$ and sends $\PK$ to Adversary.
+
+\item Adversary computes $(c, s) \gets \text{sendTokens}(\PK)$, chooses \msg, sends $(c, s, \msg)$ to Challenger.
+
+\item Challenger computes $\sig \gets \text{sign}(\SK, (c, s), \msg)$ and sends to Adversary.
+
+\item Adversary outputs $(\msg', \sig')$.
+
+\end{itemize}
+An airdop is \emph{existentially unforgeable} if
+$\probab{\msg' \neq \msg \wedge \text{verify}(c, \msg', \sig') = \text{yes}} < \text{negl}$.
+
+%TODO: Need to state security properties formally: 
+%(1) $c$ and $\text{sig}$ should reveal nothing about $\PK$,
+%(2) without $\SK$ we have existential unforgeability under a 
+%(one-time) chosen message attack.
 

### 2019-01-18 paper/paper.tex
edits

--- 2019-01-18 paper/paper.tex
@@
-%\def\useacmstyle{}
-\def\submissionpapernumber{$\infty$}
-
-\ifx\useacmstyle\undefined
 \documentclass[11pt]{article}
+\usepackage[dvipsnames]{xcolor}
+\usepackage[hidelinks]{hyperref}
+\usepackage{amsthm,amsmath,amsfonts,amssymb,amstext,mathtools}
 \usepackage{fullpage}
-    \usepackage[hidelinks]{hyperref}
-\else
-    \documentclass[sigconf,anonymous]{acmart}
-    \fancyhf{}
-    \fancyhead[C]{Anonymous submission \submissionpapernumber\ to ACM CCS 2019}
-    \fancyfoot[C]{\thepage}
-    \setcopyright{none}
-    \acmConference{ACM CCS Submission}{2019 Feb 05}{}
-    \acmYear{2019}
-    \settopmatter{printacmref=false, printccs=false, printfolios=false}
-\fi
-
-\usepackage[dvipsnames]{xcolor}
-\usepackage{amsthm,amsmath,amsfonts,amssymb,amstext,mathtools}
 \usepackage{macros}
@@
 \title{An Airdrop That Preserves Recipient Privacy}
-\author{Dan Boneh \and Chris Jeffrey \and Joseph Poon \and Riad Wahby}
+\author{Dan Boneh \and Riad Wahby}
 
@@
 \begin{equation} \label{eq:lang}
-  \mathcal{R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
+  {\cal R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
                               (n, s, w, a) \in \range{N}^4 \Bigr)  \ \ 
@@
   \phi\left(\!\!\begin{array}{l}
-                w, \mathit{w2}, \mathit{s1}, a, \\
-                \mathit{na}, \mathit{s1w}, \mathit{sa}, \mathit{s2}
+                w, \mathit{w2}, s_1, a, \\
+                \mathit{na}, \mathit{s1w}, \mathit{sa}, s_2
       \end{array}  \!\!\!\right) \deq
@@
 \begin{enumerate}
-\item The prover sets
+\item The prover chooses
+ $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}}$
+ and
+ $r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N \cdot 2^{2^\lambda}}$ and sets
     $\rv \deq (r_w, r_\mathit{w2}, r_\mathit{s1}, r_a, r_\mathit{na}, 
-                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$ where
-\[ r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}} 
-    \quad\text{and}\quad
-   r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N}.
-\]
-The prover computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
+                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$. \\
+It computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
 and sends $(c_1, c_2, \Rv)$ to the verifier.
@@
 The protocol is insecure if the group $\GG$ contains a non-identity
-element of known order.  {\bf TODO: describe an attack.}
-In the multiplicative group $(\ZZ/n)^*$ the
+element of known order.  In the multiplicative group $(\ZZ/n)^*$ the
 element $-1$ has order~$2$, and hence the protocol is insecure in this
@@
 Protocol $\prot{P}$ is a zero-knowledge protocol
-for the relation $\mathcal{R}_{g,h}$ in \eqref{eq:lang}.
+for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang}.
 \end{theorem}
@@
 \> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
-\lnum \label{ln:randZ}
 \> choose random $Z_1, Z_2, Z_3, Z_4 \rgets \GG$, \\
@@
 $r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
-are chosen uniformly in $\range{N}$.
-Consider one such value $r \rgets \range{N}$.
-Because $N$ is much larger than $\abs{\GG} \cdot \ell$
+are chosen uniformly in $\range{N \cdot 2^{2^\lambda}}$.
+Consider one such value $r \rgets \range{N \cdot 2^{2^\lambda}}$.
+Because $N \cdot 2^{2\lambda}$ is much larger than $\abs{\GG} \cdot \ell$
 we know that the pair
@@
 independent of everything else in the transcript, it follows that
-in a real transcript $Z_1, Z_2, Z_3, Z_4$ are independent and close to uniform elements in $\GG$.  This is also how these elements are chosen 
-on line~\eqref{ln:randZ} in the simulation.
+in a real transcript $Z_1, Z_2, Z_3, Z_4$ are independent and close to uniform elements in $\GG$.  This is also how these elements are chosen in the simulation.
 
@@
 where $\Delta \in \{0, \pm 1\}$. 
-In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
+As argued above, in a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
 and $\lfloor r_\text{na} / \ell \rfloor$ 
 are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
-as in the simulated $Z_5$ on line~\eqref{ln:sim}.
+as in the simulated $Z_5$ in~\eqref{ln:sim}.
 The only difference is that the real distribution is shifted by $\Delta$
@@
 \begin{definition}
-We say that algorithm $\mathcal{G}$ is an \defn{honest instance
-generator} for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}
+We say that algorithm ${\cal G}$ is an \defn{honest instance
+generator} for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}
 if it chooses integers $n, s, t$, and outputs $(c, t)$ where
@@
 Protocol $\prot{P}$ is an argument of knowledge
-for the relation $\mathcal{R}_{g,h}$ in \eqref{eq:lang} 
+for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang} 
 for instances $(c,t)$ generated by an honest instance
-generator $\mathcal{G}$,
+generator ${\cal G}$,
 when the group $\GG$ is a modeled as a generic group of unknown order. 
@@
 We construct an extractor that given an instance $(c,t)$ 
-generated by $\mathcal{G}$,
+generated by ${\cal G}$,
 interacts with a convincing prover and outputs a witness $(n, s, w, a)$ 
-for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}. 
+for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}. 
 The protocol transcript is $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
@@
 accepting transcripts
-$\mathcal{T}_1 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
+${\cal T}_1 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
 and 
-$\mathcal{T}_2 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
+${\cal T}_2 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
 Dividing the corresponding verification equations one by the other
@@
 and $a \deq \alpha_0 + n \cdot \gamma_0 \in \ZZ$.
-For any pair of accepting transcripts such as $(\mathcal{T}_1, \mathcal{T}_2)$,
+For any pair of accepting transcripts such as $({\cal T}_1, {\cal T}_2)$,
 it must be the case that 
@@
 It thus obtains a witness $(n, s, w, a)$ 
-for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}, as required.
+for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}, as required.
 \end{proof}

### 2019-01-18 paper/paper.tex
edits

@@
         \text{s.t.}\ \ 
-                \begin{aligned}
+                \begin{split}
                         c   & = g^n \cdot h^s \ \ \text{in $\GG$}, \\
@@
                         2 & \leq t \leq \lambda  \ \textrm{a prime}
-                \end{aligned}  \right\}.
+                \end{split}  \right\}.
 \end{equation}
@@
 \begin{enumerate}
-\item The prover chooses
- $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}}$
- and
- $r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N \cdot 2^{2^\lambda}}$ and sets
-    $\rv \deq (r_w, r_\mathit{w2}, r_\mathit{s1}, r_a, r_\mathit{na}, 
-                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$. \\
-It computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
-and sends $(c_1, c_2, \Rv)$ to the verifier.
+\item The prover chooses a random $\rv \rgets \range{2^{2\lambda}}^8$
+and computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$. \\
+It sends $(c_1, c_2, \Rv)$ to the verifier.
 
@@
 \begin{alg}
-\> choose random $c_1, c_2 \rgets \GG,\ \ \ell \rgets \primes$, and
-\ \ $\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
-\lnum \label{ln:randvell}
+\> choose random $\hat{c}_1, \hat{c}_2 \rgets \GG,\ \ \ell \rgets \primes$, and
+$\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
+\> set $c_1 \gets \hat{c}_1^\ell$ and $c_2 \gets \hat{c}_2^\ell$, \AlgSep
 \> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
-\> choose random $Z_1, Z_2, Z_3, Z_4 \rgets \GG$, \\
-\lnum \label{ln:sim}
-\> choose random $\hat{r}_\text{w2}, \hat{r}_\text{na} \rgets \range{2^{2\lambda}}$
-and set $Z_5 \deq \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor \hat{r}_\text{w2} / \ell \rfloor - \lfloor \hat{r}_\text{na} / \ell \rfloor \in \ZZ$, \\
-\> set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5)  \in \GG^4 \times \ZZ$, \AlgSep
+\lnum \label{ln:randv}
+\> choose random $\hat{\rv} \rgets \range{2^{2\lambda}}^8$
+and define $\hat{T} \deq \Big(\hat{c}_1^\mathit{ch},\ \hat{c}_2^\mathit{ch},\ 1,\ 1,\ \lfloor (t \cdot \mathit{ch})/\ell \rfloor\Big) \in \GG^4 \times \ZZ$, \AlgSep
+\> set $\Zv_q \deq \hat{T} \cdot \phi(\lfloor \hat{\rv}/\ell \rfloor) \in \GG^4 \times \ZZ$, \AlgSep
 \lnum \label{ln:computeR}
@@
 to an accepting transcript of a real protocol execution.
-In a real transcript we know that $c_1$ and $c_2$ are uniform in $\GG$. 
-Hence, observe that the simulated $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
+Because $\ell$ does not divide $\abs{\GG}$ with overwhelming probability,
+we know that $c_1$ and $c_2$ are uniform in $\GG$. 
+Hence, observe that $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
 exactly as in a real transcript.  It remains to show that the same holds
 for $\zv_\ell, \Zv_q$, and $\Rv$. 
-In an interaction with a real prover the quantities
-$r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
-are chosen uniformly in $\range{N \cdot 2^{2^\lambda}}$.
-Consider one such value $r \rgets \range{N \cdot 2^{2^\lambda}}$.
-Because $N \cdot 2^{2\lambda}$ is much larger than $\abs{\GG} \cdot \ell$
+In an interaction with a real prover 
+the vector $\rv$ is chosen uniformly in $\range{2^{2\lambda}}^8$.
+Consider one value $r \rgets \range{2^{2\lambda}}$.
+Because $2^{2\lambda}$ is much larger than $\ell$
 we know that the pair 
-$\big(\lfloor r/\ell \rfloor \bmod \abs{\GG},\ (r \bmod \ell) \big)$
-is statistically close to uniform in $\range{\,\abs{\GG}\,} \times \range{\ell}$.
-Similarly,  in a real transcript
-each of $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa}$
-is chosen uniformly in $\range{2^{2 \lambda}}$ and therefore
-each of these four values modulo $\ell$
-is statistically close to uniform in $\range{\ell}$.
-It follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
+$\big(\lfloor r/\ell \rfloor,\ (r \bmod \ell) \big)$
+is statistically close to uniform in $\range{2^{2\lambda}/\ell} \times \range{\ell}$.
+It directly follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
 in a real transcript, is statistically close to uniform 
-in $\range{\ell}^8$, as in line~\eqref{ln:randvell} in the simulation.
+in $\range{\ell}^8$, as in the simulation.
 
 Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly. 
-Observe that each of the first four components of $\Zv_q$ is a group
-element in $\GG$ that is randomized by
-$h^{\lfloor r_\mathit{s1} / \ell \rfloor},\
- h^{\lfloor r_\mathit{s2} / \ell \rfloor},\
- h^{\lfloor r_\mathit{s1w} / \ell \rfloor},\
- h^{\lfloor r_\mathit{sa} / \ell \rfloor}$ respectively.
-Because these four exponents are close to uniform in $\range{\,\abs{\GG}\,}$ and are
-independent of everything else in the transcript, it follows that
-in a real transcript $Z_1, Z_2, Z_3, Z_4$ are independent and close to uniform elements in $\GG$.  This is also how these elements are chosen in the simulation.
-
-It remains to argue that $Z_5 \in \ZZ$ is simulated correctly. 
-In a real transcript this $Z_5$ is computed as 
+Write $\hat{\rv}$ generated on line~\eqref{ln:randv} in the simulation
+as $\hat{\rv} = \big(r_\text{w}, r_\text{w2}, r_\text{s1}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}, r_\text{s2} \big)$.
+Then the simulated $\Zv_q$ is computed as:
+\begin{equation} \label{eq:sim}
+\Zv_q \deq \left(\begin{array}{l}
+Z_1 \gets \hat{c}_1^\mathit{ch} \cdot g^{\lfloor r_\text{w}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1}/\ell \rfloor} ,\quad
+Z_2 \gets \hat{c}_2^\mathit{ch} \cdot g^{\lfloor r_\text{a}/\ell \rfloor} \cdot h^{\lfloor r_\text{s2}/\ell \rfloor} , \AlgSep
+Z_3 \gets g^{\lfloor r_\text{w2}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1w}/\ell \rfloor} / \hat{c}_1^{\lfloor r_\text{w}/\ell \rfloor},\quad
+Z_4 \gets g^{\lfloor r_\text{na}/\ell \rfloor} \cdot h^{\lfloor r_\text{sa}/\ell \rfloor} / \hat{c}^{\lfloor r_\text{a}/\ell \rfloor}, \AlgSep
+Z_5 \gets \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2}/\ell \rfloor - \lfloor r_\text{na}/\ell \rfloor 
+\end{array}\right) \in \GG^4 \times \ZZ.  
+\end{equation}
+Let's start with $Z_5 \in \ZZ$.  
+In a real transcript 
 $Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
           \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
-Because $\mathit{w2} - \mathit{na} = t$, we have
-that $Z_5$ in a real transcript satisfies
+Therefore, because $\mathit{w2} - \mathit{na} = t$, we have
+that $Z_5$ in a real transcript satifies
 \[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
 where $\Delta \in \{0, \pm 1\}$. 
-As argued above, in a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
+In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
 and $\lfloor r_\text{na} / \ell \rfloor$ 
 are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
-as in the simulated $Z_5$ in~\eqref{ln:sim}.
+as in the the simulated $Z_5$ in~\eqref{eq:sim}.
 The only difference is that the real distribution is shifted by $\Delta$
@@
 %%  would be good to prove this as a general lemma.
-We thus conclude that the simulated $Z_5$ in~\eqref{ln:sim} 
+We thus conclude that the simulated $Z_5$ in~\eqref{eq:sim} 
 is statistically close to its real distribution.
+
+Essentially the same argument shows that $Z_1, Z_2, Z_3, Z_4$ are
+also simulated correctly. 
+For example, in a real transcript, where $c_1 = g^w h^\mathit{s1}$, we have
+\begin{align*}
+    Z_1 & \deq g^{\lfloor (\mathit{ch}\cdot w + r_\text{w}) / \ell \rfloor} \cdot 
+             h^{\lfloor (\mathit{ch}\cdot \mathit{s1} + r_\text{s1}) / \ell \rfloor} = \\
+       & =   g^{\lfloor (\mathit{ch}\cdot w) / \ell \rfloor} \cdot
+             h^{\lfloor (\mathit{ch}\cdot s1) / \ell \rfloor} \cdot
+             g^{\lfloor r_\text{w} / \ell \rfloor + \Delta_\text{w}} \cdot 
+             h^{\lfloor r_\text{s1} / \ell \rfloor + \Delta_\text{s1}} =  \\
+       & = (c_1^{1/\ell})^\mathit{ch} \cdot
+             g^{\lfloor r_\text{w} / \ell \rfloor} \cdot 
+             h^{\lfloor r_\text{s1} / \ell \rfloor} \cdot 
+             \left[ (g^{1/\ell})^{\delta_\text{w} + \ell \cdot \Delta_\text{w}} \cdot 
+               (h^{1/\ell})^{\delta_\text{s1} + \ell \cdot \Delta_\text{s1}} \right]
+\end{align*}
+where $\Delta_\text{w}, \Delta_\text{s1} \in \{0,1\}$,
+and $\delta_\text{w} \deq (\mathit{ch} \cdot w \bmod \ell) \in \range{\ell}$
+and $\delta_\text{s1} \deq (\mathit{ch} \cdot \mathit{s1} \bmod \ell) \in \range{\ell}$.
+Hence, $Z_1$ in a real transcript is distributed as 
+the simulated $Z_1$ in~\eqref{eq:sim}, where the only
+difference is the quantity 
+$\Delta \deq (g^{1/\ell})^{\delta_\text{w} - \ell \cdot \Delta_\text{w}} \cdot 
+               (h^{1/\ell})^{\delta_\text{s1} - \ell \cdot \Delta_\text{s1}} \in \GG$. 
+We claim that this $\Delta$ only negligibly affects the statistical distance
+between the real and simulated distributions. 
+{\bf TODO:} explain why.
 

### 2019-01-18 paper/paper.tex
edits

@@
 \begin{enumerate}
-\item The prover chooses
- $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}}$
- and
- $r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N \cdot 2^{2^\lambda}}$ and sets
+\item The prover sets
     $\rv \deq (r_w, r_\mathit{w2}, r_\mathit{s1}, r_a, r_\mathit{na}, 
-                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$. \\
-It computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
+                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$ where
+\[ r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}} 
+    \quad\text{and}\quad
+   r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N \cdot 2^{2\lambda}}.
+\]
+The prover computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
 and sends $(c_1, c_2, \Rv)$ to the verifier.
@@
 \> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
+\lnum \label{ln:randZ}
 \> choose random $Z_1, Z_2, Z_3, Z_4 \rgets \GG$, \\
@@
 $r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
-are chosen uniformly in $\range{N \cdot 2^{2^\lambda}}$.
-Consider one such value $r \rgets \range{N \cdot 2^{2^\lambda}}$.
+are chosen uniformly in $\range{N \cdot 2^{2\lambda}}$.
+Consider one such value $r \rgets \range{N \cdot 2^{2\lambda}}$.
 Because $N \cdot 2^{2\lambda}$ is much larger than $\abs{\GG} \cdot \ell$
@@
 independent of everything else in the transcript, it follows that
-in a real transcript $Z_1, Z_2, Z_3, Z_4$ are independent and close to uniform elements in $\GG$.  This is also how these elements are chosen in the simulation.
+in a real transcript $Z_1, Z_2, Z_3, Z_4$ are independent and close to uniform elements in $\GG$.  This is also how these elements are chosen 
+on line~\eqref{ln:randZ} in the simulation.
 
@@
 where $\Delta \in \{0, \pm 1\}$. 
-As argued above, in a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
+In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
 and $\lfloor r_\text{na} / \ell \rfloor$ 
 are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
-as in the simulated $Z_5$ in~\eqref{ln:sim}.
+as in the simulated $Z_5$ on line~\eqref{ln:sim}.
 The only difference is that the real distribution is shifted by $\Delta$

### 2019-01-18 paper/defs.tex
clean up security defn notation

--- 2019-01-18 paper/defs.tex
@@
-\section{Private airdrop: definitions}\label{sec:defs}
+\section{Definitions}\label{sec:defs}
 
-A private airdrop (PAD) system is a triple of efficient algorithms:
+\subsection{Private airdrop scheme}
+
+\paragraph{Syntax} A private airdrop (PAD) system is a triple of efficient algorithms:
 \begin{itemize}
@@
 
-TODO: Need to state security properties formally: 
-(1) $c$ and $\text{sig}$ should reveal nothing about $\PK$,
-(2) without $\SK$ we have existential unforgeability under a 
-(one-time) chosen message attack.
+\paragraph{Security} A private airdrop scheme is secure if it is \emph{anonymous} and \emph{unforgeable}.
+
+\medskip\noindent\textit{Anonymity} means, roughly speaking, that $c$ and $\sig$ reveal
+    nothing about $\PK$.
+Specifically, consider $\mathsf{Anonym}$, a game between a PPT adversary $\adv$
+    and a challenger $\chall$:
+%
+\begin{itemize}
+\item $\chall$ chooses keys $(\PK_0, \SK_0)$, $(\PK_1, \SK_1)$, and sends $(\PK_0, \PK_1)$ to $\adv$.
+
+\item $\adv$ chooses $\msg$ and sends it to $\chall$.
+
+\item $\chall$ chooses $b \rgets \{0,1\}$,
+computes $(c, s) \gets \text{sendTokens}(\PK_b)$ and
+$\sig \gets \text{sign}(\SK_b, (c, s), \msg)$,
+and sends $(c, \sig)$ to $\adv$.
+
+\item $\adv$ outputs $b'$.
+
+\end{itemize}
+%
+$\adv$ wins $\mathsf{Anonym}$ if $b' = b$.
+
+\begin{definition}
+Let an adversary $\adv$'s advantage in $\mathsf{Anonym}$ be
+$\mathrm{Adv}_{\adv}^{\mathsf{Anonym}} = \sizeof{\probab{\adv~\text{wins}} - \nicefrac{1}{2}}$.
+Then an airdrop scheme is \emph{anonymous} if, for any PPT adversary
+    $\adv$, $\mathrm{Adv}_{\adv}^{\mathsf{Anonym}} \le \text{negl}$.
+\end{definition}
+
+\medskip\noindent\textit{Unforgeability} means, roughly speaking, that
+    a party that does not know $\SK$ cannot generate a valid signature
+    for any message, even if it knows a valid signature for any other
+    message.
+Specifically, consider $\mathsf{Unforg}$, a game between a PPT adversary
+    $\adv$ and a challenger $\chall$:
+%
+\begin{itemize}
+\item $\chall$ chooses a key $(\PK, \SK)$ and sends $\PK$ to $\adv$.
+
+\item $\adv$ computes $(c, s) \gets \text{sendTokens}(\PK)$, chooses \msg, and sends $(c, s, \msg)$ to $\chall$.
+
+\item $\chall$ computes $\sig \gets \text{sign}(\SK, (c, s), \msg)$ and sends to $\adv$.
+
+\item $\adv$ outputs $(\msg', \sig')$.
+
+\end{itemize}
+%
+$\adv$ wins $\mathsf{Unforg}$ if $\msg' \neq \msg \wedge \text{verify}(c, \msg', \sig') = \text{yes}$.
+
+\begin{definition}
+Let an adversary $\adv$'s advantage in $\mathsf{Unforg}$ be
+$\mathrm{Adv}_{\adv}^{\mathsf{Unforg}} = \probab{\adv~\text{wins}}$.
+Then an airdop is \emph{unforgeable} if, for any PPT adversary $\adv$,
+$\mathrm{Adv}_{\adv}^{\mathsf{Unforg}} \le \text{negl}$.
+\end{definition}
 

### 2019-01-18 paper/defs.tex
in PAD definition, define parties S, R, V

@@
 
-\paragraph{Syntax} A private airdrop (PAD) system is a triple of efficient algorithms:
+In a private airdrop scheme PAD, a \emph{sender} \Sr creates a \emph{token}
+    for a \emph{recipient} \Rt whose key pair is $(\PK, \SK)$, and posts
+    this token in a transaction on a blockchain.
+To claim the output of the transaction, \Rt generates a signature on a message
+    indicating that the token is spent, and posts this message and signature
+    to the blockchain.
+Finally, any \emph{verifier} \Vr can check the signature on the message
+    and the token.
+
+\paragraph{Syntax} PAD is a triple of efficient algorithms:
+%
 \begin{itemize}
 \item $\text{sendTokens}(\PK) \to (c, s)$:
-Generates a token $c$ to be posted on the blockchain,
-and a secret~$s$ given to the recipient via a private channel.
-For example, an encryption of $s$ under $\PK$ can be posted
-to the blockchain.   The posted encrypted $s$ is not associated with 
-the token $c$. 
-\RSW{is it necessary to suggest that Enc(s) appear on the blockchain? It could just be posted publicly, since it doesn't need to be remembered for long.}
+%
+\Sr generates token $c$ and secret $s$, posts $c$ publicly, and sends $s$
+    to \Rt via some private channel.
+%To send a \emph{token} $c$ to a \emph{recipient} \Rt whose key is $(\PK,
+%    \SK)$, a \emph{sender} \Sr generates $c$ to be posted on a blockchain,
+%    plus a \emph{secret}~$s$ given to \Rt via some private channel.
+\unskip\footnote{For example, a encryption of $s$ under $\PK$ can be posted
+    to a public messageboard. Note, however, that the posted ciphertext
+    should not be publicly associated with the token $c$.}
+%\RSW{is it necessary to suggest that Enc(s) appear on the blockchain? It could just be posted publicly, since it doesn't need to be remembered for long.}
 
 \item $\text{sign}(\SK, (c, s), m) \to \sig$:
-Signs a message $m$ indicating that the token $c$ is spent.
+\Rt generates signature $\sig$ over message $m$.
 
 \item $\text{verify}(c, m, \sig) \to \{\text{yes},\text{no}\}:$
-Verify that a signature $\sig$ on token $c$ is valid.
+\Vr checks signature $\sig$ on message $m$ for token $c$.
 \end{itemize}

### 2019-01-18 paper/ecdsa.tex
start cleaning up warmup section

@@
-\section{A private airdrop to ECDSA and Schnorr public keys}\label{sec:dsa}
+\section{A private airdrop scheme from ECDSA}\label{sec:dsa}
 
-\rsw{this section is, for now, a quick note-stash}
-
-As a warm-up, we present a PAD scheme for ECDSA.
-\RSW{generalize to EdDSA and prime-field DSA just here, throughout, or just in a comment at the end?}
+As a warm-up, we present a PAD for ECDSA.
+\unskip\footnote{This scheme extends naturally to Schnorr, EdDSA, etc.}
 %
 %\paragraph{Notation}
-Let $\HH$ be a cyclic group of prime order $q$, generated by $\gHH$.
+Let $\HH = \langle\gHH\rangle$ be a cyclic group of prime order $q$.
 \RSW{I don't love $\HH$ and I loathe $\gHH$, but maybe it's helpful to use
@@
 
-\rsw{maybe standardize on party names, i.e., `challenger' (or `sender'),
-    `signer' (or `receiver'), and `verifier'.}
-
 \paragraph{Algorithm $\text{sendTokens}(\PK)$:} To send tokens to public key $\PK = \gHH^x$, do:
 \begin{itemize}
-\item generate a random $s \rgets \range{q}$
+\item choose $s \rgets \range{q}$
 \item output $(c, s)$ where $c \gets \PK\cdot\gHH^s$

### 2019-01-18 paper/paper.tex
edits

@@
     \quad\text{and}\quad
-   r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N \cdot 2^{2\lambda}}.
+   r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N}.
 \]
@@
 $r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
-are chosen uniformly in $\range{N \cdot 2^{2\lambda}}$.
-Consider one such value $r \rgets \range{N \cdot 2^{2\lambda}}$.
-Because $N \cdot 2^{2\lambda}$ is much larger than $\abs{\GG} \cdot \ell$
+are chosen uniformly in $\range{N}$.
+Consider one such value $r \rgets \range{N}$.
+Because $N$ is much larger than $\abs{\GG} \cdot \ell$
 we know that the pair

### 2019-01-19 paper/defs.tex
small clarification in defs

@@
 
-In a private airdrop scheme PAD, a \emph{sender} \Sr creates a \emph{token}
-    for a \emph{recipient} \Rt whose key pair is $(\PK, \SK)$, and posts
-    this token in a transaction on a blockchain.
-To claim the output of the transaction, \Rt generates a signature on a message
-    indicating that the token is spent, and posts this message and signature
-    to the blockchain.
-Finally, any \emph{verifier} \Vr can check the signature on the message
-    and the token.
+\paragraph{High-level description} In a private airdrop, a \emph{sender} \Sr creates a \emph{token}
+    for a \emph{recipient} \Rt whose public key is $\PK$, and posts
+    the token in a transaction on a blockchain.
+To claim the transaction's value, \Rt generates a new transaction and
+    uses the token and corresponding secret key $\SK$ to generate a signature; it posts the
+    new transaction and the signature to the blockchain.
+Any \emph{verifier} \Vr can check the signature on the transaction
+    using the token, \emph{without} learning $\PK$.
 
-\paragraph{Syntax} PAD is a triple of efficient algorithms:
+\paragraph{Syntax} A private airdrop scheme PAD is a triple of efficient algorithms:
 %
@@
 %
-\Sr generates token $c$ and secret $s$, posts $c$ publicly, and sends $s$
+\Sr generates token $c$ and secret $s$, then posts $c$ publicly and sends $s$
     to \Rt via some private channel.
@@
     to a public messageboard. Note, however, that the posted ciphertext
-    should not be publicly associated with the token $c$.}
+    must not publicly associate $\PK$ with the token $c$.}
 %\RSW{is it necessary to suggest that Enc(s) appear on the blockchain? It could just be posted publicly, since it doesn't need to be remembered for long.}

### 2019-01-19 paper/defs.tex
split out zk from defs

@@
 \end{definition}
-
-\subsection{Zero-knowledge proofs in generic groups}
-
-TODO: Need overview of zero-knowledge in generic groups.
-
-\paragraph{The representation extraction lemma.}
-Let $\adv$ be an algorithm that outputs 
-a generic group element $u \in \GG$.
-The following lemma shows that there is an extractor that
-can extract from $\adv$ an integer representation of $u$
-relative to a supplied set of group generators.
-Moreover, this integer representation is unique.
-
-\begin{lemma}[Unique representation extraction in generic groups]
-\label{lem:unique}
-Let $\adv_1, \adv_2$ be two randomized algorithms that interact
-with group oracles for a generic group $\GG$ of unknown order.
-For $i=1,2$, algorithm $\adv_i$ outputs $u_i \in \GG$.
-Suppose that each algorithm makes at most $q$ type-1 queries
-and let $g_1,\ldots,g_q \in \GG$ be the returned random group elements.
-
-There is an extractor $\bdv$ that emulates 
-the generic group oracles for $\adv_1$ and $\adv_2$
-such that for $i=1,2$ when $\bdv$ interacts with $\adv_i$ 
-the following holds with overwhelming probability:
-if $\adv_i$ outputs $u_i \in \GG$ 
-then the extractor $\bdv_i$ outputs a representation
-$\alpha_{i,1},\ldots,\alpha_{i,q} \in \ZZ$
-such that $u_i = g_1^{\alpha_{i,1}} \cdots g_q^{\alpha_{i,q}}$.
-Moreover, if $u_1 = u_2$ then the two representations are the same,
-namely $\alpha_{1,j} = \alpha_{2,j}$ for $j=1,\ldots,q$. 
-\end{lemma}

### 2019-01-19 paper/paper.tex
split out zk from defs

@@
+%\def\useacmstyle{}
+\def\submissionpapernumber{$\infty$}
+
+\ifx\useacmstyle\undefined
     \documentclass[11pt]{article}
+    \usepackage{fullpage}
+    \usepackage[hidelinks]{hyperref}
+\else
+    \documentclass[sigconf,anonymous]{acmart}
+    \fancyhf{}
+    \fancyhead[C]{Anonymous submission \submissionpapernumber\ to ACM CCS 2019}
+    \fancyfoot[C]{\thepage}
+    \setcopyright{none}
+    \acmConference{ACM CCS Submission}{2019 Feb 05}{}
+    \acmYear{2019}
+    \settopmatter{printacmref=false, printccs=false, printfolios=false}
+\fi
+
 \usepackage[dvipsnames]{xcolor}
-\usepackage[hidelinks]{hyperref}
 \usepackage{amsthm,amsmath,amsfonts,amssymb,amstext,mathtools}
-\usepackage{fullpage}
 \usepackage{macros}
 \usepackage[normalem]{ulem}
+\usepackage{nicefrac}
 \usepackage{peanutgallery}
-
-\begin{document}
 
@@
 
+\begin{document}
+
 \maketitle
 
-\begin{abstract}
-\end{abstract}
+\input{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\input{intro}
 
-More to come.
+\input{defs}
 
-\rsw{stashed note from talk with DB}
-Simultaneously using the schemes of \S\ref{sec:dsa} and \S\ref{sec:rsa}
-    on the same blockchain allows distinguishing between users based on
-    key type.
-Can work around this using generic ZKPK, at substantial performance cost.
-(Alt narrative: talk about generic ZKPK first, then specialize to get better
-    perf. at cost of distinguishing.)
+\input{zk}
 
-\rsw{stashed note from chat with Henry and Dima}
-Possible objection: why doesn't sender just generate a bunch of phony keys
-    and send all money to self?
-In other words, why is this scheme better, from the verifiers' point of view,
-    than the naive approach, i.e., sender generating a fresh key pair and
-    sending secret key to recipient?
-(Note that while the naive approach does not have existential unforgeability,
-    that property does not prevent self-dealing if sender knows secret key.
-Another way to say this is that the security property we need for the
-    airdrop-to-Github-users case is stronger than existential unforgeability.)
+\input{ecdsa}
 
-One answer: for each RSA key $\PK = (n, e)$ to be paid, sender publishes
-    the challenge $c = g^nh^s$ and (separately, i.e., without revealing
-    correspondence) sender also publishes
-$(\PK, s')$, $s' = E(\PK, (c',s)))$, $c' = H(g^nh^s)$.
-In other words, the sender publishes a list of purported airdrop recipients
-    separately from the list of airdrop challenge tokens.
-
-If sender was dishonest with respect to any key, i.e., if for some $(\PK,
-    s')$, any of $s', c', c, s$ is invalid, key's owner can reveal $(\hat{c}',
-    \hat{s}) = D(\PK, s')$.
-Then verifiers check that $s' = E(\PK, (\hat{c}', \hat{s}))$, and that
-    either no corresponding $c$ exists, or that $c$ is not a commitment
-    to $n$ with opening $s$.
-
-\emph{Question:} do we need to make $E()$ deterministic for this to work
-    (say, $r = H(\PK)$ in OAEP)?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Private airdrop: definitions}\label{sec:defs}
-
-A private airdrop (PAD) system is a triple of efficient algorithms:
-\begin{itemize}
-\item $\text{sendTokens}(\PK) \to (c, s)$:
-Generates a token $c$ to be posted on the blockchain,
-and a secret~$s$ given to the recipient via a private channel.
-For example, an encryption of $s$ under $\PK$ can be posted
-to the blockchain.   The posted encrypted $s$ is not associated with 
-the token $c$. 
-\RSW{is it necessary to suggest that Enc(s) appear on the blockchain? It could just be posted publicly, since it doesn't need to be remembered for long.}
-
-\item $\text{sign}(\SK, (c, s), m) \to \text{sig}$:
-Signs a message $m$ indicating that the token $c$ is spent.
-
-\item $\text{verify}(c, m, \text{sig}) \to \{\text{yes},\text{no}\}:$
-Verify that a signature $\text{sig}$ on token $c$ is valid.
-\end{itemize}
-
-TODO: Need to state security properties formally: 
-(1) $c$ and $\text{sig}$ should reveal nothing about $\PK$,
-(2) without $\SK$ we have existential unforgeability under a 
-(one-time) chosen message attack.
-
-\subsection{Zero-knowledge proofs in generic groups}
-
-TODO: Need overview of zero-knowledge in generic groups.
-
-\paragraph{The representation extraction lemma.}
-Let $\adv$ be an algorithm that outputs 
-a generic group element $u \in \GG$.
-The following lemma shows that there is an extractor that
-can extract from $\adv$ an integer representation of $u$
-relative to a supplied set of group generators.
-Moreover, this integer representation is unique.
-
-\begin{lemma}[Unique representation extraction in generic groups]
-\label{lem:unique}
-Let $\adv_1, \adv_2$ be two randomized algorithms that interact
-with group oracles for a generic group $\GG$ of unknown order.
-For $i=1,2$, algorithm $\adv_i$ outputs $u_i \in \GG$.
-Suppose that each algorithm makes at most $q$ type-1 queries
-and let $g_1,\ldots,g_q \in \GG$ be the returned random group elements.
-
-There is an extractor $\bdv$ that emulates 
-the generic group oracles for $\adv_1$ and $\adv_2$
-such that for $i=1,2$ when $\bdv$ interacts with $\adv_i$ 
-the following holds with overwhelming probability:
-if $\adv_i$ outputs $u_i \in \GG$ 
-then the extractor $\bdv_i$ outputs a representation
-$\alpha_{i,1},\ldots,\alpha_{i,q} \in \ZZ$
-such that $u_i = g_1^{\alpha_{i,1}} \cdots g_q^{\alpha_{i,q}}$.
-Moreover, if $u_1 = u_2$ then the two representations are the same,
-namely $\alpha_{1,j} = \alpha_{2,j}$ for $j=1,\ldots,q$. 
-\end{lemma}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{pad_ecdsa.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A private airdrop to RSA public keys}\label{sec:rsa}
-
-From here we use the following notations:
-$\lambda$ is the security parameter (e.g., $\lambda = 128$), 
-$\range{\ell}$ denotes the set of integers $\{0,1,\ldots,\ell-1\}$, and 
-$\primes$ is a set of size $2^\lambda$ 
-containing the smallest $2^\lambda$ odd primes. 
-%
-We will also need a set of public parameters that include the description
-of a cyclic group $\GG$ of unknown order.  We let $g$ and $h$ be two
-random generators of $\GG$ where the discrete-log of $g$ base $h$ is unknown.
-
-\subsection{Proving knowledge of the factorization of a hidden integer}\label{sec:rsa:proving}
-
-Let $n \in \range{N}$ be a secret integer 
-where $N$ is a public upper bound on~$n$.
-We will also assume that $N > \abs{\GG} \cdot 2^{2 \lambda}$.
-Let $c \deq g^n \cdot h^s \in \GG$ be a commitment to $n$, 
-where $s \rgets \range{N}$.  
-We first develop a zero knowledge protocol for proving knowledge of the
-factorization of~$n$ given only $c$.
-
-To prove knowledge of the factorization of $n$ the prover
-proves knowledge of a $w \in \range{N}$ such that $w^2 \equiv t \pmod{n}$
-for some small public prime $t \in \ZZ$, namely $2 \leq t \leq \lambda$.
-That is, we provide a ZKPK for the relation
-\begin{equation} \label{eq:lang}
-  {\cal R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
-                              (n, s, w, a) \in \range{N}^4 \Bigr)  \ \ 
-        \text{s.t.}\ \ 
-                \begin{aligned}
-                        c   & = g^n \cdot h^s \ \ \text{in $\GG$}, \\
-                        w^2 & = t + a \cdot n \ \ \text{in $\ZZ$}, \\
-                        2 & \leq t \leq \lambda  \ \textrm{a prime}
-                \end{aligned}  \right\}.
-\end{equation}
-Here $(c, t)$ is a statement and $(n, s, w, a)$ is a witness.
-The integer relation $w^2 = t + a\cdot n$ proves that 
-$w^2 \equiv t \pmod{n}$, as required.
-We note that a ZKPK for~\eqref{eq:lang} proves that $t \in \ZZ$ is a quadratic
-residue modulo the committed $n$.  Leaking this bit of information about $n$
-does not interfere with the application to a secure
-\RSW{``secure'' $\rightarrow$ ``private''?}
-airdrop.
-
-\medskip\noindent
-Protocol $\prot{P}$: The ZKPK protocol for~\eqref{eq:lang} 
-between the prover $P$ and the verifier $V$ works as follows:
-\begin{itemize}
-\item input:  the verifier has $(c, t) \in \GG \times \range{\lambda}$ and 
-the prover has $(c, t, n, s, w, a) \in \GG \times \range{N}^5$
-
-\item Prover $P$ chooses two random integers $s_1, s_2 \rgets \range{N}$ and computes
-       $c_1 \gets g^w \cdot h^{s_1} \in \GG$ and $c_2 \gets g^a \cdot h^{s_2} \in \GG$.
-
-\item Next, define a homomorphism $\phi:\ZZ^8 \to \GG^4 \times \ZZ$ 
-parameterized by $g, h, c, c_1, c_2$ as follows:
-\begin{equation} \label{eq:hom}
-  \phi\left(\!\!\begin{array}{l}
-                w, \mathit{w2}, \mathit{s1}, a, \\
-                \mathit{na}, \mathit{s1w}, \mathit{sa}, \mathit{s2}
-      \end{array}  \!\!\!\right) \deq
-      \Bigl(\ 
-       g^w \cdot h^{\mathit{s1}},\ \ \ 
-       g^a \cdot h^{\mathit{s2}},\ \ \ 
-       g^{\mathit{w2}} \cdot h^{\mathit{s1w}} / c_1^w,\ \ \ 
-       g^{\mathit{na}} \cdot h^{\mathit{sa}} / c^a,\ \ \ 
-       \mathit{w2} - \mathit{na}\ \Bigr)
-\end{equation}
-It is easy to see that $\phi$ is a group homomorphism.
-The range of $\phi$ is the group $\GG^4 \times \ZZ$.  
-We will write the group operation in this group multiplicatively.
-That is, if $(a_i, b_i, c_i, d_i, e_i) \in \GG^4 \times \ZZ$ for $i=1,2$
-then 
-\[  (a_1, b_1, c_1, d_1, e_1) \cdot (a_2, b_2, c_2, d_2, e_2) \deq 
-      (a_1 a_2,\ b_1 b_2,\ c_1 c_2,\ d_1 d_2,\ e_1 + e_2).  \]
-
-We need a ZKPK for a $\phi$-preimage of 
-$T \deq (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ$. 
-In other words, we need a zero-knowledge proof of knowledge for a vector 
-$\vv' = (w', \mathit{w2}', s_1', a', \mathit{na}', 
-              \mathit{s1w}', \mathit{sa}', s_2') \in \ZZ^8$ 
-such that 
-\[   \phi(\vv') = T = (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ.  \]
-Doing so proves 
-that $c_1$ is a commitment to $w' \in \ZZ$, 
-that $c_2$ is a commitment to $a' \in \ZZ$,
-that $\mathit{w2}' = (w')^2$, and 
-that $\mathit{na}' = a' \cdot n$ for some integer $a'$.
-Then the last relation proves that $(w')^2 - a' \cdot n = t$ in $\ZZ$,
-as required.
-
-We design a ZKPK for a $\phi$-preimage 
-using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}.
-Here the verifier is given $T \in \GG^4 \times \ZZ$ 
-and the prover is given $T$ and $\vv \in \ZZ^8$
-where $\phi(\vv) = T$. 
-The protocol works as follows:
-\begin{enumerate}
-\item The prover sets
-    $\rv \deq (r_w, r_\mathit{w2}, r_\mathit{s1}, r_a, r_\mathit{na}, 
-                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$ where
-\[ r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}} 
-    \quad\text{and}\quad
-   r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N}.
-\]
-The prover computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
-and sends $(c_1, c_2, \Rv)$ to the verifier.
-
-\item The verifier chooses challenges $\mathit{ch} \rgets \range{2^\lambda}$
-and $\ell \rgets \primes$. \\
-It sends $(\ell, \mathit{ch})$ to the prover.
-
-\item The prover computes:
-\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
-    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^8, \quad
-    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^8, \quad
-    \Zv_q \gets \phi(\zv_q)  
-\]
-and sends $(\Zv_q, \zv_\ell) \in (\GG^4 \times \ZZ) \times \range{\ell}^8$ 
-to the verifier.
-
-\item The verifier accepts if 
-$\ \Zv_q^\ell \cdot \phi(\zv_\ell) = T^\mathit{ch} \cdot \Rv\ $ in 
-$\GG^4 \times \ZZ$.
-\end{enumerate}
-\end{itemize}
-
-\paragraph{Comment 1.}
-The protocol is insecure if the group $\GG$ contains a non-identity
-element of known order.  {\bf TODO: describe an attack.}
-In the multiplicative group $(\ZZ/n)^*$ the
-element $-1$ has order~$2$, and hence the protocol is insecure in this
-group.  Instead, we can work in the quotient group $(\ZZ/n)/\{\pm 1\}$, 
-where elements are represented as integers in the interval $[1,n/2]$
-and the product of $x$ and $y$ is defined as 
-$\abs{x \cdot y} = \min(z, n-z)$ where $z = (x \cdot y \bmod n)$.
-In this group $-1$ is the same as $1$, and presumably there are
-no other known elements of known order.
-
-\paragraph{Comment 2.}
-The commitment $c_2$ to the integer $a$ is necessary for soundness,
-and in particular to ensure that $a$ is an integer.  If $c_2$ along
-with $s_2$ and the second coordinate of $\phi$ are eliminated then there
-is an attack where an adversarial prover can prove knowledge of
-$(\sqrt{3} \bmod n)$ using $a = 1/n$ and $w = 2$.
-
-\paragraph{Comment 3.}
-There is a seemingly simpler method to prove that one knows the
-factorization of~$n$, namely, prove that one knows $p$ such that $p$
-divides $n$.  That is, instead of committing to $w$ we would commit to
-$p$ and $q$ and then prove that $p \cdot q = n$. But we would
-also need to prove that the committed $p$ is not one of 
-$\{1, -1, n, -n\}$, and that results in a longer proof.
-
-\paragraph{Proof of security.}
-We need to prove the protocol above is zero-knowledge and a 
-proof of knowledge.
-
-\begin{theorem}
-Protocol $\prot{P}$ is a zero-knowledge protocol
-for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang}.
-\end{theorem}
-
-\begin{proof}
-The simulator takes $(c, t)$ as input and outputs the simulated transcript
-$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
-\begin{alg}
-\> choose random $c_1, c_2 \rgets \GG,\ \ \ell \rgets \primes$, and
-\ \ $\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
-\lnum \label{ln:randvell}
-\> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
-\lnum \label{ln:randZ}
-\> choose random $Z_1, Z_2, Z_3, Z_4 \rgets \GG$, \\
-\lnum \label{ln:sim}
-\> choose random $\hat{r}_\text{w2}, \hat{r}_\text{na} \rgets \range{2^{2\lambda}}$
-and set $Z_5 \deq \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor \hat{r}_\text{w2} / \ell \rfloor - \lfloor \hat{r}_\text{na} / \ell \rfloor \in \ZZ$, \\
-\> set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5)  \in \GG^4 \times \ZZ$, \AlgSep
-\lnum \label{ln:computeR}
-\> compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
-\> output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
-\end{alg}
-We show the simulated transcript is distributed statistically close
-to an accepting transcript of a real protocol execution.
-In a real transcript we know that $c_1$ and $c_2$ are uniform in $\GG$. 
-Hence, observe that the simulated $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
-exactly as in a real transcript.  It remains to show that the same holds
-for $\zv_\ell, \Zv_q$, and $\Rv$. 
-In an interaction with a real prover the quantities
-$r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
-are chosen uniformly in $\range{N}$.
-Consider one such value $r \rgets \range{N}$.
-Because $N$ is much larger than $\abs{\GG} \cdot \ell$
-we know that the pair
-$\big(\lfloor r/\ell \rfloor \bmod \abs{\GG},\ (r \bmod \ell) \big)$
-is statistically close to uniform in $\range{\,\abs{\GG}\,} \times \range{\ell}$.
-Similarly,  in a real transcript
-each of $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa}$
-is chosen uniformly in $\range{2^{2 \lambda}}$ and therefore
-each of these four values modulo $\ell$
-is statistically close to uniform in $\range{\ell}$.
-It follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
-in a real transcript, is statistically close to uniform 
-in $\range{\ell}^8$, as in line~\eqref{ln:randvell} in the simulation.
-
-Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly.
-Observe that each of the first four components of $\Zv_q$ is a group
-element in $\GG$ that is randomized by
-$h^{\lfloor r_\mathit{s1} / \ell \rfloor},\
- h^{\lfloor r_\mathit{s2} / \ell \rfloor},\
- h^{\lfloor r_\mathit{s1w} / \ell \rfloor},\
- h^{\lfloor r_\mathit{sa} / \ell \rfloor}$ respectively.
-Because these four exponents are close to uniform in $\range{\,\abs{\GG}\,}$ and are
-independent of everything else in the transcript, it follows that
-in a real transcript $Z_1, Z_2, Z_3, Z_4$ are independent and close to uniform elements in $\GG$.  This is also how these elements are chosen 
-on line~\eqref{ln:randZ} in the simulation.
-
-It remains to argue that $Z_5 \in \ZZ$ is simulated correctly. 
-In a real transcript this $Z_5$ is computed as 
-$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
-          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
-Because $\mathit{w2} - \mathit{na} = t$, we have
-that $Z_5$ in a real transcript satisfies
-\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
-where $\Delta \in \{0, \pm 1\}$. 
-In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
-and $\lfloor r_\text{na} / \ell \rfloor$ 
-are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
-as in the simulated $Z_5$ on line~\eqref{ln:sim}.
-The only difference is that the real distribution is shifted by $\Delta$
-where as the simulated distribution is not.  
-However this $\Delta$ only negligibly affects the statistical distance
-between the real and simulated distributions. 
-The reason is that in both distributions, 
-every possible value in the range of $Z_5$, 
-except possibly at the edges, 
-is obtained from the same number of values 
-for the pair $(r_\text{w2}, r_\text{na})$. 
-%%  would be good to prove this as a general lemma.
-We thus conclude that the simulated $Z_5$ in~\eqref{ln:sim} 
-is statistically close to its real distribution.
-
-Finally, because the simulated $c_1, c_2, \ell, \mathit{ch}, \Zv_q, \zv_\ell$
-are all distributed statistically close to a real transcript, 
-it must be the case that the computed $\Rv$ 
-on line~\eqref{ln:computeR} is also distributed as in 
-a real transcript. 
-\end{proof}
-
-\iffalse
-An optimization: the transcript elements $Z_3, Z_4 \in \GG$ can be simulated
-in a similar fashion to how we simulated $Z_5$ in the proof above.
-That is, 
-$Z_3 = g^{\lfloor r_\text{w2} / \ell \rfloor} h^{\lfloor r_\text{s1w} / \ell \rfloor} / c_1^{\lfloor r_\text{w} / \ell \rfloor} \in \GG$
-and 
-$Z_4 = g^{\lfloor r_\text{na} / \ell \rfloor} h^{\lfloor r_\text{sa} / \ell \rfloor} / c^{\lfloor r_\text{a} / \ell \rfloor} \in \GG$,
-where 
-$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}$
-are chosen uniformly in $\range{N}$. 
-It is not difficult to see that these $Z_3$ and $Z_4$ 
-are distributed as in a real transcript.
-This method of simulation can be used to make the protocol slightly more
-efficient because the randomizers 
-$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa} \in \ZZ$
-do not need to be uniform in the entire interval $\range{N}$.
-It suffices to choose these six values 
-uniformly in $\range{2^{2 \lambda}}$, which is a smaller interval
-than $\range{N}$.  Only $r_\text{s1}$ and $r_\text{s2}$ need to be chosen
-uniformly in the full interval $\range{N}$ so that $Z_1$ and $Z_2$ are uniform
-in $\GG$. 
-However, if the simulator chooses $c_1, c_2 \in \GG$ randomly in $\GG$
-so that it knows
-their $\ell$-th root, then even $Z_1$ and $Z_2$ can also be simulated as above.
-Then $r_\text{s1}$ and $r_\text{s2}$ can also be chosen uniformly
-in the range $\range{2^{2 \lambda}}$.
-In other words, the simulator works by first 
-choosing a random $\rv \gets \range{2^{2\lambda}}^8$,
-computing $\Rv \gets \phi(\rv)$, and then
-solving for $\Zv_q \in \GG^4 \times \ZZ$. 
-\fi
-
-\begin{definition}
-We say that algorithm ${\cal G}$ is an \defn{honest instance
-generator} for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}
-if it chooses integers $n, s, t$, and outputs $(c, t)$ where
-$c \deq g^n h^s \in \GG$. 
-\end{definition}
-
-\begin{theorem}
-Protocol $\prot{P}$ is an argument of knowledge
-for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang} 
-for instances $(c,t)$ generated by an honest instance
-generator ${\cal G}$,
-when the group $\GG$ is a modeled as a generic group of unknown order. 
-\end{theorem}
-
-\begin{proof}
-We construct an extractor that given an instance $(c,t)$ 
-generated by ${\cal G}$,
-interacts with a convincing prover and outputs a witness $(n, s, w, a)$ 
-for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}. 
-The protocol transcript is $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
-The extractor rewinds the prover and obtains two
-accepting transcripts
-${\cal T}_1 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
-and 
-${\cal T}_2 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
-Dividing the corresponding verification equations one by the other
-we obtain
-\[   (\Zv_q / \Zv_q')^\ell \cdot \phi(\zv_\ell - \zv_\ell') = 
-          T^{\mathit{ch} - \mathit{ch}'}. \]
-Let $\zv_\ell - \zv_\ell' = \Big(\Delta w,\ \Delta \mathit{w2},\ \Delta \mathit{s1},\ \Delta a,\ \Delta \mathit{na},\ \Delta \mathit{s1w},\ \Delta \mathit{sa},\ \Delta \mathit{s2} \Big) \in \ZZ^8$ and let $\Delta \mathit{ch} = \mathit{ch} - \mathit{ch}' \in \ZZ$.
-Then plugging this into the definition of $\phi$ we obtain
-\begin{equation} \label{eq:messy}
-      (\Zv_q / \Zv_q')^\ell \cdot
-      \left(\begin{array}{l}
-       g^{\Delta w} \cdot h^{\Delta \mathit{s1}},\ \ \ 
-       g^{\Delta a} \cdot h^{\Delta \mathit{s2}},\ \ \ 
-       g^{\Delta \mathit{w2}} \cdot h^{\Delta \mathit{s1w}} / c_1^{\Delta w}, \\
-       g^{\Delta \mathit{na}} \cdot h^{\Delta \mathit{sa}} / c^{\Delta a},\ \ \ 
-       \Delta \mathit{w2} - \Delta \mathit{na}\ 
-       \end{array} \right)
-          = \left(\begin{array}{l}c_1, \ c_2, \ 1, \\ 1,\ t \end{array}\right)^{\Delta \mathit{ch}}.
-\end{equation}
-Let $\Zv_q / \Zv_q' = (z_1, z_2, z_3, z_4, z_5)$ 
-where $z_1, z_2, z_3, z_4 \in \GG$ and $z_5 \in \ZZ$.  
-In a generic group $\GG$, the group elements $z_1, z_2, z_3, z_4$ 
-must satisfy $z_i = g^{\alpha_i} h^{\beta_i} c^{\gamma_i} \prod_{j=1}^q g_j^{\delta_{i,j}}$
-for $i=1,2,3,4$, 
-and $c_1 = g^{\alpha} h^{\beta} c^\gamma \prod_{j=1}^q g_j^{\delta_{j}}$,
-and $c_2 = g^{\alpha_0} h^{\beta_0} c^\gamma \prod_{j=1}^q g_j^{\delta_{0,j}}$,
-where the extractor knows all the listed integer exponents.
-Here $g_1,\ldots,g_q \in \GG$ are random group elements produced in response
-to a generic group oracle query for a random group element.
-
-It now follows from~\eqref{eq:messy}, and from $c = g^n h^s$, 
-and by uniqueness of representation in generic groups (\Lemma{lem:unique}),
-that the following equations must hold over the integers:
-\begin{align*}
-  \ell \cdot (\alpha_1 + n \cdot \gamma_1) + \Delta w & = (\alpha + n \cdot \gamma) \cdot \Delta \mathit{ch},  &
-  \ell \cdot (\beta_1 + s \cdot \gamma_1) + \Delta \mathit{s1} & = (\beta + s \cdot \gamma) \cdot \Delta \mathit{ch}  
-\\
-  \ell \cdot (\alpha_2 + n \cdot \gamma_2) + \Delta a & = (\alpha_0 + n \cdot \gamma_0) \cdot \Delta \mathit{ch},  &
-  \ell \cdot (\beta_2 + s \cdot \gamma_2) + \Delta \mathit{s2} & = (\beta_0 + s \cdot \gamma_0) \cdot \Delta \mathit{ch}  
-\\
-  \ell \cdot (\alpha_3 + n \cdot \gamma_3) + \Delta \mathit{w2} & = (\alpha + n \cdot \gamma) \cdot \Delta w,  &
-  \ell \cdot (\beta_3 + s \cdot \gamma_3) + \Delta \mathit{s1w} & = (\beta + s \cdot \gamma) \cdot \Delta w   
-\\
-  \ell \cdot (\alpha_4 + n \cdot \gamma_4) + \Delta \mathit{na} & = n \cdot \Delta a,  & 
-  \ell \cdot (\beta_4 + s \cdot \gamma_4) + \Delta \mathit{sa} & = s \cdot \Delta a   
-\\
-  \ell \cdot z_4 + \Delta \mathit{w2} - \Delta \mathit{na} & = t \cdot \Delta \mathit{ch} 
-\end{align*}
-The extractor knows all these values except for $n$ and $s$.
-Reducing these equations modulo $\ell$ gives:
-\begin{align}
-  \Delta w & \equiv (\alpha + n \cdot \gamma) \cdot \Delta \mathit{ch}  &
-  \Delta \mathit{s1} & \equiv (\beta + s \cdot \gamma) \cdot \Delta \mathit{ch}  & \pmod{\ell} 
-\label{eq:first} \\
-  \Delta a & \equiv (\alpha_0 + n \cdot \gamma_0) \cdot \Delta \mathit{ch}  &
-  \Delta \mathit{s2} & \equiv (\beta_0 + s \cdot \gamma_0) \cdot \Delta \mathit{ch}  & \pmod{\ell} 
-\label{eq:firsta} \\
-  \Delta \mathit{w2} & \equiv (\alpha + n \cdot \gamma) \cdot \Delta w  &
-  \Delta \mathit{s1w} & \equiv (\beta + s \cdot \gamma) \cdot \Delta w   & \pmod{\ell} 
-\label{eq:second} \\
-  \Delta \mathit{na} & \equiv n \cdot \Delta a  & 
-  \Delta \mathit{sa} & \equiv s \cdot \Delta a   & \pmod{\ell} 
-\label{eq:third} \\
-  \Delta \mathit{w2} - \Delta \mathit{na} & \equiv t \cdot \Delta \mathit{ch} 
-      &&& \pmod{\ell} 
-\label{eq:fourth} 
-\end{align}
-
-Consider the left equalities in~\eqref{eq:first} and~\eqref{eq:firsta}.
-Define $w \deq \alpha + n \cdot \gamma \in \ZZ$ 
-and $a \deq \alpha_0 + n \cdot \gamma_0 \in \ZZ$.
-For any pair of accepting transcripts such as $({\cal T}_1, {\cal T}_2)$,
-it must be the case that 
-$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ and
-$\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$. 
-The extractor knows $\Delta w,\ \Delta a$, and $\Delta \mathit{ch}$.
-Hence, by constructing a polynomial number of such accepting transcript pairs, 
-the extractor can recover $w, a \in \ZZ$ using the chinese remainder theorem.
-
-Next, consider the left equation in~\eqref{eq:second}.
-Using $w = \alpha + n \cdot \gamma$ and
-$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ gives
-$\Delta \mathit{w2} \equiv w^2 \cdot \Delta \mathit{ch} \pmod{\ell}$.
-
-Using $\Delta \mathit{w2} \equiv w^2 \cdot \Delta \mathit{ch} \pmod{\ell}$
-in~\eqref{eq:fourth}
-gives $\Delta \mathit{na} \equiv (w^2 - t) \cdot \Delta \mathit{ch} \pmod{\ell}$. 
-Finally, the left equality in~\eqref{eq:third} 
-gives $(w^2 - t)\cdot \Delta \mathit{ch} \equiv n \cdot \Delta a \pmod{\ell}$.
-Using $\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$
-we obtain that the extracted integers $w$ and $a$ must satisfy
-$(w^2 - t)\cdot \Delta \mathit{ch} \equiv 
-      n \cdot a \cdot \Delta \mathit{ch} \pmod{\ell}$.  
-Since $\ell$ does not divide $\Delta \mathit{ch}$ with overwhelming
-probability, we obtain that $w^2 - t \equiv n \cdot a \pmod{\ell}$.
-Since this equality holds modulo a random $\ell \in \primes$ 
-with overwhelming probability, 
-the equality $w^2 - t = n \cdot a$ must hold over the integers,
-as required.   Note that this implies that $a \neq 0$.
-
-Because $a \neq 0$, the extractor can obtain $(n \bmod \ell)$
-from the left equality in~\eqref{eq:third}, and thus extract $n \in \ZZ$ by
-repeating this procedure over several $\ell$ and then using the chinese
-remainder theorem.  
-Similarly, it can extract $s \in \ZZ$ from
-the right equality in~\eqref{eq:third}.   
-It thus obtains a witness $(n, s, w, a)$ 
-for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}, as required.
-\end{proof}
-
-\subsection{The concrete airdrop system}\label{sec:rsa:airdrop}
-
-The airdrop system is obtained by applying the Fiat-Shamir
-heuristic to the protocol from the previous section. 
-The concrete private airdrop system works as follows:
-
-\paragraph{Algorithm $\text{sendTokens}(\PK)$:}
-To send tokens to an RSA public key $\PK = (n, e)$ do:
-\begin{itemize}
-\item 
-generate a random $s \rgets \range{G}$.
-
-\item 
-output $(c, s)$ where $c \gets g^n \cdot h^s \in \GG$.
-\end{itemize}
-
-\medskip\noindent 
-The following two notes can help optimize the scheme:
-\begin{itemize}
-\item[$-$] $s$ is privately sent to the owner of $\PK$, for example
-by encrypting $s$ under $\PK$ to obtain a ciphertext $c'$ and
-publishing this $c'$ somewhere, not necessarily on the blockchain.  There is
-a public association between $c'$ and $\PK$ (e.g., via a hash table),
-so that the owner of $\PK$ can easily find $c'$.  One can include
-$H(c)$ in the plaintext encrypted in $c'$ to help the owner of $\PK$
-quickly find $c$.
-
-\item[$-$] One can generate $s$ 
-as $s \gets H(s')$ where $s'$ is a random 256-bit value and $H$ is a hash
-function $H:\{0,1\}^{256} \to \range{G}$.  The ciphertext $c'$ is
-an encryption of $s'$, instead of $s$, which can shrink~$c'$.
-\end{itemize}
-
-\paragraph{Algorithm $\text{sign}(\SK, (c, s), m)$:}  
-To withdraw the funds associated with the token $c$ the user
-signs a withdrawal message $m$ using the RSA secret key $\SK = (n,p,q)$ 
-as follows:
-\begin{itemize}
-\item find a prime $2 \leq t \leq \lambda$  such that $t$ is a quadratic 
-residue in $\ZZ_n$.
-
-\item find integers $(w,a)$ such that $w^2 = t + a n$ in $\ZZ$
-           (i.e. $w$ is a square root of $t$ modulo $n$)
-
-\item choose a random $s_1 \rgets \range{N}$ and compute
-           $c_1 \gets g^w \cdot h^{s_1} \in \GG$.
-
-\item choose a random $s_2 \rgets \range{N}$ and compute
-           $c_2 \gets g^a \cdot h^{s_2} \in \GG$.
-
-\item choose a random $\rv \rgets \range{2^{2\lambda}}^8$
-and compute $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$,
-where $\phi$ is the homomorphism defined in~\eqref{eq:hom}.
-
-\item compute $\mathit{seed} \gets \text{Hash}(m, \GG, g, h, c, c_1, c_2, t, \Rv$).
-
-\item
-use a $\text{PRNG}(\mathit{seed})$ to generate $(\mathit{ch}, \ell)$, 
-where $\mathit{ch} \in \range{2^\lambda}$ and $\ell \in \primes$.
-
-\item compute:
-\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
-    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^8, \quad
-    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^8, \quad
-    \Zv_q \gets \phi(\zv_q) \in \GG^4 \times \ZZ.
-\]
-
-\item output the signature 
-$\mathit{sig} = (c_1, c_2, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$.
-\end{itemize}
-
-\paragraph{Algorithm $\text{verify}(c, m, \mathit{sig}):$}
-Verify that $\mathit{sig} = (c_1, c_2, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$ 
-is a valid signature for token~$c$ on the message~$m$.
-\begin{itemize}
-\item reject if $t \notin \range{\lambda}$ or $t$ is not a prime.
-
-\item with $T \deq (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ$, 
-compute $\Rv' \gets \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$.
-
-\item compute $\mathit{seed}' \gets \text{Hash}(m, \GG, g, h, c, c_1, c_2, t, \Rv'$)
-
-\item use a $\text{PRNG}(\mathit{seed}')$ to generate 
-  $\mathit{ch}' \in \range{2^\lambda}$ and $\ell' \in \primes$. \\
-Since $\ell$ is
-  included in the signature, the verifier does not need to search for
-  a prime, but can instead verify that the given $\ell$ is prime and
-  is not too far from the base starting point of the prime search.
-
-\item accept iff $\mathit{ch}' = \mathit{ch}$ and $\ell' = \ell$.
-\end{itemize}
-
-\paragraph{Proof of security.}
-We need to prove two things: 
-(1) privacy in the random oracle model:
-there is a simulator that can generate a properly distributed
-signature just given $c$ and $m$, and 
-(2) security: an attacker that is given $c$ along with a 
-signature on some message $m$
-with respect to $c$ and can generate a valid signature for $c$ on
-some message $m' \neq m$ can be used to compute $\sqrt{t} \in \ZZ_n$
-for some $2 \leq t \leq 1000$.
-
-\paragraph{Proof of privacy.}
-TODO: Use the ZK proof of the interactive protocol. Easy corollary.
-
-\paragraph{Proof of security.}
-TODO: Use the extractor of the interactive protocol. Easy corollary.
+\input{rsa}
 

### 2019-01-19 paper/zk.tex
split out zk from defs

--- 2019-01-09 paper.tex
@@
-\documentclass[11pt]{article}
-\usepackage[hidelinks]{hyperref}
-\usepackage{amsthm,amsmath,amsfonts,amssymb,amstext,mathtools}
-\usepackage{fullpage}
-\usepackage{macros}
-
-\begin{document}
-
-\title{An Airdrop That Preserves Recipient Privacy}
-\author{Dan Boneh \and Riad Wahby}
-
-\maketitle
-
-\begin{abstract}
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-
-More to come.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Private airdrop: definitions}
-
-A private airdrop (PAD) system is a triple of efficient algorithms:
-\begin{itemize}
-\item $\text{sendTokens}(\PK) \to (c, s)$:
-Generates a token $c$ to be posted on the blockchain,
-and a secret~$s$ given to the recipient via a private channel.
-For example, an encryption of $s$ under $\PK$ can be posted
-to the blockchain.   The posted encrypted $s$ is not associated with 
-the token $c$.
-
-\item $\text{sign}(\SK, (c, s), m) \to \text{sig}$:
-Signs a message $m$ indicating that the token $c$ is spent.
-
-\item $\text{verify}(c, m, \text{sig}) \to \{\text{yes},\text{no}\}:$
-Verify that a signature $\text{sig}$ on token $c$ is valid.
-\end{itemize}
-
-TODO: Need to state security properties formally: 
-(1) $c$ and $\text{sig}$ should reveal nothing about $\PK$,
-(2) without $\SK$ we have existential unforgeability under a 
-(one-time) chosen message attack.
-
 \subsection{Zero-knowledge proofs in generic groups}
@@
 \end{lemma}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A private airdrop to ECDSA and Schnorr public keys}
-
-TODO: needs to be written.  Maybe put this first because it is so much
-simpler?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A private airdrop to RSA public keys}
-
-From here we use the following notations:
-$\lambda$ is the security parameter (e.g., $\lambda = 128$), 
-$\range{\ell}$ denotes the set of integers $\{0,1,\ldots,\ell-1\}$, and 
-$\primes$ is a set of size $2^\lambda$ 
-containing the smallest $2^\lambda$ odd primes. 
-%
-We will also need a set of public parameters that include the description
-of a cyclic group $\GG$ of unknown order.  We let $g$ and $h$ be two
-random generators of $\GG$ where the discrete-log of $g$ base $h$ is unknown.
-
-\subsection{Proving knowledge of the factorization of a hidden integer}
-
-Let $n \in \range{N}$ be a secret integer 
-where $N$ is a public upper bound on~$n$.
-We will also assume that $N > \abs{\GG} \cdot 2^{2 \lambda}$.
-Let $c \deq g^n \cdot h^s \in \GG$ be a commitment to $n$, 
-where $s \rgets \range{N}$.  
-We first develop a zero knowledge protocol for proving knowledge of the
-factorization of~$n$ given only $c$.
-
-To prove knowledge of the factorization of $n$ the prover
-proves knowledge of a $w \in \range{N}$ such that $w^2 \equiv t \pmod{n}$
-for some small public prime $t \in \ZZ$, namely $2 \leq t \leq \lambda$.
-That is, we provide a ZKPK for the relation
-\begin{equation} \label{eq:lang}
-  {\cal R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
-                              (n, s, w, a) \in \range{N}^4 \Bigr)  \ \ 
-        \text{s.t.}\ \ 
-                \begin{split}
-                        c   & = g^n \cdot h^s \ \ \text{in $\GG$}, \\
-                        w^2 & = t + a \cdot n \ \ \text{in $\ZZ$}, \\
-                        2 & \leq t \leq \lambda  \ \textrm{a prime}
-                \end{split}  \right\}.
-\end{equation}
-Here $(c, t)$ is a statement and $(n, s, w, a)$ is a witness.
-The integer relation $w^2 = t + a\cdot n$ proves that 
-$w^2 \equiv t \pmod{n}$, as required.
-We note that a ZKPK for~\eqref{eq:lang} proves that $t \in \ZZ$ is a quadratic
-residue modulo the committed $n$.  Leaking this bit of information about $n$
-does not interfere with the application to a secure airdrop.
-
-\medskip\noindent
-Protocol $\prot{P}$: The ZKPK protocol for~\eqref{eq:lang} 
-between the prover $P$ and the verifier $V$ works as follows:
-\begin{itemize}
-\item input:  the verifier has $(c, t) \in \GG \times \range{\lambda}$ and 
-the prover has $(c, t, n, s, w, a) \in \GG \times \range{N}^5$
-
-\item Prover $P$ chooses a random integers $s_1, s_2 \rgets \range{N}$ and computes
-       $c_1 \gets g^w \cdot h^{s_1} \in \GG$ and $c_2 \gets g^a \cdot h^{s_2}$.
-
-\item Next, define a homomorphism $\phi:\ZZ^8 \to \GG^4 \times \ZZ$ 
-parameterized by $g, h, c, c_1, c_2$ as follows:
-\begin{equation} \label{eq:hom}
-  \phi\left(\!\!\begin{array}{l}
-                w, \mathit{w2}, s_1, a, \\
-                \mathit{na}, \mathit{s1w}, \mathit{sa}, s_2
-      \end{array}  \!\!\!\right) \deq
-      \Bigl(\ 
-       g^w \cdot h^{\mathit{s1}},\ \ \ 
-       g^a \cdot h^{\mathit{s2}},\ \ \ 
-       g^{\mathit{w2}} \cdot h^{\mathit{s1w}} / c_1^w,\ \ \ 
-       g^{\mathit{na}} \cdot h^{\mathit{sa}} / c^a,\ \ \ 
-       \mathit{w2} - \mathit{na}\ \Bigr)
-\end{equation}
-It is easy to see that $\phi$ is a group homomorphism.
-The range of $\phi$ is the group $\GG^4 \times \ZZ$.  
-We will write the group operation in this group multiplicatively.
-That is, if $(a_i, b_i, c_i, d_i, e_i) \in \GG^4 \times \ZZ$ for $i=1,2$
-then 
-\[  (a_1, b_1, c_1, d_1, e_1) \cdot (a_2, b_2, c_2, d_2, e_2) \deq 
-      (a_1 a_2,\ b_1 b_2,\ c_1 c_2,\ d_1 d_2,\ e_1 + e_2).  \]
-
-We need a ZKPK for a $\phi$-preimage of 
-$T \deq (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ$. 
-In other words, we need a zero-knowledge proof of knowledge for a vector 
-$\vv' = (w', \mathit{w2}', s_1', a', \mathit{na}', 
-              \mathit{s1w}', \mathit{sa}', s_2') \in \ZZ^8$ 
-such that 
-\[   \phi(\vv') = T = (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ.  \]
-Doing so proves 
-that $c_1$ is a commitment to $w' \in \ZZ$, 
-that $c_2$ is a commitment to $a' \in \ZZ$,
-that $\mathit{w2}' = (w')^2$, and 
-that $\mathit{na}' = a' \cdot n$ for some integer $a'$.
-Then the last relation proves that $(w')^2 - a' \cdot n = t$ in $\ZZ$,
-as required.
-
-We design a ZKPK for a $\phi$-preimage 
-using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}:
-\begin{enumerate}
-\item The prover chooses a random $\rv \rgets \range{2^{2\lambda}}^8$
-and computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$. \\
-It sends $(c_1, c_2, \Rv)$ to the verifier.
-
-\item The verifier chooses challenges $\mathit{ch} \rgets \range{2^\lambda}$
-and $\ell \rgets \primes$. \\
-It sends $(\ell, \mathit{ch})$ to the prover.
-
-\item The prover computes:
-\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
-    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^8, \quad
-    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^8, \quad
-    \Zv_q \gets \phi(\zv_q)  
-\]
-and sends $(\Zv_q, \zv_\ell) \in (\GG^4 \times \ZZ) \times \range{\ell}^8$ 
-to the verifier.
-
-\item The verifier accepts if 
-$\ \Zv_q^\ell \cdot \phi(\zv_\ell) = T^\mathit{ch} \cdot \Rv\ $ in 
-$\GG^4 \times \ZZ$.
-\end{enumerate}
-\end{itemize}
-
-\paragraph{Comment 1.}
-The protocol is insecure if the group $\GG$ contains a non-identity
-element of known order.  In the multiplicative group $(\ZZ/n)^*$ the
-element $-1$ has order~$2$, and hence the protocol is insecure in this
-group.  Instead, we can work in the quotient group $(\ZZ/n)/\{\pm 1\}$, 
-where elements are represented as integers in the interval $[1,n/2]$
-and the product of $x$ and $y$ is defined as 
-$\abs{x \cdot y} = \min(z, n-z)$ where $z = (x \cdot y \bmod n)$.
-In this group $-1$ is the same as $1$, and presumably there are
-no other known elements of known order.
-
-\paragraph{Comment 2.}
-The commitment $c_2$ to the integer $a$ is necessary for soundness,
-and in particular to ensure that $a$ is an integer.  If $c_2$ along
-with $s_2$ and the second coordinate of $\phi$ are eliminated then there
-is an attack where an adversarial prover can prove knowledge of
-$(\sqrt{3} \bmod n)$ using $a = 1/n$ and $w = 2$.
-
-\paragraph{Comment 3.}
-There is a seemingly simpler method to prove that one knows the
-factorization of~$n$, namely, prove that one knows $p$ such that $p$
-divides $n$.  That is, instead of committing to $w$ we would commit to
-$p$ and $q$ and then prove that $p \cdot q = n$. But we would
-also need to prove that the committed $p$ is not one of 
-$\{1, -1, n, -n\}$, and that results in a longer proof.
-
-\paragraph{Proof of security.}
-We need to prove the protocol above is zero-knowledge and a 
-proof of knowledge.
-
-\begin{theorem}
-Protocol $\prot{P}$ is a zero-knowledge protocol
-for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang}.
-\end{theorem}
-
-\begin{proof}
-The simulator takes $(c, t)$ as input and outputs the simulated transcript
-$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
-\begin{alg}
-\> choose random $\hat{c}_1, \hat{c}_2 \rgets \GG,\ \ \ell \rgets \primes$, and
-$\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
-\> set $c_1 \gets \hat{c}_1^\ell$ and $c_2 \gets \hat{c}_2^\ell$, \AlgSep
-\> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
-\lnum \label{ln:randv}
-\> choose random $\hat{\rv} \rgets \range{2^{2\lambda}}^8$
-and define $\hat{T} \deq \Big(\hat{c}_1^\mathit{ch}, \hat{c}_2^\mathit{ch}, 1, 1, \lfloor (t \cdot \mathit{ch})/\ell \rfloor\Big) \in \GG^4 \times \ZZ$, \AlgSep
-\> set $\Zv_q \deq \hat{T} \cdot \phi(\lfloor \hat{\rv}/\ell \rfloor) \in \GG^4 \times \ZZ$, \AlgSep
-\lnum \label{ln:computeR}
-\> compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
-\> output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
-\end{alg}
-We show the simulated transcript is distributed statistically close
-to an accepting transcript of a real protocol execution.
-Because $\ell$ does not divide $\abs{\GG}$ with overwhelming probability,
-we know that $c_1$ and $c_2$ are uniform in $\GG$. 
-Hence, observe that $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
-exactly as in a real transcript.  It remains to show that the same holds
-for $\zv_\ell, \Zv_q$, and $\Rv$. 
-In an interaction with a real prover 
-the vector $\rv$ is chosen uniformly in $\range{2^{2\lambda}}^8$.
-Consider one value $r \rgets \range{2^{2\lambda}}$.
-Because $2^{2\lambda}$ is much larger than $\ell$
-we know that the pair 
-$\big(\lfloor r/\ell \rfloor,\ (r \bmod \ell) \big)$
-is statistically close to uniform in $\range{2^{2\lambda}/\ell} \times \range{\ell}$.
-It directly follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
-in a real transcript, is statistically close to uniform 
-in $\range{\ell}^8$, as in the simulation.
-
-Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly. 
-Write $\hat{\rv}$ generated on line~\eqref{ln:randv} in the simulation
-as $\hat{\rv} = \big(r_\text{w}, r_\text{w2}, r_\text{s1}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}, r_\text{s2} \big)$.
-Then the simulated $\Zv_q$ is computed as:
-\begin{equation} \label{eq:sim}
-\Zv_q \deq \left(\begin{array}{l}
-Z_1 \gets \hat{c}_1^\mathit{ch} \cdot g^{\lfloor r_\text{w}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1}/\ell \rfloor} ,\quad
-Z_2 \gets \hat{c}_2^\mathit{ch} \cdot g^{\lfloor r_\text{a}/\ell \rfloor} \cdot h^{\lfloor r_\text{s2}/\ell \rfloor} , \AlgSep
-Z_3 \gets g^{\lfloor r_\text{w2}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1w}/\ell \rfloor} / \hat{c}_1^{\lfloor r_\text{w}/\ell \rfloor},\quad
-Z_4 \gets g^{\lfloor r_\text{na}/\ell \rfloor} \cdot h^{\lfloor r_\text{sa}/\ell \rfloor} / \hat{c}^{\lfloor r_\text{a}/\ell \rfloor}, \AlgSep
-Z_5 \gets \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2}/\ell \rfloor - \lfloor r_\text{na}/\ell \rfloor 
-\end{array}\right) \in \GG^4 \times \ZZ.  
-\end{equation}
-Let's start with $Z_5 \in \ZZ$.  
-In a real transcript 
-$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
-          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
-Therefore, because $\mathit{w2} - \mathit{na} = t$, we have
-that $Z_5$ is a real transcript satifies
-\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor - \Delta \]
-where $\Delta \in \{0, 1\}$. 
-In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
-and $\lfloor r_\text{na} / \ell \rfloor$ 
-are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
-as in the the simulated $Z_5$ in~\eqref{eq:sim}.
-The only difference is that the real distribution is shifted by $\Delta$
-where as the simulated distribution is not.  
-Because $\Delta$ is small, $\Delta \in \{0,1\}$,
-this difference only negligibly affects the statistical distance. 
-We thus conclude that the simulated $Z_5$ in~\eqref{eq:sim} 
-is statistically close to its real distribution.
-Essentially the same argument shows that $Z_1, Z_2, Z_3, Z_4$ are
-also simulated correctly. 
-{\bf TODO:} explain why.
-
-Finally, because the simulated $c_1, c_2, \ell, \mathit{ch}, \Zv_q, \zv_\ell$
-are all distributed statistically close to a real transcript, 
-it must be the case that the computed $\Rv$ 
-on line~\eqref{ln:computeR} is also distributed as in 
-a real transcript. 
-\end{proof}
-
-\iffalse
-An optimization: the transcript elements $Z_3, Z_4 \in \GG$ can be simulated
-in a similar fashion to how we simulated $Z_5$ in the proof above.
-That is, 
-$Z_3 = g^{\lfloor r_\text{w2} / \ell \rfloor} h^{\lfloor r_\text{s1w} / \ell \rfloor} / c_1^{\lfloor r_\text{w} / \ell \rfloor} \in \GG$
-and 
-$Z_4 = g^{\lfloor r_\text{na} / \ell \rfloor} h^{\lfloor r_\text{sa} / \ell \rfloor} / c^{\lfloor r_\text{a} / \ell \rfloor} \in \GG$,
-where 
-$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}$
-are chosen uniformly in $\range{N}$. 
-It is not difficult to see that these $Z_3$ and $Z_4$ 
-are distributed as in a real transcript.
-This method of simulation can be used to make the protocol slightly more
-efficient because the randomizers 
-$r_\text{w}, r_\text{w2}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa} \in \ZZ$
-do not need to be uniform in the entire interval $\range{N}$.
-It suffices to choose these six values 
-uniformly in $\range{2^{2 \lambda}}$, which is a smaller interval
-than $\range{N}$.  Only $r_\text{s1}$ and $r_\text{s2}$ need to be chosen
-uniformly in the full interval $\range{N}$ so that $Z_1$ and $Z_2$ are uniform
-in $\GG$. 
-However, if the simulator chooses $c_1, c_2 \in \GG$ randomly in $\GG$
-so that it knows
-their $\ell$-th root, then even $Z_1$ and $Z_2$ can also be simulated as above.
-Then $r_\text{s1}$ and $r_\text{s2}$ can also be chosen uniformly
-in the range $\range{2^{2 \lambda}}$.
-In other words, the simulator works by first 
-choosing a random $\rv \gets \range{2^{2\lambda}}^8$,
-computing $\Rv \gets \phi(\rv)$, and then
-solving for $\Zv_q \in \GG^4 \times \ZZ$. 
-\fi
-
-\begin{definition}
-We say that algorithm ${\cal G}$ is an \defn{honest instance
-generator} for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}
-if it chooses integers $n, s, t$, and outputs $(c, t)$ where
-$c \deq g^n h^s \in \GG$. 
-\end{definition}
-
-\begin{theorem}
-Protocol $\prot{P}$ is an argument of knowledge
-for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang} 
-for instances $(c,t)$ generated by an honest instance
-generator ${\cal G}$,
-when the group $\GG$ is a modeled as a generic group of unknown order. 
-\end{theorem}
-
-\begin{proof}
-We construct an extractor that given an instance $(c,t)$ 
-generated by ${\cal G}$,
-interacts with a convincing prover and outputs a witness $(n, s, w, a)$ 
-for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}. 
-The protocol transcript is $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
-The extractor rewinds the prover and obtains two
-accepting transcripts
-${\cal T}_1 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
-and 
-${\cal T}_2 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
-Dividing the corresponding verification equations one by the other
-we obtain
-\[   (\Zv_q / \Zv_q')^\ell \cdot \phi(\zv_\ell - \zv_\ell') = 
-          T^{\mathit{ch} - \mathit{ch}'}. \]
-Let $\zv_\ell - \zv_\ell' = \Big(\Delta w,\ \Delta \mathit{w2},\ \Delta \mathit{s1},\ \Delta a,\ \Delta \mathit{na},\ \Delta \mathit{s1w},\ \Delta \mathit{sa},\ \Delta \mathit{s2} \Big) \in \ZZ^8$ and let $\Delta \mathit{ch} = \mathit{ch} - \mathit{ch}' \in \ZZ$.
-Then plugging this into the definition of $\phi$ we obtain
-\begin{equation} \label{eq:messy}
-      (\Zv_q / \Zv_q')^\ell \cdot
-      \left(\begin{array}{l}
-       g^{\Delta w} \cdot h^{\Delta \mathit{s1}},\ \ \ 
-       g^{\Delta a} \cdot h^{\Delta \mathit{s2}},\ \ \ 
-       g^{\Delta \mathit{w2}} \cdot h^{\Delta \mathit{s1w}} / c_1^{\Delta w}, \\
-       g^{\Delta \mathit{na}} \cdot h^{\Delta \mathit{sa}} / c^{\Delta a},\ \ \ 
-       \Delta \mathit{w2} - \Delta \mathit{na}\ 
-       \end{array} \right)
-          = \left(\begin{array}{l}c_1, \ c_2, \ 1, \\ 1,\ t \end{array}\right)^{\Delta \mathit{ch}}.
-\end{equation}
-Let $\Zv_q / \Zv_q' = (z_1, z_2, z_3, z_4, z_5)$ 
-where $z_1, z_2, z_3, z_4 \in \GG$ and $z_5 \in \ZZ$.  
-In a generic group $\GG$, the group elements $z_1, z_2, z_3, z_4$ 
-must satisfy $z_i = g^{\alpha_i} h^{\beta_i} c^{\gamma_i} \prod_{j=1}^q g_j^{\delta_{i,j}}$
-for $i=1,2,3,4$, 
-and $c_1 = g^{\alpha} h^{\beta} c^\gamma \prod_{j=1}^q g_j^{\delta_{j}}$,
-and $c_2 = g^{\alpha_0} h^{\beta_0} c^\gamma \prod_{j=1}^q g_j^{\delta_{0,j}}$,
-where the extractor knows all the listed integer exponents.
-Here $g_1,\ldots,g_q \in \GG$ are random group elements produced in response
-to a generic group oracle query for a random group element.
-
-It now follows from~\eqref{eq:messy}, and from $c = g^n h^s$, 
-and by uniqueness of representation in generic groups (\Lemma{lem:unique}),
-that the following equations must hold over the integers:
-\begin{align*}
-  \ell \cdot (\alpha_1 + n \cdot \gamma_1) + \Delta w & = (\alpha + n \cdot \gamma) \cdot \Delta \mathit{ch},  &
-  \ell \cdot (\beta_1 + s \cdot \gamma_1) + \Delta \mathit{s1} & = (\beta + s \cdot \gamma) \cdot \Delta \mathit{ch}  
-\\
-  \ell \cdot (\alpha_2 + n \cdot \gamma_2) + \Delta a & = (\alpha_0 + n \cdot \gamma_0) \cdot \Delta \mathit{ch},  &
-  \ell \cdot (\beta_2 + s \cdot \gamma_2) + \Delta \mathit{s2} & = (\beta_0 + s \cdot \gamma_0) \cdot \Delta \mathit{ch}  
-\\
-  \ell \cdot (\alpha_3 + n \cdot \gamma_3) + \Delta \mathit{w2} & = (\alpha + n \cdot \gamma) \cdot \Delta w,  &
-  \ell \cdot (\beta_3 + s \cdot \gamma_3) + \Delta \mathit{s1w} & = (\beta + s \cdot \gamma) \cdot \Delta w   
-\\
-  \ell \cdot (\alpha_4 + n \cdot \gamma_4) + \Delta \mathit{na} & = n \cdot \Delta a,  & 
-  \ell \cdot (\beta_4 + s \cdot \gamma_4) + \Delta \mathit{sa} & = s \cdot \Delta a   
-\\
-  \ell \cdot z_4 + \Delta \mathit{w2} - \Delta \mathit{na} & = t \cdot \Delta \mathit{ch} 
-\end{align*}
-The extractor knows all these values except for $n$ and $s$.
-Reducing these equations modulo $\ell$ gives:
-\begin{align}
-  \Delta w & \equiv (\alpha + n \cdot \gamma) \cdot \Delta \mathit{ch}  &
-  \Delta \mathit{s1} & \equiv (\beta + s \cdot \gamma) \cdot \Delta \mathit{ch}  & \pmod{\ell} 
-\label{eq:first} \\
-  \Delta a & \equiv (\alpha_0 + n \cdot \gamma_0) \cdot \Delta \mathit{ch}  &
-  \Delta \mathit{s2} & \equiv (\beta_0 + s \cdot \gamma_0) \cdot \Delta \mathit{ch}  & \pmod{\ell} 
-\label{eq:firsta} \\
-  \Delta \mathit{w2} & \equiv (\alpha + n \cdot \gamma) \cdot \Delta w  &
-  \Delta \mathit{s1w} & \equiv (\beta + s \cdot \gamma) \cdot \Delta w   & \pmod{\ell} 
-\label{eq:second} \\
-  \Delta \mathit{na} & \equiv n \cdot \Delta a  & 
-  \Delta \mathit{sa} & \equiv s \cdot \Delta a   & \pmod{\ell} 
-\label{eq:third} \\
-  \Delta \mathit{w2} - \Delta \mathit{na} & \equiv t \cdot \Delta \mathit{ch} 
-      &&& \pmod{\ell} 
-\label{eq:fourth} 
-\end{align}
-
-Consider the left equalities in~\eqref{eq:first} and~\eqref{eq:firsta}.
-Define $w \deq \alpha + n \cdot \gamma \in \ZZ$ 
-and $a \deq \alpha_0 + n \cdot \gamma_0 \in \ZZ$.
-For any pair of accepting transcripts such as $({\cal T}_1, {\cal T}_2)$,
-it must be the case that 
-$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ and
-$\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$. 
-The extractor knows $\Delta w,\ \Delta a$, and $\Delta \mathit{ch}$.
-Hence, by constructing a polynomial number of such accepting transcript pairs, 
-the extractor can recover $w, a \in \ZZ$ using the chinese remainder theorem.
-
-Next, consider the left equation in~\eqref{eq:second}.
-Using $w = \alpha + n \cdot \gamma$ and
-$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ gives
-$\Delta \mathit{w2} \equiv w^2 \cdot \Delta \mathit{ch} \pmod{\ell}$.
-
-Using $\Delta \mathit{w2} \equiv w^2 \cdot \Delta \mathit{ch} \pmod{\ell}$
-in~\eqref{eq:fourth}
-gives $\Delta \mathit{na} \equiv (w^2 - t) \cdot \Delta \mathit{ch} \pmod{\ell}$. 
-Finally, the left equality in~\eqref{eq:third} 
-gives $(w^2 - t)\cdot \Delta \mathit{ch} \equiv n \cdot \Delta a \pmod{\ell}$.
-Using $\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$
-we obtain that the extracted integers $w$ and $a$ must satisfy
-$(w^2 - t)\cdot \Delta \mathit{ch} \equiv 
-      n \cdot a \cdot \Delta \mathit{ch} \pmod{\ell}$.  
-Since $\ell$ does not divide $\Delta \mathit{ch}$ with overwhelming
-probability, we obtain that $w^2 - t \equiv n \cdot a \pmod{\ell}$.
-Since this equality holds modulo a random $\ell \in \primes$ 
-with overwhelming probability, 
-the equality $w^2 - t = n \cdot a$ must hold over the integers,
-as required.   Note that this implies that $a \neq 0$.
-
-Because $a \neq 0$, the extractor can obtain $(n \bmod \ell)$
-from the left equality in~\eqref{eq:third}, and thus extract $n \in \ZZ$ by
-repeating over several $\ell$.  Similarly, it can extract $s \in \ZZ$ from
-the right equality in~\eqref{eq:third}.   
-It thus obtains a witness $(n, s, w, a)$ 
-for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}, as required.
-\end{proof}
-
-\subsection{The concrete airdrop system}
-
-The airdrop system is obtained by applying the Fiat-Shamir
-heuristic to the protocol from the previous section. 
-The concrete private airdrop system works as follows:
-
-\paragraph{Algorithm $\text{sendTokens}(\PK)$:}
-To send tokens to an RSA public key $\PK = (n, e)$ do:
-\begin{itemize}
-\item 
-generate a random $s \rgets \range{G}$.
-
-\item 
-output $(c, s)$ where $c \gets g^n \cdot h^s \in \GG$.
-\end{itemize}
-
-\medskip\noindent 
-The following two notes can help optimize the scheme:
-\begin{itemize}
-\item[$-$] $s$ is privately sent to the owner of $\PK$, for example
-by encrypting $s$ under $\PK$ to obtain a ciphertext $c'$ and
-publishing this $c'$ somewhere, not necessarily on the blockchain.  There is
-a public association between $c'$ and $\PK$ (e.g., via a hash table),
-so that the owner of $\PK$ can easily find $c'$.  One can include
-$H(c)$ in the plaintext encrypted in $c'$ to help the owner of $\PK$
-quickly find $c$.
-
-\item[$-$] One can generate $s$ 
-as $s \gets H(s')$ where $s'$ is a random 256-bit value and $H$ is a hash
-function $H:\{0,1\}^{256} \to \range{G}$.  The ciphertext $c'$ is
-an encryption of $s'$, instead of $s$, which can shrink~$c'$.
-\end{itemize}
-
-\paragraph{Algorithm $\text{sign}(\SK, (c, s), m)$:}  
-To withdraw the funds associated with the token $c$ the user
-signs a withdrawal message $m$ using the RSA secret key $\SK = (n,p,q)$ 
-as follows:
-\begin{itemize}
-\item find a prime $2 \leq t \leq \lambda$  such that $t$ is a quadratic 
-residue in $\ZZ_n$.
-
-\item find integers $(w,a)$ such that $w^2 = t + a n$ in $\ZZ$
-           (i.e. $w$ is a square root of $t$ modulo $n$)
-
-\item choose a random $s_1 \rgets \range{N}$ and compute
-           $c_1 \gets g^w \cdot h^{s_1} \in \GG$.
-
-\item choose a random $s_2 \rgets \range{N}$ and compute
-           $c_2 \gets g^a \cdot h^{s_2} \in \GG$.
-
-\item choose a random $\rv \rgets \range{2^{2\lambda}}^8$
-and compute $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$,
-where $\phi$ is the homomorphism defined in~\eqref{eq:hom}.
-
-\item compute $\mathit{seed} \gets \text{Hash}(m, \GG, g, h, c, c_1, c_2, t, \Rv$).
-
-\item
-use a $\text{PRNG}(\mathit{seed})$ to generate $(\mathit{ch}, \ell)$, 
-where $\mathit{ch} \in \range{2^\lambda}$ and $\ell \in \primes$.
-
-\item compute:
-\[  \zv \gets (\mathit{ch} \cdot \vv + \rv) \in \ZZ^8, \quad
-    \zv_\ell \gets (\zv \bmod \ell) \in \range{\ell}^8, \quad
-    \zv_q \gets \lfloor \zv / \ell \rfloor \in \ZZ^8, \quad
-    \Zv_q \gets \phi(\zv_q) \in \GG^4 \times \ZZ.
-\]
-
-\item output the signature 
-$\mathit{sig} = (c_1, c_2, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$.
-\end{itemize}
-
-\paragraph{Algorithm $\text{verify}(c, m, \mathit{sig}):$}
-Verify that $\mathit{sig} = (c_1, c_2, t, \mathit{ch}, \ell, \Zv_q, \zv_\ell)$ 
-is a valid signature for token~$c$ on the message~$m$.
-\begin{itemize}
-\item reject if $t \notin \range{\lambda}$ or $t$ is not a prime.
-
-\item with $T \deq (c_1, c_2, 1, 1, t) \in \GG^4 \times \ZZ$, 
-compute $\Rv' \gets \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$.
-
-\item compute $\mathit{seed}' \gets \text{Hash}(m, \GG, g, h, c, c_1, c_2, t, \Rv'$)
-
-\item use a $\text{PRNG}(\mathit{seed}')$ to generate 
-  $\mathit{ch}' \in \range{2^\lambda}$ and $\ell' \in \primes$. \\
-Since $\ell$ is
-  included in the signature, the verifier does not need to search for
-  a prime, but can instead verify that the given $\ell$ is prime and
-  is not too far from the base starting point of the prime search.
-
-\item accept iff $\mathit{ch}' = \mathit{ch}$ and $\ell' = \ell$.
-\end{itemize}
-
-\paragraph{Proof of security.}
-We need to prove two things: 
-(1) privacy in the random oracle model:
-there is a simulator that can generate a properly distributed
-signature just given $c$ and $m$, and 
-(2) security: an attacker that is given $c$ along with a 
-signature on some message $m$
-with respect to $c$ and can generate a valid signature for $c$ on
-some message $m' \neq m$ can be used to compute $\sqrt{t} \in \ZZ_n$
-for some $2 \leq t \leq 1000$.
-
-\paragraph{Proof of privacy.}
-TODO: Use the ZK proof of the interactive protocol. Easy corollary.
-
-\paragraph{Proof of security.}
-TODO: Use the extractor of the interactive protocol. Easy corollary.
-
-\bibliographystyle{alpha}
-\bibliography{paper}
-
-\end{document}

### 2019-01-19 paper/defs.tex
defs: small

@@
     the token in a transaction on a blockchain.
-To claim the transaction's value, \Rt generates a new transaction and
+To claim the transaction's output, \Rt generates a new transaction and
     uses the token and corresponding secret key $\SK$ to generate a signature; it posts the

### 2019-01-19 paper/intro.tex
move some stuff from intro to 'prac'

@@
 More to come.
-
-\rsw{stashed note from talk with DB}
-Simultaneously using the schemes of \S\ref{sec:dsa} and \S\ref{sec:rsa}
-    on the same blockchain allows distinguishing between users based on
-    key type.
-Can work around this using generic ZKPK, at substantial performance cost.
-(Alt narrative: talk about generic ZKPK first, then specialize to get better
-    perf. at cost of distinguishing.)
-
-\rsw{stashed note from chat with Henry and Dima}
-Possible objection: why doesn't sender just generate a bunch of phony keys
-    and send all money to self?
-In other words, why is this scheme better, from the verifiers' point of view,
-    than the naive approach, i.e., sender generating a fresh key pair and
-    sending secret key to recipient?
-(Note that while the naive approach does not have existential unforgeability,
-    that property does not prevent self-dealing if sender knows secret key.
-Another way to say this is that the security property we need for the
-    airdrop-to-Github-users case is stronger than existential unforgeability.)
-
-One answer: for each RSA key $\PK = (n, e)$ to be paid, sender publishes
-    the challenge $c = g^nh^s$ and (separately, i.e., without revealing
-    correspondence) sender also publishes
-$(\PK, s')$, $s' = E(\PK, (c',s)))$, $c' = H(g^nh^s)$.
-In other words, the sender publishes a list of purported airdrop recipients
-    separately from the list of airdrop challenge tokens.
-
-If sender was dishonest with respect to any key, i.e., if for some $(\PK,
-    s')$, any of $s', c', c, s$ is invalid, key's owner can reveal $(\hat{c}',
-    \hat{s}) = D(\PK, s')$.
-Then verifiers check that $s' = E(\PK, (\hat{c}', \hat{s}))$, and that
-    either no corresponding $c$ exists, or that $c$ is not a commitment
-    to $n$ with opening $s$.

### 2019-01-19 paper/prac.tex
move some stuff from intro to 'prac'

\section{Practical considerations for private airdrops}

\rsw{stashed note from talk with DB}
Simultaneously using the schemes of \S\ref{sec:dsa} and \S\ref{sec:rsa}
    on the same blockchain allows distinguishing between users based on
    key type.
Can work around this using generic ZKPK, at substantial performance cost.
(Alt narrative: talk about generic ZKPK first, then specialize to get better
    perf. at cost of distinguishing.)

\rsw{stashed note from chat with Henry and Dima}
Possible objection: why doesn't sender just generate a bunch of phony keys
    and send all money to self?
In other words, why is this scheme better, from the verifiers' point of view,
    than the naive approach, i.e., sender generating a fresh key pair and
    sending secret key to recipient?
(Note that while the naive approach does not have existential unforgeability,
    that property does not prevent self-dealing if sender knows secret key.
Another way to say this is that the security property we need for the
    airdrop-to-Github-users case is stronger than existential unforgeability.)

One answer: for each RSA key $\PK = (n, e)$ to be paid, sender publishes
    the challenge $c = g^nh^s$ and (separately, i.e., without revealing
    correspondence) sender also publishes
$(\PK, s')$, $s' = E(\PK, (c',s)))$, $c' = H(g^nh^s)$.
In other words, the sender publishes a list of purported airdrop recipients
    separately from the list of airdrop challenge tokens.

If sender was dishonest with respect to any key, i.e., if for some $(\PK,
    s')$, any of $s', c', c, s$ is invalid, key's owner can reveal $(\hat{c}',
    \hat{s}) = D(\PK, s')$.
Then verifiers check that $s' = E(\PK, (\hat{c}', \hat{s}))$, and that
    either no corresponding $c$ exists, or that $c$ is not a commitment
    to $n$ with opening $s$.

### 2019-01-19 paper/defs.tex
defs: better game names (maybe)

@@
     nothing about $\PK$.
-Specifically, consider $\mathsf{Anonym}$, a game between a PPT adversary $\adv$
+Specifically, consider $\mathsf{Anon}$, a game between a PPT adversary $\adv$
     and a challenger $\chall$:
@@
 %
-$\adv$ wins $\mathsf{Anonym}$ if $b' = b$.
+$\adv$ wins $\mathsf{Anon}$ if $b' = b$.
 
 \begin{definition}
-Let an adversary $\adv$'s advantage in $\mathsf{Anonym}$ be
-$\mathrm{Adv}_{\adv}^{\mathsf{Anonym}} = \sizeof{\probab{\adv~\text{wins}} - \nicefrac{1}{2}}$.
+Let an adversary $\adv$'s advantage in $\mathsf{Anon}$ be
+$\mathrm{Adv}_{\adv}^{\mathsf{Anon}} = \sizeof{\probab{\adv~\text{wins}} - \nicefrac{1}{2}}$.
 Then an airdrop scheme is \emph{anonymous} if, for any PPT adversary
-    $\adv$, $\mathrm{Adv}_{\adv}^{\mathsf{Anonym}} \le \text{negl}$.
+    $\adv$, $\mathrm{Adv}_{\adv}^{\mathsf{Anon}} \le \text{negl}$.
 \end{definition}
@@
     message.
-Specifically, consider $\mathsf{Unforg}$, a game between a PPT adversary
+Specifically, consider $\mathsf{Forge}$, a game between a PPT adversary
     $\adv$ and a challenger $\chall$:
@@
 %
-$\adv$ wins $\mathsf{Unforg}$ if $\msg' \neq \msg \wedge \text{verify}(c, \msg', \sig') = \text{yes}$.
+$\adv$ wins $\mathsf{Forge}$ if $\msg' \neq \msg \wedge \text{verify}(c, \msg', \sig') = \text{yes}$.
 
 \begin{definition}
-Let an adversary $\adv$'s advantage in $\mathsf{Unforg}$ be
-$\mathrm{Adv}_{\adv}^{\mathsf{Unforg}} = \probab{\adv~\text{wins}}$.
+Let an adversary $\adv$'s advantage in $\mathsf{Forge}$ be
+$\mathrm{Adv}_{\adv}^{\mathsf{Forge}} = \probab{\adv~\text{wins}}$.
 Then an airdop is \emph{unforgeable} if, for any PPT adversary $\adv$,
-$\mathrm{Adv}_{\adv}^{\mathsf{Unforg}} \le \text{negl}$.
+$\mathrm{Adv}_{\adv}^{\mathsf{Forge}} \le \text{negl}$.
 \end{definition}
